---
title: "namibia_hec_stats"
author: "Chris Kracha"
date: '2022-09-24'
output: html_document
---

```{r setup}
library(here)
library(janitor)
library(broom)
library(rgdal)
library(exactextractr)
library(terra)
library(tidyverse)
library(sf)

# Enter YOUR data path to HWC_data folder, including "HWC_data"
HWC_data <- "G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data" 
```

## Load in data
```{r}
namibia_hec <- read_csv(paste0(HWC_data, "/R_files/R_input_data/namibia/namibia_hec.csv")) %>%
  clean_names() %>%
  dplyr::select(-amount_paid)

lu <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))

conservancies <- vect(paste0(HWC_data, "/R_files/R_input_data/shapefilesforconservancies/communal_conservancies.shp")) %>%
  terra::project(crs(lu))

sdm <- rast(paste0(HWC_data, "/Wallace SDM Rasters/LQ/1981_2010/afel_historic_sdm.tif"))

# Reproject SDM to equal area
sdm_reproj <- sdm %>%
  terra::project(crs(lu)) %>%
  crop(conservancies)
```

## Create initial HEC data frame
```{r}
cons_df <- as.data.frame(conservancies,
                     geom = NULL,
                     xy = FALSE,
                     # KEEP NAs until last possible join 
                     # so that columns don't mismatch
                     na.rm = FALSE) %>%
  dplyr::select(1:8)
```


## Extract SDM to table
```{r}
sdm_extract <- terra::extract(sdm_reproj, conservancies, 
                       fun = max, # find maximum value
                       method = "simple", 
                       cells = TRUE, 
                       na.rm = FALSE) %>% 
  rename(sdm_max = afel_historic_sdm)
```

## Land use to table

### Crop land use to africa
```{r}
lu_at <- crop(lu, conservancies)
#plot(lu_im)
```

### Reclassify baseline land use to cropland binary
We want cropland (category 5) to be 1, everything else to be 0
```{r}
baseline_cropland <- lu_at
baseline_cropland[baseline_cropland != 5] <- 0
baseline_cropland[baseline_cropland == 5] <- 1
#plot(baseline_cropland)
```

### Extract proportion of cell covered in cropland to table
```{r}
crop_extract <- terra::extract(baseline_cropland, conservancies, 
                        # Mean of binary values = proportion
                        fun = mean,
                        method = "simple",
                        cells = TRUE, 
                        na.rm = FALSE) %>% 
  rename(crop_mean = global_LULC_2015)
```

## Forest binary to table

### Reclassify baseline land use to forest binary
```{r}
baseline_forest <- lu_at 
baseline_forest[baseline_forest != 2] <- 0
baseline_forest[baseline_forest == 2] <- 1

```

### Extract proportion of cell covered in forest to table
```{r}
forest_extract <- terra::extract(baseline_forest, conservancies, 
                        # Mean of binary values = proportion
                        fun = mean,
                        method = "simple",
                        cells = TRUE, 
                        na.rm = FALSE) %>% 
  rename(forest_mean = global_LULC_2015)
```

## Water binary to table

### Reclassify baseline land use to water binary
We want water (category 1) to be 1, everything else to be 0
```{r}
baseline_water <- lu_at
baseline_water[baseline_water != 1] <- 0
baseline_water[baseline_water == 1] <- 1
#plot(baseline_water)
```

### Extract proportion of cell covered in water
```{r}
water_extract <- terra::extract(baseline_water, conservancies, 
                        # Mean of binary values = proportion
                        fun = mean,
                        method = "simple",
                        cells = TRUE, 
                        na.rm = FALSE) %>% 
  rename(water_mean = global_LULC_2015)
```

## Population to table

### Load population data
```{r}
population_raw <- rast(paste0(HWC_data, "/Geospatial Data/Pop_dens/ppp_2010_1km_Aggregated.tif"))

population_reproj <- population_raw %>% 
  crop(sdm) %>%
  terra::project(crs(lu), method = "near")

plot(population_reproj)
```

### Extract population in each cell
```{r}
population_extract <- extract(population_reproj,
                              conservancies,
                              fun = sum, 
                              method = "simple",
                              cells = TRUE,
                              na.rm = FALSE) %>% 
  rename(population_n = ppp_2010_1km_Aggregated) %>%
  mutate(population_nK = population_n/1000)
# population_nK units are 1000s of people
```

## Join tables
```{r}
# First merge SDM and crop
variables_join <- sdm_extract %>%
  merge(crop_extract, by = "ID") %>%

# Now merge sdm/crop table with water
  merge(water_extract, by = "ID") %>%

# Merge that table with forest %
  merge(forest_extract, by = "ID") %>%

# Merge that table with population
  merge(population_extract, by = "ID")

# Now merge with conflict, remove hec NA values (100), and convert date to year only

analysis_table <- right_join(cons_df, variables_join, by = c("OBJECTID_1" = "ID")) %>%
  right_join(namibia_hec, by = c("NAME" = "location")) %>%
  na.omit() %>%
  mutate(incidents_normalized = number_of_incidents/AREA_KM2,
         hectares_normalized = number_of_hectares_destroyed/AREA_KM2)
```

## Visualize variables' relationship to HEC  incidents
```{r}
analysis_table %>%
  ggplot(aes(x = sdm_max, y = number_of_incidents)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = crop_mean, y = number_of_incidents)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = water_mean, y = number_of_incidents)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = forest_mean, y = number_of_incidents)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = population_nK, y = number_of_incidents)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)
```
## Visualize variables' relationship to HEC incidents (normalized to area)
```{r}
analysis_table %>%
  ggplot(aes(x = sdm_max, y = incidents_normalized)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = crop_mean, y = incidents_normalized)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = water_mean, y = incidents_normalized)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = forest_mean, y = incidents_normalized)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = population_nK, y = incidents_normalized)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)
```

## Visualize variables' relationship to crop damage
```{r}
analysis_table %>%
  ggplot(aes(x = sdm_max, y = number_of_hectares_destroyed)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = crop_mean, y = number_of_hectares_destroyed)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = water_mean, y = number_of_hectares_destroyed)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = forest_mean, y = number_of_hectares_destroyed)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = population_nK, y = number_of_hectares_destroyed)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)
```

## Visualize variables' relationship to crop damage (normalized by area)
```{r}
analysis_table %>%
  ggplot(aes(x = sdm_max, y = hectares_normalized)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = crop_mean, y = hectares_normalized)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = water_mean, y = hectares_normalized)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = forest_mean, y = hectares_normalized)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)

analysis_table %>%
  ggplot(aes(x = population_nK, y = hectares_normalized)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="lm", 
                se = FALSE)
```

