---
title: "assam_random_effects_model"
author: "Grace Kumaishi"
date: "8/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(broom)
library(rgdal)
#library(exactextractr)
library(terra)
library(lubridate)

# Enter YOUR data path to HWC_data folder, including "HWC_data". 
# May require double forward slashes
HWC_data <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data" 
```

# Load Data and Reproject to WGS84 Equal Area

## Load in Land Use Raster & Assam HEC vector and reproject HEC to land use/equal area
```{r}
lu <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))

assam_HEC_reproj <- vect(paste0(HWC_data, "/Geospatial Data/Assam_India/AWS-all_data/AWS-all_data.shp")) %>%
  project(crs(lu))

crs(assam_HEC_reproj)
plot(assam_HEC_reproj)
```

## Load in Historic SDM and reproject to land use/equal area
```{r}
# Read in the baseline land use and SDM
sdm <- rast(paste0(HWC_data, "/Wallace SDM Rasters/asia/1981_2010/asian_elephant_historic_raw.tif"))
```

### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)
```{r}
ext(sdm) <- c(65.8581934609999990,
              131.0665265334999958,
              -12.2168058669999979,
              35.8248606080000016)
```

### Re-project SDM to equal-area
```{r}
sdm_reproj_im <- sdm %>% 
  project(crs(lu))
```

# Create Simplified HEC Presence data frame

### Turn SpatVector into data frame
```{r}
hec <- as.data.frame(assam_HEC_reproj,
                     geom = NULL,
                     xy = FALSE,
                     na.rm = FALSE) %>% 
  select(c(Conflict, DateSent))

hec <- tibble::rowid_to_column(hec, "ID")
```


# SDM Extraction

### Extract maximum SDM value at each cell
```{r}
sdm_extract <- extract(sdm_reproj_im, assam_HEC_reproj, 
                       fun = max, 
                       method = "simple", 
                       cells = TRUE, 
                       na.rm = FALSE) %>% 
  rename(sdm_max = asian_elephant_historic_raw)
```

# Cropland Extraction

### Crop land use to asia
```{r}
lu_im <- crop(lu, sdm_reproj_im)
plot(lu_im)
```

### Reclassify baseline land use to cropland binary
We want cropland (category 5) to be 1, everything else to be 0
```{r}
baseline_cropland <- lu_im
baseline_cropland[baseline_cropland != 5] <- 0
baseline_cropland[baseline_cropland == 5] <- 1
plot(baseline_cropland)
```

### Aggregate land use to fit HEC grid
```{r}
# factor <- c(ceiling(11470/1000), ceiling(9649/1000)) 
# # Found with ArcGIS Pro
# 
# base_cropland_agg_HEC <- aggregate(baseline_cropland, fact = factor)
# 
# names(base_cropland_agg_HEC) <- "crop_2015"
# 
# plot(base_cropland_agg_HEC)
```

### Extract proportion of cell covered in cropland
```{r}
crop_extract <- extract(baseline_cropland, assam_HEC_reproj, # I didn't use the aggregated file as it was no longer binary, probably want to double check this
                        fun = mean, # not sure about this, how do we get proportions in R?
                        method = "simple",
                        cells = TRUE, 
                        na.rm = FALSE) %>% 
  rename(crop_mean = global_LULC_2015)
```

# Water Extraction

### Reclassify baseline land use to water binary
We want water (category 1) to be 1, everything else to be 0
```{r}
baseline_water <- lu_im
baseline_water[baseline_water != 1] <- 0
baseline_water[baseline_water == 1] <- 1
plot(baseline_water)
```

### Aggregate water to fit HEC grid
```{r}
# factor <- c(ceiling(11470/1000), ceiling(9649/1000)) 
# # Found with ArcGIS Pro
# 
# base_water_agg_HEC <- aggregate(baseline_water, fact = factor) 
# 
# names(base_water_agg_HEC) <- "water_2015"
# 
# plot(base_water_agg_HEC)
```

### Extract proportion of cell covered in water
```{r}
water_extract <- extract(baseline_water, assam_HEC_reproj, # I didn't use the aggregated file as it was no longer binary, probably want to double check this
                        fun = mean, # not sure about this, how do we get proportions in R?
                        method = "simple",
                        cells = TRUE, 
                        na.rm = FALSE) %>% 
  rename(water_mean = global_LULC_2015)
```

# Join tables/merge dataframes containing SDM, crop, and water data

```{r}
# First merge SDM and crop
sdm_crop_join <- merge(sdm_extract, crop_extract, by = "ID")

# Now merge sdm/crop table with water
sdm_crop_water_join <- merge(sdm_crop_join, water_extract, by = "ID")

# Now merge with conflict, remove hec NA values (100), and convert date to year only
analysis_table <- merge(hec, sdm_crop_water_join, by = "ID") %>% 
  filter(Conflict != 100) %>% 
  rename(hec = Conflict) %>% 
  mutate(year = year(DateSent)) %>% 
  select(-DateSent)
```

# Run Random Effects Model

```{r}
library(plm)

random <- plm(hec ~ sdm_max, data = analysis_table, model = "random")
#summary(random)
```






