---
title: "assam_random_effects_model"
author: "Grace Kumaishi, Chris Kracha"
date: "8/23/2022"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(broom)
library(rgdal)
library(lubridate)
library(terra)

# Enter YOUR data path to HWC_data folder, including "HWC_data". # May require double forward slashes

HWC_data <- "G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data" 
```

# Load Data and Reproject

## Load in Land Use Raster & Assam HEC vector and reproject HEC to land use/equal area
```{r}
lu <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))

assam_HEC_reproj <- vect(paste0(HWC_data, "/Geospatial Data/Assam_India/AWS-all_data/AWS-all_data.shp")) %>%
  terra::project(crs(lu))

crs(assam_HEC_reproj)
```

## Load in Historic SDM
```{r}
# Read in the baseline land use and SDM
sdm <- rast(paste0(HWC_data, "/Wallace SDM Rasters/asia/1981_2010/asian_elephant_historic_raw.tif"))
```

### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)
```{r}
ext(sdm) <- c(65.8581934609999990,
              131.0665265334999958,
              -12.2168058669999979,
              35.8248606080000016)
```

### Re-project SDM to equal-area
```{r}
sdm_reproj_im <- sdm %>% 
  terra::project(crs(lu))
```

## Load in Surface Water
```{r}
sWater <- rast(paste0(HWC_data, "/Geospatial Data/Surface_water/occurrence_90E_30Nv1_3_2020.tif")) %>%
  aggregate(., fact = 10, fun = "mean") %>%
  terra::project(crs(lu))
```

# Create Simplified HEC Presence data frame

### Turn SpatVector into data frame
```{r}
hec_df <- as.data.frame(assam_HEC_reproj,
                     geom = NULL,
                     xy = FALSE,
                     # KEEP NAs until last possible join 
                     # so that columns don't mismatch
                     na.rm = FALSE) %>%
  dplyr::select(c(Conflict, Crop, DateSent, Respondant, Col_Row))

hec_df <- rowid_to_column(hec_df, "ID") # Add ID column
```

# SDM Extraction

### Extract maximum SDM value at each cell
```{r}
sdm_extract <- terra::extract(sdm_reproj_im, assam_HEC_reproj, 
                       fun = max, # find maximum value
                       method = "simple", 
                       cells = TRUE, 
                       na.rm = FALSE) %>% 
  rename(sdm_max = asian_elephant_historic_raw)
```

# Cropland Extraction

### Crop land use to asia
```{r}
lu_im <- crop(lu, sdm_reproj_im)
#plot(lu_im)
```

### Reclassify baseline land use to cropland binary
We want cropland (category 5) to be 1, everything else to be 0
```{r}
baseline_cropland <- lu_im
baseline_cropland[baseline_cropland != 5] <- 0
baseline_cropland[baseline_cropland == 5] <- 1
#plot(baseline_cropland)
```

### Extract proportion of cell covered in cropland
```{r}
crop_extract <- terra::extract(baseline_cropland, assam_HEC_reproj, 
                        # Mean of binary values = proportion
                        fun = mean,
                        method = "simple",
                        cells = TRUE, 
                        na.rm = FALSE) %>% 
  rename(crop_mean = global_LULC_2015)
```

# Water Extraction (from Chen)

### Reclassify baseline land use to water binary
We want water (category 1) to be 1, everything else to be 0
```{r}
baseline_water <- lu_im
baseline_water[baseline_water != 1] <- 0
baseline_water[baseline_water == 1] <- 1
#plot(baseline_water)
```

### Extract proportion of cell covered in water
```{r}
water_extract <- terra::extract(baseline_water, assam_HEC_reproj, 
                        # Mean of binary values = proportion
                        fun = mean,
                        method = "simple",
                        cells = TRUE, 
                        na.rm = FALSE) %>% 
  rename(water_mean = global_LULC_2015)
```

# Distance to Forest

### Create polygon of binary forest
```{r}
baseline_forest_dist <- lu_im 
baseline_forest_dist[baseline_forest_dist != 2] <- NA
baseline_forest_dist[baseline_forest_dist == 2] <- 1 

forest_crop <- crop(baseline_forest_dist, assam_HEC_reproj)
```

### terra::distance (to give you a SpatRaster)
```{r}
forest_dist <- terra::distance(forest_crop)
#plot(forest_dist)
```

### Find geographic distance (distance raster) to polygon edge
```{r}
forest_dist_extract <- terra::extract(forest_dist, assam_HEC_reproj, 
                        fun = max, ### Do we want maximum here???
                        method = "simple",
                        cells = TRUE, 
                        na.rm = FALSE) %>% 
  rename(forest_dist_m = global_LULC_2015) %>% 
  mutate(forest_dist_km = (forest_dist_m/1000)) %>% 
  dplyr::select(-forest_dist_m)
```

# Percent Forest
```{r}
baseline_forest <- lu_im 
baseline_forest[baseline_forest != 2] <- 0
baseline_forest[baseline_forest == 2] <- 1

```

```{r}
forest_extract <- terra::extract(baseline_forest, assam_HEC_reproj, 
                        # Mean of binary values = proportion
                        fun = mean,
                        method = "simple",
                        cells = TRUE, 
                        na.rm = FALSE) %>% 
  rename(forest_mean = global_LULC_2015)
```

# Number of People per cell

### Load population data
```{r}
population_raw <- rast(paste0(HWC_data, "/Geospatial Data/Pop_dens/ppp_2010_1km_Aggregated.tif"))

population_reproj <- population_raw %>% 
  crop(sdm) %>%
  terra::project(crs(lu))

plot(population_reproj)
```

### Extract population in each cell
```{r}
population_extract <- terra::extract(population_reproj,
                              assam_HEC_reproj,
                              fun = sum, 
                              method = "simple",
                              cells = TRUE,
                              na.rm = FALSE) %>% 
  rename(population_n = ppp_2010_1km_Aggregated) %>%
  mutate(population_nK = population_n/1000)
```

# Join tables/merge dataframes containing SDM, crop, and water data

```{r}
# First merge SDM and crop
variables_join <- sdm_extract %>%
  merge(crop_extract, by = "ID") %>%

# Now merge sdm/crop table with water
  merge(water_extract, by = "ID") %>%

# Merge that table with forest %
  merge(forest_extract, by = "ID") %>%
  
# Merge that table with forest distance
  merge(forest_dist_extract, by = "ID") %>%

# Merge that table with population
  merge(population_extract, by = "ID")

# Now merge with conflict, remove hec NA values (100), and convert date to year only
analysis_table <- merge(hec_df, variables_join, by = "ID") %>% 
  filter(Conflict != 100) %>% 
  rename(hec = Conflict,
         hecCrop = Crop,
         date = DateSent,
         respondant = Respondant) %>%
  # hec must be numeric or factor to run analysis
  mutate(hec = as.factor(hec),
         hecCrop = as.factor(hecCrop),
         respondant = as.factor(respondant))
```

# Variable distribution visualization

### Histograms with absolute y-axis
```{r}
ggplot(analysis_table, aes(x = crop_mean, fill = hec)) +
  geom_histogram() +
  labs(title = "Assam Cells Cropland", 
       x = "% Cropland",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212")) 

ggplot(analysis_table, aes(x = water_mean, fill = hec)) +
  geom_histogram() +
  labs(title = "Assam Cells Water", 
       x = "% Water",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212")) 

ggplot(analysis_table, aes(x = sdm_max, fill = hec)) +
  geom_histogram() +
  labs(title = "Assam Cells SDM", 
       x = "Maximum SDM",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212"))

ggplot(analysis_table, aes(x = forest_mean, fill = hec)) +
  geom_histogram() +
  labs(title = "Assam Cells Forest", 
       x = "% Forest",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212"))

ggplot(analysis_table, aes(x = forest_dist_km, fill = hec)) +
  geom_histogram() +
  labs(title = "Assam Cells Forest Distance", 
       x = "Max Distance to Forest (km)",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212"))

ggplot(analysis_table, aes(x = population_nK, fill = hec)) +
  geom_histogram() +
  labs(title = "Assam Cells Population", 
       x = "Population (thousands)",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212"))

ggplot(analysis_table, aes(x = as.factor(date), fill = hec)) +
  geom_bar(stat = "count") +
  labs(title = "Assam Cells by Date", 
       x = "Date Sent",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212")) +
  theme(axis.text.x=element_text(angle = -45, hjust = 0))

ggplot(analysis_table, aes(x = as.factor(respondant), 
                           fill = hec)) +
  geom_bar(stat = "count") +
  labs(title = "Assam Cells by Respondant", 
       x = "Respondant",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212"))

```

### Histograms with proportionate y-axis
```{r}
ggplot(analysis_table, aes(x = crop_mean, fill = hec)) +
  geom_histogram(position = "fill") +
  labs(title = "Assam Cells Cropland (Proportional)", 
       x = "% Cropland",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212")) 

ggplot(analysis_table, aes(x = water_mean, fill = hec)) +
  geom_histogram(position = "fill") +
  labs(title = "Assam Cells Water (Proportional)", 
       x = "% Water",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212")) 

ggplot(analysis_table, aes(x = sdm_max, fill = hec)) +
  geom_histogram(position = "fill") +
  labs(title = "Assam Cells SDM (Proportional)", 
       x = "Maximum SDM",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212"))

ggplot(analysis_table, aes(x = forest_mean, fill = hec)) +
  geom_histogram(position = "fill") +
  labs(title = "Assam Cells Forest", 
       x = "% Forest",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212"))

ggplot(analysis_table, aes(x = forest_dist_km, fill = hec)) +
  geom_histogram(position = "fill") +
  labs(title = "Assam Cells Forest Distance (Proportional)", 
       x = "Max Distance to Forest (km)",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212"))

ggplot(analysis_table, aes(x = population_nK, fill = hec)) +
  geom_histogram(position = "fill") +
  labs(title = "Assam Cells Population (Proportional)", 
       x = "Population (thousands)",
       fill = "HEC Presence") +
  scale_fill_manual(labels = c("No", "Yes"), 
                    values = c("#a3a3a3", "#ff1212"))
```

### Boxplots
```{r}
ggplot(analysis_table, aes(x = hec, y = crop_mean)) + 
  geom_boxplot()

ggplot(analysis_table, aes(x = hec, y = sdm_max)) + 
  geom_boxplot()

ggplot(analysis_table, aes(x = hec, y = population_nK)) + 
  geom_boxplot()

ggplot(analysis_table, aes(x = hec, y = forest_mean)) +
  geom_boxplot()

ggplot(analysis_table, aes(x = hec, y = forest_dist_km)) +
  geom_boxplot()

ggplot(analysis_table, aes(x = hec, y = water_mean)) +
  geom_boxplot()
```

# Mixed effects logit model

## Predicting all HEC

### Logistic model
```{r}
library(lme4)
reg1 <- glmer(hec ~ sdm_max + crop_mean + population_nK + 
                (1|date) + (1|respondant), 
              data = analysis_table, 
              family = binomial(link = "logit"))

summary(reg1)
```

### Logit regression for each variable
```{r}
analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = sdm_max, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="glm", 
                se = FALSE, 
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = crop_mean, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="glm", 
                se = FALSE, 
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = population_nK, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="glm", 
                se = FALSE, 
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = forest_mean, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="glm", 
                se = FALSE, 
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hec = as.numeric(hec) - 1,
         crop_dev = abs((crop_mean - mean(crop_mean))
                        /sd(crop_mean))) %>%
  ggplot(aes(x = crop_dev, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="glm", 
                se = FALSE, 
                method.args = list(family = binomial))
```

### Additive model for each variable
```{r}
analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = sdm_max, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = crop_mean, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = population_nK, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = forest_mean, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = forest_dist_km, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = water_mean, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))
```

## Predicting just crop-related HEC

### Logistic Regression
```{r}
reg2 <- glmer(hecCrop ~ crop_mean + sdm_max + population_nK +
                (1|date) + (1|respondant), 
              data = analysis_table, 
              family = binomial(link = "logit"))

summary(reg2)
```

### Logit regression for each variable
```{r}
analysis_table %>%
  drop_na() %>%
  mutate(hecCrop = as.numeric(hecCrop) - 1) %>%
  filter(hecCrop != 2) %>%
  ggplot(aes(x = sdm_max, y = hecCrop)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="glm", 
                se = FALSE, 
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hecCrop = as.numeric(hecCrop) - 1) %>%
  filter(hecCrop != 2) %>%
  ggplot(aes(x = crop_mean, y = hecCrop)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="glm", 
                se = FALSE, 
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hecCrop = as.numeric(hecCrop) - 1) %>%
  filter(hecCrop != 2) %>%
  ggplot(aes(x = population_nK, y = hecCrop)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="glm", 
                se = FALSE, 
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hec = as.numeric(hec) - 1) %>%
  ggplot(aes(x = forest_dist_km, y = hec)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="glm", 
                se = FALSE, 
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hecCrop = as.numeric(hecCrop) - 1,
         crop_dev = abs((crop_mean - mean(crop_mean))
                        /sd(crop_mean))) %>%
  filter(hecCrop != 2) %>%
  ggplot(aes(x = crop_dev, y = hecCrop)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="glm", 
                se = FALSE, 
                method.args = list(family = binomial))
```



### Additive model for each variable
```{r}
analysis_table %>%
  mutate(hecCrop = as.numeric(hecCrop) - 1) %>%
  filter(hecCrop != 2) %>%
  ggplot(aes(x = sdm_max, y = hecCrop)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hecCrop = as.numeric(hecCrop) - 1) %>%
  filter(hecCrop != 2) %>%
  ggplot(aes(x = crop_mean, y = hecCrop)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hecCrop = as.numeric(hecCrop) - 1) %>%
  filter(hecCrop != 2) %>%
  ggplot(aes(x = population_nK, y = hecCrop)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hecCrop = as.numeric(hecCrop) - 1) %>%
  filter(hecCrop != 2) %>%
  ggplot(aes(x = forest_mean, y = hecCrop)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hecCrop = as.numeric(hecCrop) - 1) %>%
  filter(hecCrop != 2) %>%
  ggplot(aes(x = forest_dist_km, y = hecCrop)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))

analysis_table %>%
  mutate(hecCrop = as.numeric(hecCrop) - 1) %>%
  filter(hecCrop != 2) %>%
  ggplot(aes(x = water_mean, y = hecCrop)) + 
    geom_point(alpha=.5) +
    stat_smooth(method="gam", 
                se = FALSE,
                method.args = list(family = binomial))
```