---
title: "Assam Chi Square Test"
author: "Grace Kumaishi"
date: "8/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(broom)
library(rgdal)
library(exactextractr)
library(terra)

# Enter YOUR data path to HWC_data folder, including "HWC_data". 
# May require double forward slashes
HWC_data <- "G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data" 
```

## POINT HEC CHI SQ

### Load in existing data

```{r}
historic_bivariate_asia_raw <- terra::rast(here(HWC_data, "/Geospatial Data/bivariate_outputs/asel_bivariate_baseline.tif"))
  
historic_bivariate_asia_project <- terra::project(x = historic_bivariate_asia_raw, y = "epsg:4326", method = "near")
```

### Get counts of bivariate category for HEC in Goalpara

```{r}
# Load tidy Goalpara HEC file
goalpara_hec_tidy <- read.csv(here(HWC_data, "/Geospatial Data/Assam_India/Goalpara_HEC_tidy.csv"))

# Make into SpatVector
goalpara_hec_tidy_vect <- terra::vect(goalpara_hec_tidy, geom = c("longitude", "latitude"), crs = "epsg:4326")

# Create new Goalpara file with only cropland
goalpara_hec_crop <- goalpara_hec_tidy %>% 
  filter(hec_type == "crop")

# Make into SpatVector
goalpara_hec_crop_vect <- terra::vect(goalpara_hec_crop, geom = c("longitude", "latitude"), crs = "epsg:4326")
```

```{r}
# Extract bivariate at points
goalpara_hec_extract <- extract(historic_bivariate_asia_project, goalpara_hec_crop_vect, 
                            fun = NULL, 
                            method = "simple",
                            list = FALSE,
                            factors = TRUE) 
```

```{r}
goalpara_hec_extract_count <- goalpara_hec_extract %>% 
  count(indicus_historic) %>% 
  arrange(-n) 
```

### Get counts of bivariate category for random points in Goalpara

```{r}
# Load random Goalpara points
goalpara_random <- terra::vect(here(HWC_data, "/Geospatial Data/Assam_India/random_points_goalpara.shp"), crs = "epsg:4326")
```

```{r}
# Extract bivariate at random points
goalpara_extract_random <- extract(historic_bivariate_asia_project, goalpara_random, 
                            fun = NULL, 
                            method = "simple",
                            list = FALSE,
                            factors = TRUE) 
```

```{r}
goalpara_extract_random_count <- goalpara_extract_random %>% 
  count(indicus_historic) %>% 
  arrange(-n) 
```

### Create table with both extracts by hand

```{r}
bivariate_counts <- data.frame(points = c("HEC", "Random"),
                               med_suit_high_crop = c(14, 46),
                               high_suit_no_crop = c(0, 13),
                               high_suit_med_crop = c(56, 97),
                               high_suit_high_crop = c(273, 187)) 

bivariate_proportions <- bivariate_counts %>% #add proportions/percentages
  janitor::adorn_percentages() %>% 
  janitor::adorn_pct_formatting(digits = 2) %>% 
  janitor::adorn_ns()
```

### Convert to contingency table

```{r}
bivariate_ct <- bivariate_counts %>% 
  column_to_rownames(var = "points")
```

### Run Chi Square test

```{r}
# Are the different point distributions and bivariate categories independent? Are proportions at each category so different that we can conclude there is a significant association of point distribution on the category?

bivariate_x2 <- chisq.test(bivariate_ct)

bivariate_x2

bivariate_tidy <- broom::tidy(bivariate_x2)
```

## DIGITIZED HEC CHI SQ 

```{r}
# Load in csv with extractions

assam_extract_digitized <- read.csv(here(HWC_data, "/Geospatial Data/Assam_India/assam_points_table_with_conflict.csv"))

assam_summarize_digitized <- assam_extract_digitized %>% 
  group_by(Conflict, Bivar_value) %>% 
  summarise(count = n()) %>% 
  pivot_wider(names_from = Bivar_value, values_from = count)

assam_na_digitized <- head(assam_summarize, -1)

assam_ct_digitized <- assam_na_digitized %>% 
  column_to_rownames(var = "Conflict")
```

```{r}
# Run chi-square test

digitized_x2 <- chisq.test(assam_ct_digitized)

digitized_x2

digitized_tidy <- broom::tidy(digitized_x2)
```

## GRIDDED HEC CHI SQ 

```{r}
# Load in Assam vector grid

assam_HEC_vect <- vect(paste0(HWC_data, "/Geospatial Data/Assam_India/AWS-all_data/AWS-all_data.shp"))

# Extract bivariate to Assam vector

assam_extract <- extract(historic_bivariate_asia_project, assam_HEC_vect, method = "simple") %>%
  right_join(., as.data.frame(assam_HEC_vect), by = "ID")

assam_summarize <- assam_extract %>% 
  group_by(Conflict, indicus_historic) %>% 
  summarise(count = n()) %>% 
  pivot_wider(names_from = indicus_historic, values_from = count)

assam_remove_na <- head(assam_summarize, -1) %>%
  select(1:6)

assam_ct <- assam_remove_na %>% 
  column_to_rownames(var = "Conflict")
```

```{r}
# Run chi-square test

gridded_x2 <- chisq.test(assam_ct)

gridded_x2

gridded_tidy <- broom::tidy(gridded_x2)
```

## CONTINUOUS GRIDDED HEC MODELING

#### Load in HEC vector and reproject to land use
```{r}
lu <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))

assam_HEC_reproj <- vect(paste0(HWC_data, "/Geospatial Data/Assam_India/AWS-all_data/AWS-all_data.shp")) %>%
  project(crs(lu))

crs(assam_HEC_reproj)
plot(assam_HEC_reproj)
```

### SDM
```{r}
# Read in the baseline land use and SDM
sdm <- rast(paste0(HWC_data, "/Wallace SDM Rasters/asia/1981_2010/indicus_historic.tif"))
```

#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)
```{r}
ext(sdm) <- c(65.8581934609999990,
              131.0665265334999958,
              -12.2168058669999979,
              35.8248606080000016)
```

#### Re-project SDM to equal-area
```{r}
sdm_reproj_im <- sdm %>% 
  project(crs(lu))
```

### Cropland

#### Crop land use to asia
```{r}
lu_im <- crop(lu, sdm_reproj_im)
```

#### Reclassify baseline land use to cropland binary
We want cropland (category 5) to be 1, everything else to be 0
```{r}
baseline_cropland <- lu_im
baseline_cropland[baseline_cropland != 5] <- 0
baseline_cropland[baseline_cropland == 5] <- 1
plot(baseline_cropland)
```

#### Aggregate land use to fit HEC grid
```{r}
factor <- c(ceiling(11470/1000), ceiling(9649/1000)) 
# Found with ArcGIS Pro

base_cropland_agg_HEC <- aggregate(baseline_cropland, fact = factor)

names(base_cropland_agg_HEC) <- "crop_2015"

plot(base_cropland_agg_HEC)
```

### Water

#### Reclassify baseline land use to water binary
We want water (category 1) to be 1, everything else to be 0
```{r}
baseline_water <- lu_im
baseline_water[baseline_water != 1] <- 0
baseline_water[baseline_water == 1] <- 1
plot(baseline_water)
```

#### Aggregate water to fit HEC grid
```{r}
factor <- c(ceiling(11470/1000), ceiling(9649/1000)) 
# Found with ArcGIS Pro

base_water_agg_HEC <- aggregate(baseline_water, fact = factor) 

names(base_water_agg_HEC) <- "water_2015"

plot(base_water_agg_HEC)
```

### Extraction into table

#### Extract continuous SDM
```{r}
assam_extract_sdm <- extract(sdm_reproj_im, assam_HEC_reproj, method = "simple") %>%
  right_join(., as.data.frame(assam_HEC_reproj), by = "ID") %>%
  filter(Respondant != "dd") %>%
  distinct(ID, .keep_all = TRUE)
```

#### Combine and extract LU
```{r}
base_lu_agg_HEC <- c(base_cropland_agg_HEC, base_water_agg_HEC)

assam_extract_lu <- extract(base_lu_agg_HEC, assam_HEC_reproj, method = "simple") %>%
  right_join(., assam_extract_sdm, by = "ID") %>%
  rename(sdm_2015 = indicus_historic)

assam_extract_lu
```

### Statistical test





