---
title: "Asia Chelsa Data Wrangling (Future)"
author: "Grace Kumaishi"
date: "7/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(terra)
library(tidyverse)
library(sf)
```

```{r}
## Elements required for each scenario
#indomalay region, which rasters will be cropped to
indomalay_region <- st_read("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/indomalay_region/indomalay_region.shp", crs = 4326)

bios <- c(1,2,4,6,7,12,14,15)
layers <- 1:8
```

############################### 2071-2100 ############################### 

############################ SSP 1 RCP 2.6 ##############################

# 2071 - 2100
# SSP 1 RCP 2.6
# GFDL-ESM4 MODEL
DONE
```{r}
gfdl_2071_2100_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/126/GFDL_ESM4/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_gfdl-esm4_ssp126_V.2.1.tif"))

gfdl_2071_2100_126_crop <- terra::crop(gfdl_2071_2100_126_stack, indomalay_region)

for (i in layers){
  r <- gfdl_2071_2100_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/GFDL_ESM4/gfdl_2071_2100_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 1 RCP 2.6
# IPSL-CM6A-LR
DONE
```{r}
ipsl_2071_2100_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/126/IPSL_CM6A_LR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_ipsl-cm6a-lr_ssp126_V.2.1.tif"))

ipsl_2071_2100_126_crop <- terra::crop(ipsl_2071_2100_126_stack, indomalay_region)

for (i in layers){
  r <- ipsl_2071_2100_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/IPSL_CM6A_LR/ipsl_2071_2100_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 1 RCP 2.6
# MPI-ESM1-2-HR
DONe
```{r}
mpi_2071_2100_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/126/MPI_ESM1_2_HR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_mpi-esm1-2-hr_ssp126_V.2.1.tif"))

mpi_2071_2100_126_crop <- terra::crop(mpi_2071_2100_126_stack, indomalay_region)

for (i in layers){
  r <- mpi_2071_2100_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MPI_ESM1_2_HR/mpi_2071_2100_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 1 RCP 2.6
# MRI-ESM2-0
DONE
```{r}
mri_2071_2100_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/126/MRI_ESM2_0/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_mri-esm2-0_ssp126_V.2.1.tif"))

mri_2071_2100_126_crop <- terra::crop(mri_2071_2100_126_stack, indomalay_region)

for (i in layers){
  r <- mri_2071_2100_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MRI_ESM2_0/mri_2071_2100_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 1 RCP 2.6
# UKESM1-0-LL
DONE
```{r}
ukesm_2071_2100_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/126/UKESM1_0_LL/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_ukesm1-0-ll_ssp126_V.2.1.tif"))

ukesm_2071_2100_126_crop <- terra::crop(ukesm_2071_2100_126_stack, indomalay_region)

for (i in layers){
  r <- ukesm_2071_2100_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/UKESM1_0_LL/ukesm_2071_2100_126_bio", i, ".tif"), overwrite = FALSE)
}
```

############################ SSP 3 RCP 7 #################################

# 2071 - 2100
# SSP 3 RCP 7
# GFDL-ESM4 MODEL
DONE
```{r}
gfdl_2071_2100_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/370/GFDL_ESM4/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_gfdl-esm4_ssp370_V.2.1.tif"))

gfdl_2071_2100_370_crop <- terra::crop(gfdl_2071_2100_370_stack, indomalay_region)

for (i in layers){
  r <- gfdl_2071_2100_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/GFDL_ESM4/gfdl_2071_2100_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 3 RCP 7
# IPSL-CM6A-LR
DONE
```{r}
ipsl_2071_2100_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/370/IPSL_CM6A_LR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_ipsl-cm6a-lr_ssp370_V.2.1.tif"))

ipsl_2071_2100_370_crop <- terra::crop(ipsl_2071_2100_370_stack, indomalay_region)

for (i in layers){
  r <- ipsl_2071_2100_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/IPSL_CM6A_LR/ipsl_2071_2100_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 3 RCP 7
# MPI-ESM1-2-HR
DONE
```{r}
mpi_2071_2100_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/370/MPI_ESM1_2_HR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_mpi-esm1-2-hr_ssp370_V.2.1.tif"))

mpi_2071_2100_370_crop <- terra::crop(mpi_2071_2100_370_stack, indomalay_region)

for (i in layers){
  r <- mpi_2071_2100_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MPI_ESM1_2_HR/mpi_2071_2100_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 3 RCP 7
# MRI-ESM2-0
DONE
```{r}
mri_2071_2100_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/370/MRI_ESM2_0/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_mri-esm2-0_ssp370_V.2.1.tif"))

mri_2071_2100_370_crop <- terra::crop(mri_2071_2100_370_stack, indomalay_region)

for (i in layers){
  r <- mri_2071_2100_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MRI_ESM2_0/mri_2071_2100_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 3 RCP 7
# UKESM1-0-LL
DONE
```{r}
ukesm_2071_2100_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/370/UKESM1_0_LL/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_ukesm1-0-ll_ssp370_V.2.1.tif"))

ukesm_2071_2100_370_crop <- terra::crop(ukesm_2071_2100_370_stack, indomalay_region)

for (i in layers){
  r <- ukesm_2071_2100_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/UKESM1_0_LL/ukesm_2071_2100_370_bio", i, ".tif"), overwrite = FALSE)
}
```

############################ SSP 5 RCP 8.5 #################################

# 2071 - 2100
# SSP 5 RCP 8.5
# GFDL-ESM4 MODEL
DONE
```{r}
gfdl_2071_2100_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/585/GFDL_ESM4/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_gfdl-esm4_ssp585_V.2.1.tif"))

gfdl_2071_2100_585_crop <- terra::crop(gfdl_2071_2100_585_stack, indomalay_region)

for (i in layers){
  r <- gfdl_2071_2100_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/GFDL_ESM4/gfdl_2071_2100_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 5 RCP 8.5
# IPSL-CM6A-LR
DONE
```{r}
ipsl_2071_2100_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/585/IPSL_CM6A_LR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_ipsl-cm6a-lr_ssp585_V.2.1.tif"))

ipsl_2071_2100_585_crop <- terra::crop(ipsl_2071_2100_585_stack, indomalay_region)

for (i in layers){
  r <- ipsl_2071_2100_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/IPSL_CM6A_LR/ipsl_2071_2100_585_bio", i, ".tif"), overwrite = FALSE) 
}
```

# 2071 - 2100
# SSP 5 RCP 8.5
# MPI-ESM1-2-HR
DONE
```{r}
mpi_2071_2100_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/585/MPI_ESM1_2_HR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_mpi-esm1-2-hr_ssp585_V.2.1.tif"))

mpi_2071_2100_585_crop <- terra::crop(mpi_2071_2100_585_stack, indomalay_region)

for (i in layers){
  r <- mpi_2071_2100_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MPI_ESM1_2_HR/mpi_2071_2100_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 5 RCP 8.5
# MRI-ESM2-0
DONE
```{r}
mri_2071_2100_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/585/MRI_ESM2_0/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_mri-esm2-0_ssp585_V.2.1.tif"))

mri_2071_2100_585_crop <- terra::crop(mri_2071_2100_585_stack, indomalay_region)

for (i in layers){
  r <- mri_2071_2100_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MRI_ESM2_0/mri_2071_2100_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2071 - 2100
# SSP 5 RCP 8.5
# UKESM1-0-LL
DONE
```{r}
ukesm_2071_2100_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2071_2100/585/UKESM1_0_LL/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2071-2100_ukesm1-0-ll_ssp585_V.2.1.tif"))

ukesm_2071_2100_585_crop <- terra::crop(ukesm_2071_2100_585_stack, indomalay_region)

for (i in layers){
  r <- ukesm_2071_2100_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/UKESM1_0_LL/ukesm_2071_2100_585_bio", i, ".tif"), overwrite = FALSE)
}
```

############################### 2041-2070 ############################### 

############################ SSP 1 RCP 2.6 ##############################

# 2041 - 2070
# SSP 1 RCP 2.6
# GFDL-ESM4 MODEL
DONE
```{r}
gfdl_2041_2070_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/126/GFDL_ESM4/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_gfdl-esm4_ssp126_V.2.1.tif"))

gfdl_2041_2070_126_crop <- terra::crop(gfdl_2041_2070_126_stack, indomalay_region)

for (i in layers){
  r <- gfdl_2041_2070_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/GFDL_ESM4/gfdl_2041_2070_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 1 RCP 2.6
# IPSL-CM6A-LR
DONE
```{r}
ipsl_2041_2070_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/126/IPSL_CM6A_LR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_ipsl-cm6a-lr_ssp126_V.2.1.tif"))

ipsl_2041_2070_126_crop <- terra::crop(ipsl_2041_2070_126_stack, indomalay_region)

for (i in layers){
  r <- ipsl_2041_2070_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/IPSL_CM6A_LR/ipsl_2041_2070_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 1 RCP 2.6
# MPI-ESM1-2-HR
DONE
```{r}
mpi_2041_2070_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/126/MPI_ESM1_2_HR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_mpi-esm1-2-hr_ssp126_V.2.1.tif"))

mpi_2041_2070_126_crop <- terra::crop(mpi_2041_2070_126_stack, indomalay_region)

for (i in layers){
  r <- mpi_2041_2070_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MPI_ESM1_2_HR/mpi_2041_2070_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 1 RCP 2.6
# MRI-ESM2-0
DONE
```{r}
mri_2041_2070_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/126/MRI_ESM2_0/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_mri-esm2-0_ssp126_V.2.1.tif"))

mri_2041_2070_126_crop <- terra::crop(mri_2041_2070_126_stack, indomalay_region)

for (i in layers){
  r <- mri_2041_2070_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MRI_ESM2_0/mri_2041_2070_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 1 RCP 2.6
# UKESM1-0-LL
DONE
```{r}
ukesm_2041_2070_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/126/UKESM1_0_LL/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_ukesm1-0-ll_ssp126_V.2.1.tif"))

ukesm_2041_2070_126_crop <- terra::crop(ukesm_2041_2070_126_stack, indomalay_region)

for (i in layers){
  r <- ukesm_2041_2070_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/UKESM1_0_LL/ukesm_2041_2070_126_bio", i, ".tif"), overwrite = FALSE)
}
```

############################ SSP 3 RCP 7 #################################

# 2041 - 2070
# SSP 3 RCP 7
# GFDL-ESM4 MODEL
DONE
```{r}
gfdl_2041_2070_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/370/GFDL_ESM4/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_gfdl-esm4_ssp370_V.2.1.tif"))

gfdl_2041_2070_370_crop <- terra::crop(gfdl_2041_2070_370_stack, indomalay_region)

for (i in layers){
  r <- gfdl_2041_2070_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/GFDL_ESM4/gfdl_2041_2070_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 3 RCP 7
# IPSL-CM6A-LR
DONE
```{r}
ipsl_2041_2070_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/370/IPSL_CM6A_LR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_ipsl-cm6a-lr_ssp370_V.2.1.tif"))

ipsl_2041_2070_370_crop <- terra::crop(ipsl_2041_2070_370_stack, indomalay_region)

for (i in layers){
  r <- ipsl_2041_2070_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/IPSL_CM6A_LR/ipsl_2041_2070_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 3 RCP 7
# MPI-ESM1-2-HR
DONE
```{r}
mpi_2041_2070_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/370/MPI_ESM1_2_HR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_mpi-esm1-2-hr_ssp370_V.2.1.tif"))

mpi_2041_2070_370_crop <- terra::crop(mpi_2041_2070_370_stack, indomalay_region)

for (i in layers){
  r <- mpi_2041_2070_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MPI_ESM1_2_HR/mpi_2041_2070_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 3 RCP 7
# MRI-ESM2-0
DONE
```{r}
mri_2041_2070_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/370/MRI_ESM2_0/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_mri-esm2-0_ssp370_V.2.1.tif"))

mri_2041_2070_370_crop <- terra::crop(mri_2041_2070_370_stack, indomalay_region)

for (i in layers){
  r <- mri_2041_2070_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MRI_ESM2_0/mri_2041_2070_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 3 RCP 7
# UKESM1-0-LL
DONE
```{r}
ukesm_2041_2070_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_ukesm1-0-ll_ssp370_V.2.1.tif"))

ukesm_2041_2070_370_crop <- terra::crop(ukesm_2041_2070_370_stack, indomalay_region)

for (i in layers){
  r <- ukesm_2041_2070_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio", i, ".tif"), overwrite = FALSE)
}
```

############################ SSP 5 RCP 8.5 #################################

# 2041 - 2070
# SSP 5 RCP 8.5
# GFDL-ESM4 MODEL
DONE
```{r}
gfdl_2041_2070_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/585/GFDL_ESM4/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_gfdl-esm4_ssp585_V.2.1.tif"))

gfdl_2041_2070_585_crop <- terra::crop(gfdl_2041_2070_585_stack, indomalay_region)

for (i in layers){
  r <- gfdl_2041_2070_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/GFDL_ESM4/gfdl_2041_2070_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 5 RCP 8.5
# IPSL-CM6A-LR
DONE
```{r}
ipsl_2041_2070_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/585/IPSL_CM6A_LR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_ipsl-cm6a-lr_ssp585_V.2.1.tif"))

ipsl_2041_2070_585_crop <- terra::crop(ipsl_2041_2070_585_stack, indomalay_region)

for (i in layers){
  r <- ipsl_2041_2070_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/IPSL_CM6A_LR/ipsl_2041_2070_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 5 RCP 8.5
# MPI-ESM1-2-HR
DONE
```{r}
mpi_2041_2070_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/585/MPI_ESM1_2_HR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_mpi-esm1-2-hr_ssp585_V.2.1.tif"))

mpi_2041_2070_585_crop <- terra::crop(mpi_2041_2070_585_stack, indomalay_region)

for (i in layers){
  r <- mpi_2041_2070_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MPI_ESM1_2_HR/mpi_2041_2070_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 5 RCP 8.5
# MRI-ESM2-0
DONE
```{r}
mri_2041_2070_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/585/MRI_ESM2_0/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_mri-esm2-0_ssp585_V.2.1.tif"))

mri_2041_2070_585_crop <- terra::crop(mri_2041_2070_585_stack, indomalay_region)

for (i in layers){
  r <- mri_2041_2070_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MRI_ESM2_0/mri_2041_2070_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2041 - 2070
# SSP 5 RCP 8.5
# UKESM1-0-LL
DONE
```{r}
ukesm_2041_2070_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2041_2070/585/UKESM1_0_LL/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2041-2070_ukesm1-0-ll_ssp585_V.2.1.tif"))

ukesm_2041_2070_585_crop <- terra::crop(ukesm_2041_2070_585_stack, indomalay_region)

for (i in layers){
  r <- ukesm_2041_2070_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/UKESM1_0_LL/ukesm_2041_2070_585_bio", i, ".tif"), overwrite = FALSE)
}
```

############################### 2011-2040 ###############################

############################ SSP 1 RCP 2.6 ##############################

# 2011 - 2040
# SSP 1 RCP 2.6
# GFDL-ESM4 MODEL
DONE
```{r}
gfdl_2011_2040_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/126/GFDL_ESM4/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_gfdl-esm4_ssp126_V.2.1.tif"))

gfdl_2011_2040_126_crop <- terra::crop(gfdl_2011_2040_126_stack, indomalay_region)

for (i in layers){
  r <- gfdl_2011_2040_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/GFDL_ESM4/gfdl_2011_2040_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 1 RCP 2.6
# IPSL-CM6A-LR
DONE
```{r}
ipsl_2011_2040_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/126/IPSL_CM6A_LR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_ipsl-cm6a-lr_ssp126_V.2.1.tif"))

ipsl_2011_2040_126_crop <- terra::crop(ipsl_2011_2040_126_stack, indomalay_region)

for (i in layers){
  r <- ipsl_2011_2040_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/IPSL_CM6A_LR/ipsl_2011_2040_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 1 RCP 2.6
# MPI-ESM1-2-HR
DONE
```{r}
mpi_2011_2040_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/126/MPI_ESM1_2_HR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_mpi-esm1-2-hr_ssp126_V.2.1.tif"))

mpi_2011_2040_126_crop <- terra::crop(mpi_2011_2040_126_stack, indomalay_region)

for (i in layers){
  r <- mpi_2011_2040_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MPI_ESM1_2_HR/mpi_2011_2040_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 1 RCP 2.6
# MRI-ESM2-0
DONE
```{r}
mri_2011_2040_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/126/MRI_ESM2_0/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_mri-esm2-0_ssp126_V.2.1.tif"))

mri_2011_2040_126_crop <- terra::crop(mri_2011_2040_126_stack, indomalay_region)

for (i in layers){
  r <- mri_2011_2040_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MRI_ESM2_0/mri_2011_2040_126_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 1 RCP 2.6
# UKESM1-0-LL
DONE
```{r}
ukesm_2011_2040_126_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/126/UKESM1_0_LL/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_ukesm1-0-ll_ssp126_V.2.1.tif"))

ukesm_2011_2040_126_crop <- terra::crop(ukesm_2011_2040_126_stack, indomalay_region)

for (i in layers){
  r <- ukesm_2011_2040_126_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/UKESM1_0_LL/ukesm_2011_2040_126_bio", i, ".tif"), overwrite = FALSE)
}
```

############################ SSP 3 RCP 7 #################################

# 2011 - 2040
# SSP 3 RCP 7
# GFDL-ESM4 MODEL
DONE
```{r}
gfdl_2011_2040_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/370/GFDL_ESM4/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_gfdl-esm4_ssp370_V.2.1.tif"))

gfdl_2011_2040_370_crop <- terra::crop(gfdl_2011_2040_370_stack, indomalay_region)

for (i in layers){
  r <- gfdl_2011_2040_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/GFDL_ESM4/gfdl_2011_2040_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 3 RCP 7
# IPSL-CM6A-LR
DONE
```{r}
ipsl_2011_2040_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/370/IPSL_CM6A_LR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_ipsl-cm6a-lr_ssp370_V.2.1.tif"))

ipsl_2011_2040_370_crop <- terra::crop(ipsl_2011_2040_370_stack, indomalay_region)

for (i in layers){
  r <- ipsl_2011_2040_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/IPSL_CM6A_LR/ipsl_2011_2040_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 3 RCP 7
# MPI-ESM1-2-HR
DONE
```{r}
mpi_2011_2040_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/370/MPI_ESM1_2_HR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_mpi-esm1-2-hr_ssp370_V.2.1.tif"))

mpi_2011_2040_370_crop <- terra::crop(mpi_2011_2040_370_stack, indomalay_region)

for (i in layers){
  r <- mpi_2011_2040_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MPI_ESM1_2_HR/mpi_2011_2040_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 3 RCP 7
# MRI-ESM2-0
DONE
```{r}
mri_2011_2040_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/370/MRI_ESM2_0/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_mri-esm2-0_ssp370_V.2.1.tif"))

mri_2011_2040_370_crop <- terra::crop(mri_2011_2040_370_stack, indomalay_region)

for (i in layers){
  r <- mri_2011_2040_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MRI_ESM2_0/mri_2011_2040_370_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 3 RCP 7
# UKESM1-0-LL
DONE
```{r}
ukesm_2011_2040_370_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/370/UKESM1_0_LL/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_ukesm1-0-ll_ssp370_V.2.1.tif"))

ukesm_2011_2040_370_crop <- terra::crop(ukesm_2011_2040_370_stack, indomalay_region)

for (i in layers){
  r <- ukesm_2011_2040_370_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/UKESM1_0_LL/ukesm1_2011_2040_370_bio", i, ".tif"), overwrite = FALSE)
}
```

############################ SSP 5 RCP 8.5 #################################

# 2011 - 2040
# SSP 5 RCP 8.5
# GFDL-ESM4 MODEL
DONE
```{r}
gfdl_2011_2040_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/585/GFDL_ESM4/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_gfdl-esm4_ssp585_V.2.1.tif"))

gfdl_2011_2040_585_crop <- terra::crop(gfdl_2011_2040_585_stack, indomalay_region)

for (i in layers){
  r <- gfdl_2011_2040_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/GFDL_ESM4/gfdl_2011_2040_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 5 RCP 8.5
# IPSL-CM6A-LR
DONE
```{r}
ipsl_2011_2040_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/585/IPSL_CM6A_LR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_ipsl-cm6a-lr_ssp585_V.2.1.tif"))

ipsl_2011_2040_585_crop <- terra::crop(ipsl_2011_2040_585_stack, indomalay_region)

for (i in layers){
  r <- ipsl_2011_2040_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/IPSL_CM6A_LR/ipsl_2011_2040_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 5 RCP 8.5
# MPI-ESM1-2-HR
DONE
```{r}
mpi_2011_2040_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/585/MPI_ESM1_2_HR/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_mpi-esm1-2-hr_ssp585_V.2.1.tif"))

mpi_2011_2040_585_crop <- terra::crop(mpi_2011_2040_585_stack, indomalay_region)

for (i in layers){
  r <- mpi_2011_2040_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MPI_ESM1_2_HR/mpi_2011_2040_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 5 RCP 8.5
# MRI-ESM2-0
DONE
```{r}
mri_2011_2040_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/585/MRI_ESM2_0/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_mri-esm2-0_ssp585_V.2.1.tif"))

mri_2011_2040_585_crop <- terra::crop(mri_2011_2040_585_stack, indomalay_region)

for (i in layers){
  r <- mri_2011_2040_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MRI_ESM2_0/mri_2011_2040_585_bio", i, ".tif"), overwrite = FALSE)
}
```

# 2011 - 2040
# SSP 3 RCP 7
# UKESM1-0-LL
DONE
```{r}
ukesm_2011_2040_585_stack <- stack(paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/chelsa_asia/2011_2040/585/UKESM1_0_LL/CHELSA_bio", c(1,2,4,6,7,12,14,15), "_2011-2040_ukesm1-0-ll_ssp585_V.2.1.tif"))

ukesm_2011_2040_585_crop <- terra::crop(ukesm_2011_2040_585_stack, indomalay_region)

for (i in layers){
  r <- ukesm_2011_2040_585_crop[[i]]
  agg <- aggregate(r, fact = 5, fun = mean)
  terra::writeRaster(agg, paste0("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/UKESM1_0_LL/ukesm_2011_2040_585_bio", i, ".tif"), overwrite = FALSE)
}
```

