---
title: "Asia CHELSA Check"
author: "Grace Kumaishi"
date: "7/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(spocc)
library(spThin)
library(dismo)
library(rgeos)
library(ENMeval)
library(dplyr)
library(sf)
library(terra)
library(patchwork)
```

### DESCRIPTION

This document was created to perform visual checks on individual projected chelsa layers. We found some issues (holes and incorrect units) with some of the Africa variables, so we wanted to do the same here. We also wanted to see if we could visually explain some of the projected SDM outputs with individual variables included in the analysis. 

```{r}
## Elements required for each scenario
#indomalay region, which rasters will be cropped to
indomalay_region <- st_read("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/indomalay_region/indomalay_region.shp", crs = 4326)
```

DONE
```{r}
#### Historic ####
historic_chelsa_01 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Chelsa_Data/asia_masked_CHELSA_data/asia_masked_CHELSA_layer01.tif") 

historic_chelsa_02 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Chelsa_Data/asia_masked_CHELSA_data/asia_masked_CHELSA_layer02.tif")

historic_chelsa_04 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Chelsa_Data/asia_masked_CHELSA_data/asia_masked_CHELSA_layer04.tif")

historic_chelsa_06 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Chelsa_Data/asia_masked_CHELSA_data/asia_masked_CHELSA_layer06.tif")

historic_chelsa_07 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Chelsa_Data/asia_masked_CHELSA_data/asia_masked_CHELSA_layer07.tif")

historic_chelsa_12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Chelsa_Data/asia_masked_CHELSA_data/asia_masked_CHELSA_layer12.tif")

historic_chelsa_14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Chelsa_Data/asia_masked_CHELSA_data/asia_masked_CHELSA_layer14.tif")

historic_chelsa_15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Chelsa_Data/asia_masked_CHELSA_data/asia_masked_CHELSA_layer15.tif")

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(historic_chelsa_01)
plot(historic_chelsa_02)
plot(historic_chelsa_04)
plot(historic_chelsa_06)
plot(historic_chelsa_07)
plot(historic_chelsa_12)
plot(historic_chelsa_14)
plot(historic_chelsa_15)
```

############ 2011 - 2041 ############

####### 126 #######

## GFDL_ESM4 ##
DONE
```{r}
gfdl_2011_2040_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/GFDL_ESM4/gfdl_2011_2040_126_bio1.tif")

gfdl_2011_2040_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/GFDL_ESM4/gfdl_2011_2040_126_bio2.tif")

gfdl_2011_2040_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/GFDL_ESM4/gfdl_2011_2040_126_bio4.tif")

gfdl_2011_2040_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/GFDL_ESM4/gfdl_2011_2040_126_bio6.tif")

gfdl_2011_2040_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/GFDL_ESM4/gfdl_2011_2040_126_bio7.tif")

gfdl_2011_2040_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/GFDL_ESM4/gfdl_2011_2040_126_bio12.tif")

gfdl_2011_2040_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/GFDL_ESM4/gfdl_2011_2040_126_bio14.tif")

gfdl_2011_2040_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/GFDL_ESM4/gfdl_2011_2040_126_bio15.tif")

gfdl_2011_2040_126_bio1 <- terra::mask(gfdl_2011_2040_126_bio1, indomalay_region)
gfdl_2011_2040_126_bio2 <- terra::mask(gfdl_2011_2040_126_bio2, indomalay_region)
gfdl_2011_2040_126_bio4 <- terra::mask(gfdl_2011_2040_126_bio4, indomalay_region)
gfdl_2011_2040_126_bio6 <- terra::mask(gfdl_2011_2040_126_bio6, indomalay_region)
gfdl_2011_2040_126_bio7 <- terra::mask(gfdl_2011_2040_126_bio7, indomalay_region)
gfdl_2011_2040_126_bio12 <- terra::mask(gfdl_2011_2040_126_bio12, indomalay_region)
gfdl_2011_2040_126_bio14 <- terra::mask(gfdl_2011_2040_126_bio14, indomalay_region)
gfdl_2011_2040_126_bio15 <- terra::mask(gfdl_2011_2040_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(gfdl_2011_2040_126_bio1)
plot(gfdl_2011_2040_126_bio2)
plot(gfdl_2011_2040_126_bio4)
plot(gfdl_2011_2040_126_bio6)
plot(gfdl_2011_2040_126_bio7)
plot(gfdl_2011_2040_126_bio12)
plot(gfdl_2011_2040_126_bio14)
plot(gfdl_2011_2040_126_bio15)
```

## IPSL_CM6A_LR ##
DONE
```{r}
ipsl_2011_2040_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/IPSL_CM6A_LR/ipsl_2011_2040_126_bio1.tif")

ipsl_2011_2040_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/IPSL_CM6A_LR/ipsl_2011_2040_126_bio2.tif")

ipsl_2011_2040_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/IPSL_CM6A_LR/ipsl_2011_2040_126_bio4.tif")

ipsl_2011_2040_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/IPSL_CM6A_LR/ipsl_2011_2040_126_bio6.tif")

ipsl_2011_2040_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/IPSL_CM6A_LR/ipsl_2011_2040_126_bio7.tif")

ipsl_2011_2040_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/IPSL_CM6A_LR/ipsl_2011_2040_126_bio12.tif")

ipsl_2011_2040_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/IPSL_CM6A_LR/ipsl_2011_2040_126_bio14.tif")

ipsl_2011_2040_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/IPSL_CM6A_LR/ipsl_2011_2040_126_bio15.tif")

ipsl_2011_2040_126_bio1 <- terra::mask(ipsl_2011_2040_126_bio1, indomalay_region)
ipsl_2011_2040_126_bio2 <- terra::mask(ipsl_2011_2040_126_bio2, indomalay_region)
ipsl_2011_2040_126_bio4 <- terra::mask(ipsl_2011_2040_126_bio4, indomalay_region)
ipsl_2011_2040_126_bio6 <- terra::mask(ipsl_2011_2040_126_bio6, indomalay_region)
ipsl_2011_2040_126_bio7 <- terra::mask(ipsl_2011_2040_126_bio7, indomalay_region)
ipsl_2011_2040_126_bio12 <- terra::mask(ipsl_2011_2040_126_bio12, indomalay_region)
ipsl_2011_2040_126_bio14 <- terra::mask(ipsl_2011_2040_126_bio14, indomalay_region)
ipsl_2011_2040_126_bio15 <- terra::mask(ipsl_2011_2040_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ipsl_2011_2040_126_bio1)
plot(ipsl_2011_2040_126_bio2)
plot(ipsl_2011_2040_126_bio4)
plot(ipsl_2011_2040_126_bio6)
plot(ipsl_2011_2040_126_bio7)
plot(ipsl_2011_2040_126_bio12)
plot(ipsl_2011_2040_126_bio14)
plot(ipsl_2011_2040_126_bio15)
```

## MPI_ESM1_2_HR ##
DONE
```{r}
mpi_2011_2040_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MPI_ESM1_2_HR/mpi_2011_2040_126_bio1.tif")

mpi_2011_2040_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MPI_ESM1_2_HR/mpi_2011_2040_126_bio2.tif")

mpi_2011_2040_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MPI_ESM1_2_HR/mpi_2011_2040_126_bio4.tif")

mpi_2011_2040_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MPI_ESM1_2_HR/mpi_2011_2040_126_bio6.tif")

mpi_2011_2040_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MPI_ESM1_2_HR/mpi_2011_2040_126_bio7.tif")

mpi_2011_2040_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MPI_ESM1_2_HR/mpi_2011_2040_126_bio12.tif")

mpi_2011_2040_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MPI_ESM1_2_HR/mpi_2011_2040_126_bio14.tif")

mpi_2011_2040_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MPI_ESM1_2_HR/mpi_2011_2040_126_bio15.tif")

mpi_2011_2040_126_bio1 <- terra::mask(mpi_2011_2040_126_bio1, indomalay_region)
mpi_2011_2040_126_bio2 <- terra::mask(mpi_2011_2040_126_bio2, indomalay_region)
mpi_2011_2040_126_bio4 <- terra::mask(mpi_2011_2040_126_bio4, indomalay_region)
mpi_2011_2040_126_bio6 <- terra::mask(mpi_2011_2040_126_bio6, indomalay_region)
mpi_2011_2040_126_bio7 <- terra::mask(mpi_2011_2040_126_bio7, indomalay_region)
mpi_2011_2040_126_bio12 <- terra::mask(mpi_2011_2040_126_bio12, indomalay_region)
mpi_2011_2040_126_bio14 <- terra::mask(mpi_2011_2040_126_bio14, indomalay_region)
mpi_2011_2040_126_bio15 <- terra::mask(mpi_2011_2040_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mpi_2011_2040_126_bio1)
plot(mpi_2011_2040_126_bio2)
plot(mpi_2011_2040_126_bio4)
plot(mpi_2011_2040_126_bio6)
plot(mpi_2011_2040_126_bio7)
plot(mpi_2011_2040_126_bio12)
plot(mpi_2011_2040_126_bio14)
plot(mpi_2011_2040_126_bio15)
```

## MRI_ESM2_0 ##
DONE
```{r}
mri_2011_2040_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MRI_ESM2_0/mri_2011_2040_126_bio1.tif") 

mri_2011_2040_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MRI_ESM2_0/mri_2011_2040_126_bio2.tif") 

mri_2011_2040_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MRI_ESM2_0/mri_2011_2040_126_bio4.tif") 

mri_2011_2040_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MRI_ESM2_0/mri_2011_2040_126_bio6.tif") 

mri_2011_2040_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MRI_ESM2_0/mri_2011_2040_126_bio7.tif") 

mri_2011_2040_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MRI_ESM2_0/mri_2011_2040_126_bio12.tif") 

mri_2011_2040_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MRI_ESM2_0/mri_2011_2040_126_bio14.tif") 

mri_2011_2040_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/MRI_ESM2_0/mri_2011_2040_126_bio15.tif") 

mri_2011_2040_126_bio1 <- terra::mask(mri_2011_2040_126_bio1, indomalay_region)
mri_2011_2040_126_bio2 <- terra::mask(mri_2011_2040_126_bio2, indomalay_region)
mri_2011_2040_126_bio4 <- terra::mask(mri_2011_2040_126_bio4, indomalay_region)
mri_2011_2040_126_bio6 <- terra::mask(mri_2011_2040_126_bio6, indomalay_region)
mri_2011_2040_126_bio7 <- terra::mask(mri_2011_2040_126_bio7, indomalay_region)
mri_2011_2040_126_bio12 <- terra::mask(mri_2011_2040_126_bio12, indomalay_region)
mri_2011_2040_126_bio14 <- terra::mask(mri_2011_2040_126_bio14, indomalay_region)
mri_2011_2040_126_bio15 <- terra::mask(mri_2011_2040_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mri_2011_2040_126_bio1)
plot(mri_2011_2040_126_bio2)
plot(mri_2011_2040_126_bio4)
plot(mri_2011_2040_126_bio6)
plot(mri_2011_2040_126_bio7)
plot(mri_2011_2040_126_bio12)
plot(mri_2011_2040_126_bio14)
plot(mri_2011_2040_126_bio15)
```

## UKESM1_0_LL ##
DONE
```{r}
ukesm_2011_2040_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/UKESM1_0_LL/ukesm_2011_2040_126_bio1.tif")

ukesm_2011_2040_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/UKESM1_0_LL/ukesm_2011_2040_126_bio2.tif")

ukesm_2011_2040_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/UKESM1_0_LL/ukesm_2011_2040_126_bio4.tif")

ukesm_2011_2040_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/UKESM1_0_LL/ukesm_2011_2040_126_bio6.tif")

ukesm_2011_2040_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/UKESM1_0_LL/ukesm_2011_2040_126_bio7.tif")

ukesm_2011_2040_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/UKESM1_0_LL/ukesm_2011_2040_126_bio12.tif")

ukesm_2011_2040_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/UKESM1_0_LL/ukesm_2011_2040_126_bio14.tif")

ukesm_2011_2040_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/126/UKESM1_0_LL/ukesm_2011_2040_126_bio15.tif")

ukesm_2011_2040_126_bio1 <- terra::mask(ukesm_2011_2040_126_bio1, indomalay_region)
ukesm_2011_2040_126_bio2 <- terra::mask(ukesm_2011_2040_126_bio2, indomalay_region)
ukesm_2011_2040_126_bio4 <- terra::mask(ukesm_2011_2040_126_bio4, indomalay_region)
ukesm_2011_2040_126_bio6 <- terra::mask(ukesm_2011_2040_126_bio6, indomalay_region)
ukesm_2011_2040_126_bio7 <- terra::mask(ukesm_2011_2040_126_bio7, indomalay_region)
ukesm_2011_2040_126_bio12 <- terra::mask(ukesm_2011_2040_126_bio12, indomalay_region)
ukesm_2011_2040_126_bio14 <- terra::mask(ukesm_2011_2040_126_bio14, indomalay_region)
ukesm_2011_2040_126_bio15 <- terra::mask(ukesm_2011_2040_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ukesm_2011_2040_126_bio1)
plot(ukesm_2011_2040_126_bio2)
plot(ukesm_2011_2040_126_bio4)
plot(ukesm_2011_2040_126_bio6)
plot(ukesm_2011_2040_126_bio7)
plot(ukesm_2011_2040_126_bio12)
plot(ukesm_2011_2040_126_bio14)
plot(ukesm_2011_2040_126_bio15)
```

############ 2011 - 2041 ############

####### 370 #######

## GFDL_ESM4 ##
DONE
```{r}
gfdl_2011_2040_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/GFDL_ESM4/gfdl_2011_2040_370_bio1.tif")

gfdl_2011_2040_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/GFDL_ESM4/gfdl_2011_2040_370_bio2.tif")

gfdl_2011_2040_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/GFDL_ESM4/gfdl_2011_2040_370_bio4.tif")

gfdl_2011_2040_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/GFDL_ESM4/gfdl_2011_2040_370_bio6.tif")

gfdl_2011_2040_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/GFDL_ESM4/gfdl_2011_2040_370_bio7.tif")

gfdl_2011_2040_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/GFDL_ESM4/gfdl_2011_2040_370_bio12.tif")

gfdl_2011_2040_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/GFDL_ESM4/gfdl_2011_2040_370_bio14.tif")

gfdl_2011_2040_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/GFDL_ESM4/gfdl_2011_2040_370_bio15.tif")

gfdl_2011_2040_370_bio1 <- terra::mask(gfdl_2011_2040_370_bio1, indomalay_region)
gfdl_2011_2040_370_bio2 <- terra::mask(gfdl_2011_2040_370_bio2, indomalay_region)
gfdl_2011_2040_370_bio4 <- terra::mask(gfdl_2011_2040_370_bio4, indomalay_region)
gfdl_2011_2040_370_bio6 <- terra::mask(gfdl_2011_2040_370_bio6, indomalay_region)
gfdl_2011_2040_370_bio7 <- terra::mask(gfdl_2011_2040_370_bio7, indomalay_region)
gfdl_2011_2040_370_bio12 <- terra::mask(gfdl_2011_2040_370_bio12, indomalay_region)
gfdl_2011_2040_370_bio14 <- terra::mask(gfdl_2011_2040_370_bio14, indomalay_region)
gfdl_2011_2040_370_bio15 <- terra::mask(gfdl_2011_2040_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(gfdl_2011_2040_370_bio1)
plot(gfdl_2011_2040_370_bio2)
plot(gfdl_2011_2040_370_bio4)
plot(gfdl_2011_2040_370_bio6)
plot(gfdl_2011_2040_370_bio7)
plot(gfdl_2011_2040_370_bio12)
plot(gfdl_2011_2040_370_bio14)
plot(gfdl_2011_2040_370_bio15)
```

## IPSL_CM6A_LR ##
DONE
```{r}
ipsl_2011_2040_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/IPSL_CM6A_LR/ipsl_2011_2040_370_bio1.tif")

ipsl_2011_2040_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/IPSL_CM6A_LR/ipsl_2011_2040_370_bio2.tif")

ipsl_2011_2040_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/IPSL_CM6A_LR/ipsl_2011_2040_370_bio4.tif")

ipsl_2011_2040_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/IPSL_CM6A_LR/ipsl_2011_2040_370_bio6.tif")

ipsl_2011_2040_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/IPSL_CM6A_LR/ipsl_2011_2040_370_bio7.tif")

ipsl_2011_2040_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/IPSL_CM6A_LR/ipsl_2011_2040_370_bio12.tif")

ipsl_2011_2040_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/IPSL_CM6A_LR/ipsl_2011_2040_370_bio14.tif")

ipsl_2011_2040_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/IPSL_CM6A_LR/ipsl_2011_2040_370_bio15.tif")

ipsl_2011_2040_370_bio1 <- terra::mask(ipsl_2011_2040_370_bio1, indomalay_region)
ipsl_2011_2040_370_bio2 <- terra::mask(ipsl_2011_2040_370_bio2, indomalay_region)
ipsl_2011_2040_370_bio4 <- terra::mask(ipsl_2011_2040_370_bio4, indomalay_region)
ipsl_2011_2040_370_bio6 <- terra::mask(ipsl_2011_2040_370_bio6, indomalay_region)
ipsl_2011_2040_370_bio7 <- terra::mask(ipsl_2011_2040_370_bio7, indomalay_region)
ipsl_2011_2040_370_bio12 <- terra::mask(ipsl_2011_2040_370_bio12, indomalay_region)
ipsl_2011_2040_370_bio14 <- terra::mask(ipsl_2011_2040_370_bio14, indomalay_region)
ipsl_2011_2040_370_bio15 <- terra::mask(ipsl_2011_2040_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ipsl_2011_2040_370_bio1)
plot(ipsl_2011_2040_370_bio2)
plot(ipsl_2011_2040_370_bio4)
plot(ipsl_2011_2040_370_bio6)
plot(ipsl_2011_2040_370_bio7)
plot(ipsl_2011_2040_370_bio12)
plot(ipsl_2011_2040_370_bio14)
plot(ipsl_2011_2040_370_bio15)
```

## MPI_ESM1_2_HR ##
DONE
```{r}
mpi_2011_2040_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MPI_ESM1_2_HR/mpi_2011_2040_370_bio1.tif")

mpi_2011_2040_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MPI_ESM1_2_HR/mpi_2011_2040_370_bio2.tif")

mpi_2011_2040_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MPI_ESM1_2_HR/mpi_2011_2040_370_bio4.tif")

mpi_2011_2040_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MPI_ESM1_2_HR/mpi_2011_2040_370_bio6.tif")

mpi_2011_2040_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MPI_ESM1_2_HR/mpi_2011_2040_370_bio7.tif")

mpi_2011_2040_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MPI_ESM1_2_HR/mpi_2011_2040_370_bio12.tif")

mpi_2011_2040_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MPI_ESM1_2_HR/mpi_2011_2040_370_bio14.tif")

mpi_2011_2040_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MPI_ESM1_2_HR/mpi_2011_2040_370_bio15.tif")

mpi_2011_2040_370_bio1 <- terra::mask(mpi_2011_2040_370_bio1, indomalay_region)
mpi_2011_2040_370_bio2 <- terra::mask(mpi_2011_2040_370_bio2, indomalay_region)
mpi_2011_2040_370_bio4 <- terra::mask(mpi_2011_2040_370_bio4, indomalay_region)
mpi_2011_2040_370_bio6 <- terra::mask(mpi_2011_2040_370_bio6, indomalay_region)
mpi_2011_2040_370_bio7 <- terra::mask(mpi_2011_2040_370_bio7, indomalay_region)
mpi_2011_2040_370_bio12 <- terra::mask(mpi_2011_2040_370_bio12, indomalay_region)
mpi_2011_2040_370_bio14 <- terra::mask(mpi_2011_2040_370_bio14, indomalay_region)
mpi_2011_2040_370_bio15 <- terra::mask(mpi_2011_2040_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mpi_2011_2040_370_bio1)
plot(mpi_2011_2040_370_bio2)
plot(mpi_2011_2040_370_bio4)
plot(mpi_2011_2040_370_bio6)
plot(mpi_2011_2040_370_bio7)
plot(mpi_2011_2040_370_bio12)
plot(mpi_2011_2040_370_bio14)
plot(mpi_2011_2040_370_bio15)
```

## MRI_ESM2_0 ##
DONE
```{r}
mri_2011_2040_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MRI_ESM2_0/mri_2011_2040_370_bio1.tif")

mri_2011_2040_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MRI_ESM2_0/mri_2011_2040_370_bio2.tif")

mri_2011_2040_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MRI_ESM2_0/mri_2011_2040_370_bio4.tif")

mri_2011_2040_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MRI_ESM2_0/mri_2011_2040_370_bio6.tif")

mri_2011_2040_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MRI_ESM2_0/mri_2011_2040_370_bio7.tif")

mri_2011_2040_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MRI_ESM2_0/mri_2011_2040_370_bio12.tif")

mri_2011_2040_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MRI_ESM2_0/mri_2011_2040_370_bio14.tif")

mri_2011_2040_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/MRI_ESM2_0/mri_2011_2040_370_bio15.tif")

mri_2011_2040_370_bio1 <- terra::mask(mri_2011_2040_370_bio1, indomalay_region)
mri_2011_2040_370_bio2 <- terra::mask(mri_2011_2040_370_bio2, indomalay_region)
mri_2011_2040_370_bio4 <- terra::mask(mri_2011_2040_370_bio4, indomalay_region)
mri_2011_2040_370_bio6 <- terra::mask(mri_2011_2040_370_bio6, indomalay_region)
mri_2011_2040_370_bio7 <- terra::mask(mri_2011_2040_370_bio7, indomalay_region)
mri_2011_2040_370_bio12 <- terra::mask(mri_2011_2040_370_bio12, indomalay_region)
mri_2011_2040_370_bio14 <- terra::mask(mri_2011_2040_370_bio14, indomalay_region)
mri_2011_2040_370_bio15 <- terra::mask(mri_2011_2040_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mri_2011_2040_370_bio1)
plot(mri_2011_2040_370_bio2)
plot(mri_2011_2040_370_bio4)
plot(mri_2011_2040_370_bio6)
plot(mri_2011_2040_370_bio7)
plot(mri_2011_2040_370_bio12)
plot(mri_2011_2040_370_bio14)
plot(mri_2011_2040_370_bio15)
```

## UKESM1_0_LL ##
DONE
```{r}
ukesm_2011_2040_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/UKESM1_0_LL/ukesm_2011_2040_370_bio1.tif")

ukesm_2011_2040_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/UKESM1_0_LL/ukesm_2011_2040_370_bio2.tif")

ukesm_2011_2040_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/UKESM1_0_LL/ukesm_2011_2040_370_bio4.tif")

ukesm_2011_2040_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/UKESM1_0_LL/ukesm_2011_2040_370_bio6.tif")

ukesm_2011_2040_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/UKESM1_0_LL/ukesm_2011_2040_370_bio7.tif")

ukesm_2011_2040_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/UKESM1_0_LL/ukesm_2011_2040_370_bio12.tif")

ukesm_2011_2040_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/UKESM1_0_LL/ukesm_2011_2040_370_bio14.tif")

ukesm_2011_2040_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/370/UKESM1_0_LL/ukesm_2011_2040_370_bio15.tif")

ukesm_2011_2040_370_bio1 <- terra::mask(ukesm_2011_2040_370_bio1, indomalay_region)
ukesm_2011_2040_370_bio2 <- terra::mask(ukesm_2011_2040_370_bio2, indomalay_region)
ukesm_2011_2040_370_bio4 <- terra::mask(ukesm_2011_2040_370_bio4, indomalay_region)
ukesm_2011_2040_370_bio6 <- terra::mask(ukesm_2011_2040_370_bio6, indomalay_region)
ukesm_2011_2040_370_bio7 <- terra::mask(ukesm_2011_2040_370_bio7, indomalay_region)
ukesm_2011_2040_370_bio12 <- terra::mask(ukesm_2011_2040_370_bio12, indomalay_region)
ukesm_2011_2040_370_bio14 <- terra::mask(ukesm_2011_2040_370_bio14, indomalay_region)
ukesm_2011_2040_370_bio15 <- terra::mask(ukesm_2011_2040_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ukesm_2011_2040_370_bio1)
plot(ukesm_2011_2040_370_bio2)
plot(ukesm_2011_2040_370_bio4)
plot(ukesm_2011_2040_370_bio6)
plot(ukesm_2011_2040_370_bio7)
plot(ukesm_2011_2040_370_bio12)
plot(ukesm_2011_2040_370_bio14)
plot(ukesm_2011_2040_370_bio15)
```

############ 2011 - 2041 ############ 

###### 585 #######

## GFDL_ESM4 ##
DONE
```{r}
gfdl_2011_2040_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/GFDL_ESM4/gfdl_2011_2040_585_bio1.tif")

gfdl_2011_2040_585_bio1 <- terra::mask(gfdl_2011_2040_585_bio1, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(gfdl_2011_2040_585_bio1)
```

## IPSL_CM6A_LR ##
DONE
```{r}
ipsl_2011_2040_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/IPSL_CM6A_LR/ipsl_2011_2040_585_bio1.tif")

ipsl_2011_2040_585_bio1 <- terra::mask(ipsl_2011_2040_585_bio1, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ipsl_2011_2040_585_bio1)
```

## MPI_ESM1_2_HR ##
DONE
```{r}
mpi_2011_2040_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MPI_ESM1_2_HR/mpi_2011_2040_585_bio1.tif")

mpi_2011_2040_585_bio1 <- terra::mask(mpi_2011_2040_585_bio1, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mpi_2011_2040_585_bio1)
```

## MRI_ESM2_0 ##
DONE
```{r}
mri_2011_2040_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MRI_ESM2_0/mri_2011_2040_585_bio1.tif")

mri_2011_2040_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MRI_ESM2_0/mri_2011_2040_585_bio2.tif")

mri_2011_2040_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MRI_ESM2_0/mri_2011_2040_585_bio4.tif")

mri_2011_2040_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MRI_ESM2_0/mri_2011_2040_585_bio6.tif")

mri_2011_2040_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MRI_ESM2_0/mri_2011_2040_585_bio7.tif")

mri_2011_2040_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MRI_ESM2_0/mri_2011_2040_585_bio12.tif")

mri_2011_2040_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MRI_ESM2_0/mri_2011_2040_585_bio14.tif")

mri_2011_2040_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/MRI_ESM2_0/mri_2011_2040_585_bio15.tif")

mri_2011_2040_585_bio1 <- terra::mask(mri_2011_2040_585_bio1, indomalay_region)
mri_2011_2040_585_bio2 <- terra::mask(mri_2011_2040_585_bio2, indomalay_region)
mri_2011_2040_585_bio4 <- terra::mask(mri_2011_2040_585_bio4, indomalay_region)
mri_2011_2040_585_bio6 <- terra::mask(mri_2011_2040_585_bio6, indomalay_region)
mri_2011_2040_585_bio7 <- terra::mask(mri_2011_2040_585_bio7, indomalay_region)
mri_2011_2040_585_bio12 <- terra::mask(mri_2011_2040_585_bio12, indomalay_region)
mri_2011_2040_585_bio14 <- terra::mask(mri_2011_2040_585_bio14, indomalay_region)
mri_2011_2040_585_bio15 <- terra::mask(mri_2011_2040_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mri_2011_2040_585_bio1)
plot(mri_2011_2040_585_bio2)
plot(mri_2011_2040_585_bio4)
plot(mri_2011_2040_585_bio6)
plot(mri_2011_2040_585_bio7)
plot(mri_2011_2040_585_bio12)
plot(mri_2011_2040_585_bio14)
plot(mri_2011_2040_585_bio15)
```

## UKESM1_0_LL ##
DONE
```{r}
ukesm_2011_2040_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/UKESM1_0_LL/ukesm_2011_2040_585_bio1.tif")

ukesm_2011_2040_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/UKESM1_0_LL/ukesm_2011_2040_585_bio2.tif")

ukesm_2011_2040_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/UKESM1_0_LL/ukesm_2011_2040_585_bio4.tif")

ukesm_2011_2040_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/UKESM1_0_LL/ukesm_2011_2040_585_bio6.tif")

ukesm_2011_2040_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/UKESM1_0_LL/ukesm_2011_2040_585_bio7.tif")

ukesm_2011_2040_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/UKESM1_0_LL/ukesm_2011_2040_585_bio12.tif")

ukesm_2011_2040_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/UKESM1_0_LL/ukesm_2011_2040_585_bio14.tif")

ukesm_2011_2040_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2011_2040/585/UKESM1_0_LL/ukesm_2011_2040_585_bio15.tif")

ukesm_2011_2040_585_bio1 <- terra::mask(ukesm_2011_2040_585_bio1, indomalay_region)
ukesm_2011_2040_585_bio2 <- terra::mask(ukesm_2011_2040_585_bio2, indomalay_region)
ukesm_2011_2040_585_bio4 <- terra::mask(ukesm_2011_2040_585_bio4, indomalay_region)
ukesm_2011_2040_585_bio6 <- terra::mask(ukesm_2011_2040_585_bio6, indomalay_region)
ukesm_2011_2040_585_bio7 <- terra::mask(ukesm_2011_2040_585_bio7, indomalay_region)
ukesm_2011_2040_585_bio12 <- terra::mask(ukesm_2011_2040_585_bio12, indomalay_region)
ukesm_2011_2040_585_bio14 <- terra::mask(ukesm_2011_2040_585_bio14, indomalay_region)
ukesm_2011_2040_585_bio15 <- terra::mask(ukesm_2011_2040_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ukesm_2011_2040_585_bio1)
plot(ukesm_2011_2040_585_bio2)
plot(ukesm_2011_2040_585_bio4)
plot(ukesm_2011_2040_585_bio6)
plot(ukesm_2011_2040_585_bio7)
plot(ukesm_2011_2040_585_bio12)
plot(ukesm_2011_2040_585_bio14)
plot(ukesm_2011_2040_585_bio15)
```

############ 2041 - 2070 ############

####### 126 #######

## GFDL_ESM4 ##
DONE
```{r}
gfdl_2041_2070_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/GFDL_ESM4/gfdl_2041_2070_126_bio1.tif")

gfdl_2041_2070_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/GFDL_ESM4/gfdl_2041_2070_126_bio2.tif")

gfdl_2041_2070_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/GFDL_ESM4/gfdl_2041_2070_126_bio4.tif")

gfdl_2041_2070_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/GFDL_ESM4/gfdl_2041_2070_126_bio6.tif")

gfdl_2041_2070_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/GFDL_ESM4/gfdl_2041_2070_126_bio7.tif")

gfdl_2041_2070_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/GFDL_ESM4/gfdl_2041_2070_126_bio12.tif")

gfdl_2041_2070_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/GFDL_ESM4/gfdl_2041_2070_126_bio14.tif")

gfdl_2041_2070_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/GFDL_ESM4/gfdl_2041_2070_126_bio15.tif")

gfdl_2041_2070_126_bio1 <- terra::mask(gfdl_2041_2070_126_bio1, indomalay_region)
gfdl_2041_2070_126_bio2 <- terra::mask(gfdl_2041_2070_126_bio2, indomalay_region)
gfdl_2041_2070_126_bio4 <- terra::mask(gfdl_2041_2070_126_bio4, indomalay_region)
gfdl_2041_2070_126_bio6 <- terra::mask(gfdl_2041_2070_126_bio6, indomalay_region)
gfdl_2041_2070_126_bio7 <- terra::mask(gfdl_2041_2070_126_bio7, indomalay_region)
gfdl_2041_2070_126_bio12 <- terra::mask(gfdl_2041_2070_126_bio12, indomalay_region)
gfdl_2041_2070_126_bio14 <- terra::mask(gfdl_2041_2070_126_bio14, indomalay_region)
gfdl_2041_2070_126_bio15 <- terra::mask(gfdl_2041_2070_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(gfdl_2041_2070_126_bio1)
plot(gfdl_2041_2070_126_bio2)
plot(gfdl_2041_2070_126_bio4)
plot(gfdl_2041_2070_126_bio6)
plot(gfdl_2041_2070_126_bio7)
plot(gfdl_2041_2070_126_bio12)
plot(gfdl_2041_2070_126_bio14)
plot(gfdl_2041_2070_126_bio15)
```

## IPSL_CM6A_LR ##
DONE
```{r}
ipsl_2041_2070_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/IPSL_CM6A_LR/ipsl_2041_2070_126_bio1.tif")

ipsl_2041_2070_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/IPSL_CM6A_LR/ipsl_2041_2070_126_bio2.tif")

ipsl_2041_2070_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/IPSL_CM6A_LR/ipsl_2041_2070_126_bio4.tif")

ipsl_2041_2070_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/IPSL_CM6A_LR/ipsl_2041_2070_126_bio6.tif")

ipsl_2041_2070_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/IPSL_CM6A_LR/ipsl_2041_2070_126_bio7.tif")

ipsl_2041_2070_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/IPSL_CM6A_LR/ipsl_2041_2070_126_bio12.tif")

ipsl_2041_2070_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/IPSL_CM6A_LR/ipsl_2041_2070_126_bio14.tif")

ipsl_2041_2070_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/IPSL_CM6A_LR/ipsl_2041_2070_126_bio15.tif")

ipsl_2041_2070_126_bio1 <- terra::mask(ipsl_2041_2070_126_bio1, indomalay_region)
ipsl_2041_2070_126_bio2 <- terra::mask(ipsl_2041_2070_126_bio2, indomalay_region)
ipsl_2041_2070_126_bio4 <- terra::mask(ipsl_2041_2070_126_bio4, indomalay_region)
ipsl_2041_2070_126_bio6 <- terra::mask(ipsl_2041_2070_126_bio6, indomalay_region)
ipsl_2041_2070_126_bio7 <- terra::mask(ipsl_2041_2070_126_bio7, indomalay_region)
ipsl_2041_2070_126_bio12 <- terra::mask(ipsl_2041_2070_126_bio12, indomalay_region)
ipsl_2041_2070_126_bio14 <- terra::mask(ipsl_2041_2070_126_bio14, indomalay_region)
ipsl_2041_2070_126_bio15 <- terra::mask(ipsl_2041_2070_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ipsl_2041_2070_126_bio1)
plot(ipsl_2041_2070_126_bio2)
plot(ipsl_2041_2070_126_bio4)
plot(ipsl_2041_2070_126_bio6)
plot(ipsl_2041_2070_126_bio7)
plot(ipsl_2041_2070_126_bio12)
plot(ipsl_2041_2070_126_bio14)
plot(ipsl_2041_2070_126_bio15)
```

## MPI_ESM1_2_HR ##
DONE
```{r}
mpi_2041_2070_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MPI_ESM1_2_HR/mpi_2041_2070_126_bio1.tif")

mpi_2041_2070_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MPI_ESM1_2_HR/mpi_2041_2070_126_bio2.tif")

mpi_2041_2070_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MPI_ESM1_2_HR/mpi_2041_2070_126_bio4.tif")

mpi_2041_2070_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MPI_ESM1_2_HR/mpi_2041_2070_126_bio6.tif")

mpi_2041_2070_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MPI_ESM1_2_HR/mpi_2041_2070_126_bio7.tif")

mpi_2041_2070_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MPI_ESM1_2_HR/mpi_2041_2070_126_bio12.tif")

mpi_2041_2070_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MPI_ESM1_2_HR/mpi_2041_2070_126_bio14.tif")

mpi_2041_2070_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MPI_ESM1_2_HR/mpi_2041_2070_126_bio15.tif")

mpi_2041_2070_126_bio1 <- terra::mask(mpi_2041_2070_126_bio1, indomalay_region)
mpi_2041_2070_126_bio2 <- terra::mask(mpi_2041_2070_126_bio2, indomalay_region)
mpi_2041_2070_126_bio4 <- terra::mask(mpi_2041_2070_126_bio4, indomalay_region)
mpi_2041_2070_126_bio6 <- terra::mask(mpi_2041_2070_126_bio6, indomalay_region)
mpi_2041_2070_126_bio7 <- terra::mask(mpi_2041_2070_126_bio7, indomalay_region)
mpi_2041_2070_126_bio12 <- terra::mask(mpi_2041_2070_126_bio12, indomalay_region)
mpi_2041_2070_126_bio14 <- terra::mask(mpi_2041_2070_126_bio14, indomalay_region)
mpi_2041_2070_126_bio15 <- terra::mask(mpi_2041_2070_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mpi_2041_2070_126_bio1)
plot(mpi_2041_2070_126_bio2)
plot(mpi_2041_2070_126_bio4)
plot(mpi_2041_2070_126_bio6)
plot(mpi_2041_2070_126_bio7)
plot(mpi_2041_2070_126_bio12)
plot(mpi_2041_2070_126_bio14)
plot(mpi_2041_2070_126_bio15)
```

## MRI_ESM2_0 ##
DONE
```{r}
mri_2041_2070_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MRI_ESM2_0/mri_2041_2070_126_bio1.tif") 

mri_2041_2070_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MRI_ESM2_0/mri_2041_2070_126_bio2.tif") 

mri_2041_2070_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MRI_ESM2_0/mri_2041_2070_126_bio4.tif") 

mri_2041_2070_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MRI_ESM2_0/mri_2041_2070_126_bio6.tif") 

mri_2041_2070_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MRI_ESM2_0/mri_2041_2070_126_bio7.tif") 

mri_2041_2070_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MRI_ESM2_0/mri_2041_2070_126_bio12.tif") 

mri_2041_2070_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MRI_ESM2_0/mri_2041_2070_126_bio14.tif") 

mri_2041_2070_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/MRI_ESM2_0/mri_2041_2070_126_bio15.tif") 

mri_2041_2070_126_bio1 <- terra::mask(mri_2041_2070_126_bio1, indomalay_region)
mri_2041_2070_126_bio2 <- terra::mask(mri_2041_2070_126_bio2, indomalay_region)
mri_2041_2070_126_bio4 <- terra::mask(mri_2041_2070_126_bio4, indomalay_region)
mri_2041_2070_126_bio6 <- terra::mask(mri_2041_2070_126_bio6, indomalay_region)
mri_2041_2070_126_bio7 <- terra::mask(mri_2041_2070_126_bio7, indomalay_region)
mri_2041_2070_126_bio12 <- terra::mask(mri_2041_2070_126_bio12, indomalay_region)
mri_2041_2070_126_bio14 <- terra::mask(mri_2041_2070_126_bio14, indomalay_region)
mri_2041_2070_126_bio15 <- terra::mask(mri_2041_2070_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mri_2041_2070_126_bio1)
plot(mri_2041_2070_126_bio2)
plot(mri_2041_2070_126_bio4)
plot(mri_2041_2070_126_bio6)
plot(mri_2041_2070_126_bio7)
plot(mri_2041_2070_126_bio12)
plot(mri_2041_2070_126_bio14)
plot(mri_2041_2070_126_bio15)
```

## UKESM1_0_LL ##
DONE
```{r}
ukesm_2041_2070_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/UKESM1_0_LL/ukesm_2041_2070_126_bio1.tif")

ukesm_2041_2070_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/UKESM1_0_LL/ukesm_2041_2070_126_bio2.tif")

ukesm_2041_2070_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/UKESM1_0_LL/ukesm_2041_2070_126_bio4.tif")

ukesm_2041_2070_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/UKESM1_0_LL/ukesm_2041_2070_126_bio6.tif")

ukesm_2041_2070_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/UKESM1_0_LL/ukesm_2041_2070_126_bio7.tif")

ukesm_2041_2070_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/UKESM1_0_LL/ukesm_2041_2070_126_bio12.tif")

ukesm_2041_2070_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/UKESM1_0_LL/ukesm_2041_2070_126_bio14.tif")

ukesm_2041_2070_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/126/UKESM1_0_LL/ukesm_2041_2070_126_bio15.tif")

ukesm_2041_2070_126_bio1 <- terra::mask(ukesm_2041_2070_126_bio1, indomalay_region)
ukesm_2041_2070_126_bio2 <- terra::mask(ukesm_2041_2070_126_bio2, indomalay_region)
ukesm_2041_2070_126_bio4 <- terra::mask(ukesm_2041_2070_126_bio4, indomalay_region)
ukesm_2041_2070_126_bio6 <- terra::mask(ukesm_2041_2070_126_bio6, indomalay_region)
ukesm_2041_2070_126_bio7 <- terra::mask(ukesm_2041_2070_126_bio7, indomalay_region)
ukesm_2041_2070_126_bio12 <- terra::mask(ukesm_2041_2070_126_bio12, indomalay_region)
ukesm_2041_2070_126_bio14 <- terra::mask(ukesm_2041_2070_126_bio14, indomalay_region)
ukesm_2041_2070_126_bio15 <- terra::mask(ukesm_2041_2070_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ukesm_2041_2070_126_bio1)
plot(ukesm_2041_2070_126_bio2)
plot(ukesm_2041_2070_126_bio4)
plot(ukesm_2041_2070_126_bio6)
plot(ukesm_2041_2070_126_bio7)
plot(ukesm_2041_2070_126_bio12)
plot(ukesm_2041_2070_126_bio14)
plot(ukesm_2041_2070_126_bio15)
```

############ 2041 - 2070 ############

####### 370 #######

## GFDL_ESM4 ##
DONE
```{r}
gfdl_2041_2070_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/GFDL_ESM4/gfdl_2041_2070_370_bio1.tif")

gfdl_2041_2070_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/GFDL_ESM4/gfdl_2041_2070_370_bio2.tif")

gfdl_2041_2070_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/GFDL_ESM4/gfdl_2041_2070_370_bio4.tif")

gfdl_2041_2070_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/GFDL_ESM4/gfdl_2041_2070_370_bio6.tif")

gfdl_2041_2070_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/GFDL_ESM4/gfdl_2041_2070_370_bio7.tif")

gfdl_2041_2070_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/GFDL_ESM4/gfdl_2041_2070_370_bio12.tif")

gfdl_2041_2070_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/GFDL_ESM4/gfdl_2041_2070_370_bio14.tif")

gfdl_2041_2070_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/GFDL_ESM4/gfdl_2041_2070_370_bio15.tif")

gfdl_2041_2070_370_bio1 <- terra::mask(gfdl_2041_2070_370_bio1, indomalay_region)
gfdl_2041_2070_370_bio2 <- terra::mask(gfdl_2041_2070_370_bio2, indomalay_region)
gfdl_2041_2070_370_bio4 <- terra::mask(gfdl_2041_2070_370_bio4, indomalay_region)
gfdl_2041_2070_370_bio6 <- terra::mask(gfdl_2041_2070_370_bio6, indomalay_region)
gfdl_2041_2070_370_bio7 <- terra::mask(gfdl_2041_2070_370_bio7, indomalay_region)
gfdl_2041_2070_370_bio12 <- terra::mask(gfdl_2041_2070_370_bio12, indomalay_region)
gfdl_2041_2070_370_bio14 <- terra::mask(gfdl_2041_2070_370_bio14, indomalay_region)
gfdl_2041_2070_370_bio15 <- terra::mask(gfdl_2041_2070_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(gfdl_2041_2070_370_bio1)
plot(gfdl_2041_2070_370_bio2)
plot(gfdl_2041_2070_370_bio4)
plot(gfdl_2041_2070_370_bio6)
plot(gfdl_2041_2070_370_bio7)
plot(gfdl_2041_2070_370_bio12)
plot(gfdl_2041_2070_370_bio14)
plot(gfdl_2041_2070_370_bio15)
```

## IPSL_CM6A_LR ##
DONE
```{r}
ipsl_2041_2070_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/IPSL_CM6A_LR/ipsl_2041_2070_370_bio1.tif")

ipsl_2041_2070_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/IPSL_CM6A_LR/ipsl_2041_2070_370_bio2.tif")

ipsl_2041_2070_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/IPSL_CM6A_LR/ipsl_2041_2070_370_bio4.tif")

ipsl_2041_2070_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/IPSL_CM6A_LR/ipsl_2041_2070_370_bio6.tif")

ipsl_2041_2070_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/IPSL_CM6A_LR/ipsl_2041_2070_370_bio7.tif")

ipsl_2041_2070_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/IPSL_CM6A_LR/ipsl_2041_2070_370_bio12.tif")

ipsl_2041_2070_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/IPSL_CM6A_LR/ipsl_2041_2070_370_bio14.tif")

ipsl_2041_2070_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/IPSL_CM6A_LR/ipsl_2041_2070_370_bio15.tif")

ipsl_2041_2070_370_bio1 <- terra::mask(ipsl_2041_2070_370_bio1, indomalay_region)
ipsl_2041_2070_370_bio2 <- terra::mask(ipsl_2041_2070_370_bio2, indomalay_region)
ipsl_2041_2070_370_bio4 <- terra::mask(ipsl_2041_2070_370_bio4, indomalay_region)
ipsl_2041_2070_370_bio6 <- terra::mask(ipsl_2041_2070_370_bio6, indomalay_region)
ipsl_2041_2070_370_bio7 <- terra::mask(ipsl_2041_2070_370_bio7, indomalay_region)
ipsl_2041_2070_370_bio12 <- terra::mask(ipsl_2041_2070_370_bio12, indomalay_region)
ipsl_2041_2070_370_bio14 <- terra::mask(ipsl_2041_2070_370_bio14, indomalay_region)
ipsl_2041_2070_370_bio15 <- terra::mask(ipsl_2041_2070_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ipsl_2041_2070_370_bio1)
plot(ipsl_2041_2070_370_bio2)
plot(ipsl_2041_2070_370_bio4)
plot(ipsl_2041_2070_370_bio6)
plot(ipsl_2041_2070_370_bio7)
plot(ipsl_2041_2070_370_bio12)
plot(ipsl_2041_2070_370_bio14)
plot(ipsl_2041_2070_370_bio15)
```

## MPI_ESM1_2_HR ##
DONE
```{r}
mpi_2041_2070_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MPI_ESM1_2_HR/mpi_2041_2070_370_bio1.tif")

mpi_2041_2070_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MPI_ESM1_2_HR/mpi_2041_2070_370_bio2.tif")

mpi_2041_2070_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MPI_ESM1_2_HR/mpi_2041_2070_370_bio4.tif")

mpi_2041_2070_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MPI_ESM1_2_HR/mpi_2041_2070_370_bio6.tif")

mpi_2041_2070_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MPI_ESM1_2_HR/mpi_2041_2070_370_bio7.tif")

mpi_2041_2070_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MPI_ESM1_2_HR/mpi_2041_2070_370_bio12.tif")

mpi_2041_2070_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MPI_ESM1_2_HR/mpi_2041_2070_370_bio14.tif")

mpi_2041_2070_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MPI_ESM1_2_HR/mpi_2041_2070_370_bio15.tif")

mpi_2041_2070_370_bio1 <- terra::mask(mpi_2041_2070_370_bio1, indomalay_region)
mpi_2041_2070_370_bio2 <- terra::mask(mpi_2041_2070_370_bio2, indomalay_region)
mpi_2041_2070_370_bio4 <- terra::mask(mpi_2041_2070_370_bio4, indomalay_region)
mpi_2041_2070_370_bio6 <- terra::mask(mpi_2041_2070_370_bio6, indomalay_region)
mpi_2041_2070_370_bio7 <- terra::mask(mpi_2041_2070_370_bio7, indomalay_region)
mpi_2041_2070_370_bio12 <- terra::mask(mpi_2041_2070_370_bio12, indomalay_region)
mpi_2041_2070_370_bio14 <- terra::mask(mpi_2041_2070_370_bio14, indomalay_region)
mpi_2041_2070_370_bio15 <- terra::mask(mpi_2041_2070_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mpi_2041_2070_370_bio1)
plot(mpi_2041_2070_370_bio2)
plot(mpi_2041_2070_370_bio4)
plot(mpi_2041_2070_370_bio6)
plot(mpi_2041_2070_370_bio7)
plot(mpi_2041_2070_370_bio12)
plot(mpi_2041_2070_370_bio14)
plot(mpi_2041_2070_370_bio15)
```

## MRI_ESM2_0 ##
DONE
```{r}
mri_2041_2070_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MRI_ESM2_0/mri_2041_2070_370_bio1.tif")

mri_2041_2070_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MRI_ESM2_0/mri_2041_2070_370_bio2.tif")

mri_2041_2070_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MRI_ESM2_0/mri_2041_2070_370_bio4.tif")

mri_2041_2070_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MRI_ESM2_0/mri_2041_2070_370_bio6.tif")

mri_2041_2070_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MRI_ESM2_0/mri_2041_2070_370_bio7.tif")

mri_2041_2070_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MRI_ESM2_0/mri_2041_2070_370_bio12.tif")

mri_2041_2070_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MRI_ESM2_0/mri_2041_2070_370_bio14.tif")

mri_2041_2070_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/MRI_ESM2_0/mri_2041_2070_370_bio15.tif")

mri_2041_2070_370_bio1 <- terra::mask(mri_2041_2070_370_bio1, indomalay_region)
mri_2041_2070_370_bio2 <- terra::mask(mri_2041_2070_370_bio2, indomalay_region)
mri_2041_2070_370_bio4 <- terra::mask(mri_2041_2070_370_bio4, indomalay_region)
mri_2041_2070_370_bio6 <- terra::mask(mri_2041_2070_370_bio6, indomalay_region)
mri_2041_2070_370_bio7 <- terra::mask(mri_2041_2070_370_bio7, indomalay_region)
mri_2041_2070_370_bio12 <- terra::mask(mri_2041_2070_370_bio12, indomalay_region)
mri_2041_2070_370_bio14 <- terra::mask(mri_2041_2070_370_bio14, indomalay_region)
mri_2041_2070_370_bio15 <- terra::mask(mri_2041_2070_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mri_2041_2070_370_bio1)
plot(mri_2041_2070_370_bio2)
plot(mri_2041_2070_370_bio4)
plot(mri_2041_2070_370_bio6)
plot(mri_2041_2070_370_bio7)
plot(mri_2041_2070_370_bio12)
plot(mri_2041_2070_370_bio14)
plot(mri_2041_2070_370_bio15)
```

## UKESM1_0_LL ##
DONE
```{r}
ukesm_2041_2070_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio1.tif")

ukesm_2041_2070_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio2.tif")

ukesm_2041_2070_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio4.tif")

ukesm_2041_2070_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio6.tif")

ukesm_2041_2070_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio7.tif")

ukesm_2041_2070_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio12.tif")

ukesm_2041_2070_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio14.tif")

ukesm_2041_2070_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio15.tif")

ukesm_2041_2070_370_bio1 <- terra::mask(ukesm_2041_2070_370_bio1, indomalay_region)
ukesm_2041_2070_370_bio2 <- terra::mask(ukesm_2041_2070_370_bio2, indomalay_region)
ukesm_2041_2070_370_bio4 <- terra::mask(ukesm_2041_2070_370_bio4, indomalay_region)
ukesm_2041_2070_370_bio6 <- terra::mask(ukesm_2041_2070_370_bio6, indomalay_region)
ukesm_2041_2070_370_bio7 <- terra::mask(ukesm_2041_2070_370_bio7, indomalay_region)
ukesm_2041_2070_370_bio12 <- terra::mask(ukesm_2041_2070_370_bio12, indomalay_region)
ukesm_2041_2070_370_bio14 <- terra::mask(ukesm_2041_2070_370_bio14, indomalay_region)
ukesm_2041_2070_370_bio15 <- terra::mask(ukesm_2041_2070_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ukesm_2041_2070_370_bio1)
plot(ukesm_2041_2070_370_bio2)
plot(ukesm_2041_2070_370_bio4)
plot(ukesm_2041_2070_370_bio6)
plot(ukesm_2041_2070_370_bio7)
plot(ukesm_2041_2070_370_bio12)
plot(ukesm_2041_2070_370_bio14)
plot(ukesm_2041_2070_370_bio15)
```

############ 2041 - 2070 ############

####### 585 #######

## GFDL_ESM4 ##
DONE
```{r}
gfdl_2041_2070_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/GFDL_ESM4/gfdl_2041_2070_585_bio1.tif")

gfdl_2041_2070_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/GFDL_ESM4/gfdl_2041_2070_585_bio2.tif")

gfdl_2041_2070_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/GFDL_ESM4/gfdl_2041_2070_585_bio4.tif")

gfdl_2041_2070_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/GFDL_ESM4/gfdl_2041_2070_585_bio6.tif")

gfdl_2041_2070_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/GFDL_ESM4/gfdl_2041_2070_585_bio7.tif")

gfdl_2041_2070_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/GFDL_ESM4/gfdl_2041_2070_585_bio12.tif")

gfdl_2041_2070_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/GFDL_ESM4/gfdl_2041_2070_585_bio14.tif")

gfdl_2041_2070_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/GFDL_ESM4/gfdl_2041_2070_585_bio15.tif")

gfdl_2041_2070_585_bio1 <- terra::mask(gfdl_2041_2070_585_bio1, indomalay_region)
gfdl_2041_2070_585_bio2 <- terra::mask(gfdl_2041_2070_585_bio2, indomalay_region)
gfdl_2041_2070_585_bio4 <- terra::mask(gfdl_2041_2070_585_bio4, indomalay_region)
gfdl_2041_2070_585_bio6 <- terra::mask(gfdl_2041_2070_585_bio6, indomalay_region)
gfdl_2041_2070_585_bio7 <- terra::mask(gfdl_2041_2070_585_bio7, indomalay_region)
gfdl_2041_2070_585_bio12 <- terra::mask(gfdl_2041_2070_585_bio12, indomalay_region)
gfdl_2041_2070_585_bio14 <- terra::mask(gfdl_2041_2070_585_bio14, indomalay_region)
gfdl_2041_2070_585_bio15 <- terra::mask(gfdl_2041_2070_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(gfdl_2041_2070_585_bio1)
plot(gfdl_2041_2070_585_bio2)
plot(gfdl_2041_2070_585_bio4)
plot(gfdl_2041_2070_585_bio6)
plot(gfdl_2041_2070_585_bio7)
plot(gfdl_2041_2070_585_bio12)
plot(gfdl_2041_2070_585_bio14)
plot(gfdl_2041_2070_585_bio15)
```

## IPSL_CM6A_LR ##
DONE
```{r}
ipsl_2041_2070_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/IPSL_CM6A_LR/ipsl_2041_2070_585_bio1.tif")

ipsl_2041_2070_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/IPSL_CM6A_LR/ipsl_2041_2070_585_bio2.tif")

ipsl_2041_2070_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/IPSL_CM6A_LR/ipsl_2041_2070_585_bio4.tif")

ipsl_2041_2070_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/IPSL_CM6A_LR/ipsl_2041_2070_585_bio6.tif")

ipsl_2041_2070_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/IPSL_CM6A_LR/ipsl_2041_2070_585_bio7.tif")

ipsl_2041_2070_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/IPSL_CM6A_LR/ipsl_2041_2070_585_bio12.tif")

ipsl_2041_2070_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/IPSL_CM6A_LR/ipsl_2041_2070_585_bio14.tif")

ipsl_2041_2070_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/IPSL_CM6A_LR/ipsl_2041_2070_585_bio15.tif")

ipsl_2041_2070_585_bio1 <- terra::mask(ipsl_2041_2070_585_bio1, indomalay_region)
ipsl_2041_2070_585_bio2 <- terra::mask(ipsl_2041_2070_585_bio2, indomalay_region)
ipsl_2041_2070_585_bio4 <- terra::mask(ipsl_2041_2070_585_bio4, indomalay_region)
ipsl_2041_2070_585_bio6 <- terra::mask(ipsl_2041_2070_585_bio6, indomalay_region)
ipsl_2041_2070_585_bio7 <- terra::mask(ipsl_2041_2070_585_bio7, indomalay_region)
ipsl_2041_2070_585_bio12 <- terra::mask(ipsl_2041_2070_585_bio12, indomalay_region)
ipsl_2041_2070_585_bio14 <- terra::mask(ipsl_2041_2070_585_bio14, indomalay_region)
ipsl_2041_2070_585_bio15 <- terra::mask(ipsl_2041_2070_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ipsl_2041_2070_585_bio1)
plot(ipsl_2041_2070_585_bio2)
plot(ipsl_2041_2070_585_bio4)
plot(ipsl_2041_2070_585_bio6)
plot(ipsl_2041_2070_585_bio7)
plot(ipsl_2041_2070_585_bio12)
plot(ipsl_2041_2070_585_bio14)
plot(ipsl_2041_2070_585_bio15)
```

## MPI_ESM1_2_HR ##
DONE
```{r}
mpi_2041_2070_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MPI_ESM1_2_HR/mpi_2041_2070_585_bio1.tif")

mpi_2041_2070_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MPI_ESM1_2_HR/mpi_2041_2070_585_bio2.tif")

mpi_2041_2070_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MPI_ESM1_2_HR/mpi_2041_2070_585_bio4.tif")

mpi_2041_2070_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MPI_ESM1_2_HR/mpi_2041_2070_585_bio6.tif")

mpi_2041_2070_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MPI_ESM1_2_HR/mpi_2041_2070_585_bio7.tif")

mpi_2041_2070_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MPI_ESM1_2_HR/mpi_2041_2070_585_bio12.tif")

mpi_2041_2070_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MPI_ESM1_2_HR/mpi_2041_2070_585_bio14.tif")

mpi_2041_2070_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MPI_ESM1_2_HR/mpi_2041_2070_585_bio15.tif")

mpi_2041_2070_585_bio1 <- terra::mask(mpi_2041_2070_585_bio1, indomalay_region)
mpi_2041_2070_585_bio2 <- terra::mask(mpi_2041_2070_585_bio2, indomalay_region)
mpi_2041_2070_585_bio4 <- terra::mask(mpi_2041_2070_585_bio4, indomalay_region)
mpi_2041_2070_585_bio6 <- terra::mask(mpi_2041_2070_585_bio6, indomalay_region)
mpi_2041_2070_585_bio7 <- terra::mask(mpi_2041_2070_585_bio7, indomalay_region)
mpi_2041_2070_585_bio12 <- terra::mask(mpi_2041_2070_585_bio12, indomalay_region)
mpi_2041_2070_585_bio14 <- terra::mask(mpi_2041_2070_585_bio14, indomalay_region)
mpi_2041_2070_585_bio15 <- terra::mask(mpi_2041_2070_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mpi_2041_2070_585_bio1)
plot(mpi_2041_2070_585_bio2)
plot(mpi_2041_2070_585_bio4)
plot(mpi_2041_2070_585_bio6)
plot(mpi_2041_2070_585_bio7)
plot(mpi_2041_2070_585_bio12)
plot(mpi_2041_2070_585_bio14)
plot(mpi_2041_2070_585_bio15)
```

## MRI_ESM2_0 ##
DONE
```{r}
mri_2041_2070_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MRI_ESM2_0/mri_2041_2070_585_bio1.tif")

mri_2041_2070_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MRI_ESM2_0/mri_2041_2070_585_bio2.tif")

mri_2041_2070_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MRI_ESM2_0/mri_2041_2070_585_bio4.tif")

mri_2041_2070_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MRI_ESM2_0/mri_2041_2070_585_bio6.tif")

mri_2041_2070_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MRI_ESM2_0/mri_2041_2070_585_bio7.tif")

mri_2041_2070_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MRI_ESM2_0/mri_2041_2070_585_bio12.tif")

mri_2041_2070_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MRI_ESM2_0/mri_2041_2070_585_bio14.tif")

mri_2041_2070_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/MRI_ESM2_0/mri_2041_2070_585_bio15.tif")

mri_2041_2070_585_bio1 <- terra::mask(mri_2041_2070_585_bio1, indomalay_region)
mri_2041_2070_585_bio2 <- terra::mask(mri_2041_2070_585_bio2, indomalay_region)
mri_2041_2070_585_bio4 <- terra::mask(mri_2041_2070_585_bio4, indomalay_region)
mri_2041_2070_585_bio6 <- terra::mask(mri_2041_2070_585_bio6, indomalay_region)
mri_2041_2070_585_bio7 <- terra::mask(mri_2041_2070_585_bio7, indomalay_region)
mri_2041_2070_585_bio12 <- terra::mask(mri_2041_2070_585_bio12, indomalay_region)
mri_2041_2070_585_bio14 <- terra::mask(mri_2041_2070_585_bio14, indomalay_region)
mri_2041_2070_585_bio15 <- terra::mask(mri_2041_2070_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mri_2041_2070_585_bio1)
plot(mri_2041_2070_585_bio2)
plot(mri_2041_2070_585_bio4)
plot(mri_2041_2070_585_bio6)
plot(mri_2041_2070_585_bio7)
plot(mri_2041_2070_585_bio12)
plot(mri_2041_2070_585_bio14)
plot(mri_2041_2070_585_bio15)
```

## UKESM1_0_LL ##
DONE
```{r}
ukesm_2041_2070_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/UKESM1_0_LL/ukesm_2041_2070_585_bio1.tif")

ukesm_2041_2070_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/UKESM1_0_LL/ukesm_2041_2070_585_bio2.tif")

ukesm_2041_2070_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/UKESM1_0_LL/ukesm_2041_2070_585_bio4.tif")

ukesm_2041_2070_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/UKESM1_0_LL/ukesm_2041_2070_585_bio6.tif")

ukesm_2041_2070_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/UKESM1_0_LL/ukesm_2041_2070_585_bio7.tif")

ukesm_2041_2070_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/UKESM1_0_LL/ukesm_2041_2070_585_bio12.tif")

ukesm_2041_2070_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/UKESM1_0_LL/ukesm_2041_2070_585_bio14.tif")

ukesm_2041_2070_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/585/UKESM1_0_LL/ukesm_2041_2070_585_bio15.tif")

ukesm_2041_2070_585_bio1 <- terra::mask(ukesm_2041_2070_585_bio1, indomalay_region)
ukesm_2041_2070_585_bio2 <- terra::mask(ukesm_2041_2070_585_bio2, indomalay_region)
ukesm_2041_2070_585_bio4 <- terra::mask(ukesm_2041_2070_585_bio4, indomalay_region)
ukesm_2041_2070_585_bio6 <- terra::mask(ukesm_2041_2070_585_bio6, indomalay_region)
ukesm_2041_2070_585_bio7 <- terra::mask(ukesm_2041_2070_585_bio7, indomalay_region)
ukesm_2041_2070_585_bio12 <- terra::mask(ukesm_2041_2070_585_bio12, indomalay_region)
ukesm_2041_2070_585_bio14 <- terra::mask(ukesm_2041_2070_585_bio14, indomalay_region)
ukesm_2041_2070_585_bio15 <- terra::mask(ukesm_2041_2070_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ukesm_2041_2070_585_bio1)
plot(ukesm_2041_2070_585_bio2)
plot(ukesm_2041_2070_585_bio4)
plot(ukesm_2041_2070_585_bio6)
plot(ukesm_2041_2070_585_bio7)
plot(ukesm_2041_2070_585_bio12)
plot(ukesm_2041_2070_585_bio14)
plot(ukesm_2041_2070_585_bio15)
```

############ 2071 - 2100 ############

####### 126 #######

## GFDL_ESM4 ##
DONE
```{r}
gfdl_2071_2100_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/GFDL_ESM4/gfdl_2071_2100_126_bio1.tif")

gfdl_2071_2100_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/GFDL_ESM4/gfdl_2071_2100_126_bio2.tif")

gfdl_2071_2100_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/GFDL_ESM4/gfdl_2071_2100_126_bio4.tif")

gfdl_2071_2100_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/GFDL_ESM4/gfdl_2071_2100_126_bio6.tif")

gfdl_2071_2100_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/GFDL_ESM4/gfdl_2071_2100_126_bio7.tif")

gfdl_2071_2100_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/GFDL_ESM4/gfdl_2071_2100_126_bio12.tif")

gfdl_2071_2100_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/GFDL_ESM4/gfdl_2071_2100_126_bio14.tif")

gfdl_2071_2100_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/GFDL_ESM4/gfdl_2071_2100_126_bio15.tif")

gfdl_2071_2100_126_bio1 <- terra::mask(gfdl_2071_2100_126_bio1, indomalay_region)
gfdl_2071_2100_126_bio2 <- terra::mask(gfdl_2071_2100_126_bio2, indomalay_region)
gfdl_2071_2100_126_bio4 <- terra::mask(gfdl_2071_2100_126_bio4, indomalay_region)
gfdl_2071_2100_126_bio6 <- terra::mask(gfdl_2071_2100_126_bio6, indomalay_region)
gfdl_2071_2100_126_bio7 <- terra::mask(gfdl_2071_2100_126_bio7, indomalay_region)
gfdl_2071_2100_126_bio12 <- terra::mask(gfdl_2071_2100_126_bio12, indomalay_region)
gfdl_2071_2100_126_bio14 <- terra::mask(gfdl_2071_2100_126_bio14, indomalay_region)
gfdl_2071_2100_126_bio15 <- terra::mask(gfdl_2071_2100_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(gfdl_2071_2100_126_bio1)
plot(gfdl_2071_2100_126_bio2)
plot(gfdl_2071_2100_126_bio4)
plot(gfdl_2071_2100_126_bio6)
plot(gfdl_2071_2100_126_bio7)
plot(gfdl_2071_2100_126_bio12)
plot(gfdl_2071_2100_126_bio14)
plot(gfdl_2071_2100_126_bio15)
```

## IPSL_CM6A_LR ##
DONE
```{r}
ipsl_2071_2100_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/IPSL_CM6A_LR/ipsl_2071_2100_126_bio1.tif")

ipsl_2071_2100_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/IPSL_CM6A_LR/ipsl_2071_2100_126_bio2.tif")

ipsl_2071_2100_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/IPSL_CM6A_LR/ipsl_2071_2100_126_bio4.tif")

ipsl_2071_2100_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/IPSL_CM6A_LR/ipsl_2071_2100_126_bio6.tif")

ipsl_2071_2100_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/IPSL_CM6A_LR/ipsl_2071_2100_126_bio7.tif")

ipsl_2071_2100_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/IPSL_CM6A_LR/ipsl_2071_2100_126_bio12.tif")

ipsl_2071_2100_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/IPSL_CM6A_LR/ipsl_2071_2100_126_bio14.tif")

ipsl_2071_2100_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/IPSL_CM6A_LR/ipsl_2071_2100_126_bio15.tif")

ipsl_2071_2100_126_bio1 <- terra::mask(ipsl_2071_2100_126_bio1, indomalay_region)
ipsl_2071_2100_126_bio2 <- terra::mask(ipsl_2071_2100_126_bio2, indomalay_region)
ipsl_2071_2100_126_bio4 <- terra::mask(ipsl_2071_2100_126_bio4, indomalay_region)
ipsl_2071_2100_126_bio6 <- terra::mask(ipsl_2071_2100_126_bio6, indomalay_region)
ipsl_2071_2100_126_bio7 <- terra::mask(ipsl_2071_2100_126_bio7, indomalay_region)
ipsl_2071_2100_126_bio12 <- terra::mask(ipsl_2071_2100_126_bio12, indomalay_region)
ipsl_2071_2100_126_bio14 <- terra::mask(ipsl_2071_2100_126_bio14, indomalay_region)
ipsl_2071_2100_126_bio15 <- terra::mask(ipsl_2071_2100_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ipsl_2071_2100_126_bio1)
plot(ipsl_2071_2100_126_bio2)
plot(ipsl_2071_2100_126_bio4)
plot(ipsl_2071_2100_126_bio6)
plot(ipsl_2071_2100_126_bio7)
plot(ipsl_2071_2100_126_bio12)
plot(ipsl_2071_2100_126_bio14)
plot(ipsl_2071_2100_126_bio15)
```

## MPI_ESM1_2_HR ##
DONE
```{r}
mpi_2071_2100_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MPI_ESM1_2_HR/mpi_2071_2100_126_bio1.tif")

mpi_2071_2100_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MPI_ESM1_2_HR/mpi_2071_2100_126_bio2.tif")

mpi_2071_2100_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MPI_ESM1_2_HR/mpi_2071_2100_126_bio4.tif")

mpi_2071_2100_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MPI_ESM1_2_HR/mpi_2071_2100_126_bio6.tif")

mpi_2071_2100_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MPI_ESM1_2_HR/mpi_2071_2100_126_bio7.tif")

mpi_2071_2100_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MPI_ESM1_2_HR/mpi_2071_2100_126_bio12.tif")

mpi_2071_2100_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MPI_ESM1_2_HR/mpi_2071_2100_126_bio14.tif")

mpi_2071_2100_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MPI_ESM1_2_HR/mpi_2071_2100_126_bio15.tif")

mpi_2071_2100_126_bio1 <- terra::mask(mpi_2071_2100_126_bio1, indomalay_region)
mpi_2071_2100_126_bio2 <- terra::mask(mpi_2071_2100_126_bio2, indomalay_region)
mpi_2071_2100_126_bio4 <- terra::mask(mpi_2071_2100_126_bio4, indomalay_region)
mpi_2071_2100_126_bio6 <- terra::mask(mpi_2071_2100_126_bio6, indomalay_region)
mpi_2071_2100_126_bio7 <- terra::mask(mpi_2071_2100_126_bio7, indomalay_region)
mpi_2071_2100_126_bio12 <- terra::mask(mpi_2071_2100_126_bio12, indomalay_region)
mpi_2071_2100_126_bio14 <- terra::mask(mpi_2071_2100_126_bio14, indomalay_region)
mpi_2071_2100_126_bio15 <- terra::mask(mpi_2071_2100_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mpi_2071_2100_126_bio1)
plot(mpi_2071_2100_126_bio2)
plot(mpi_2071_2100_126_bio4)
plot(mpi_2071_2100_126_bio6)
plot(mpi_2071_2100_126_bio7)
plot(mpi_2071_2100_126_bio12)
plot(mpi_2071_2100_126_bio14)
plot(mpi_2071_2100_126_bio15)
```

## MRI_ESM2_0 ##
DONE
```{r}
mri_2071_2100_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MRI_ESM2_0/mri_2071_2100_126_bio1.tif") 

mri_2071_2100_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MRI_ESM2_0/mri_2071_2100_126_bio2.tif") 

mri_2071_2100_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MRI_ESM2_0/mri_2071_2100_126_bio4.tif") 

mri_2071_2100_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MRI_ESM2_0/mri_2071_2100_126_bio6.tif") 

mri_2071_2100_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MRI_ESM2_0/mri_2071_2100_126_bio7.tif") 

mri_2071_2100_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MRI_ESM2_0/mri_2071_2100_126_bio12.tif") 

mri_2071_2100_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MRI_ESM2_0/mri_2071_2100_126_bio14.tif") 

mri_2071_2100_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/MRI_ESM2_0/mri_2071_2100_126_bio15.tif") 

mri_2071_2100_126_bio1 <- terra::mask(mri_2071_2100_126_bio1, indomalay_region)
mri_2071_2100_126_bio2 <- terra::mask(mri_2071_2100_126_bio2, indomalay_region)
mri_2071_2100_126_bio4 <- terra::mask(mri_2071_2100_126_bio4, indomalay_region)
mri_2071_2100_126_bio6 <- terra::mask(mri_2071_2100_126_bio6, indomalay_region)
mri_2071_2100_126_bio7 <- terra::mask(mri_2071_2100_126_bio7, indomalay_region)
mri_2071_2100_126_bio12 <- terra::mask(mri_2071_2100_126_bio12, indomalay_region)
mri_2071_2100_126_bio14 <- terra::mask(mri_2071_2100_126_bio14, indomalay_region)
mri_2071_2100_126_bio15 <- terra::mask(mri_2071_2100_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mri_2071_2100_126_bio1)
plot(mri_2071_2100_126_bio2)
plot(mri_2071_2100_126_bio4)
plot(mri_2071_2100_126_bio6)
plot(mri_2071_2100_126_bio7)
plot(mri_2071_2100_126_bio12)
plot(mri_2071_2100_126_bio14)
plot(mri_2071_2100_126_bio15)
```

## UKESM1_0_LL ##
DONE
```{r}
ukesm_2071_2100_126_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/UKESM1_0_LL/ukesm_2071_2100_126_bio1.tif")

ukesm_2071_2100_126_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/UKESM1_0_LL/ukesm_2071_2100_126_bio2.tif")

ukesm_2071_2100_126_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/UKESM1_0_LL/ukesm_2071_2100_126_bio4.tif")

ukesm_2071_2100_126_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/UKESM1_0_LL/ukesm_2071_2100_126_bio6.tif")

ukesm_2071_2100_126_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/UKESM1_0_LL/ukesm_2071_2100_126_bio7.tif")

ukesm_2071_2100_126_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/UKESM1_0_LL/ukesm_2071_2100_126_bio12.tif")

ukesm_2071_2100_126_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/UKESM1_0_LL/ukesm_2071_2100_126_bio14.tif")

ukesm_2071_2100_126_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/126/UKESM1_0_LL/ukesm_2071_2100_126_bio15.tif")

ukesm_2071_2100_126_bio1 <- terra::mask(ukesm_2071_2100_126_bio1, indomalay_region)
ukesm_2071_2100_126_bio2 <- terra::mask(ukesm_2071_2100_126_bio2, indomalay_region)
ukesm_2071_2100_126_bio4 <- terra::mask(ukesm_2071_2100_126_bio4, indomalay_region)
ukesm_2071_2100_126_bio6 <- terra::mask(ukesm_2071_2100_126_bio6, indomalay_region)
ukesm_2071_2100_126_bio7 <- terra::mask(ukesm_2071_2100_126_bio7, indomalay_region)
ukesm_2071_2100_126_bio12 <- terra::mask(ukesm_2071_2100_126_bio12, indomalay_region)
ukesm_2071_2100_126_bio14 <- terra::mask(ukesm_2071_2100_126_bio14, indomalay_region)
ukesm_2071_2100_126_bio15 <- terra::mask(ukesm_2071_2100_126_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ukesm_2071_2100_126_bio1)
plot(ukesm_2071_2100_126_bio2)
plot(ukesm_2071_2100_126_bio4)
plot(ukesm_2071_2100_126_bio6)
plot(ukesm_2071_2100_126_bio7)
plot(ukesm_2071_2100_126_bio12)
plot(ukesm_2071_2100_126_bio14)
plot(ukesm_2071_2100_126_bio15)
```

############ 2071 - 2100 ############

####### 370 #######

## GFDL_ESM4 ##
DONE
```{r}
gfdl_2071_2100_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/GFDL_ESM4/gfdl_2071_2100_370_bio1.tif")

gfdl_2071_2100_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/GFDL_ESM4/gfdl_2071_2100_370_bio2.tif")

gfdl_2071_2100_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/GFDL_ESM4/gfdl_2071_2100_370_bio4.tif")

gfdl_2071_2100_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/GFDL_ESM4/gfdl_2071_2100_370_bio6.tif")

gfdl_2071_2100_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/GFDL_ESM4/gfdl_2071_2100_370_bio7.tif")

gfdl_2071_2100_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/GFDL_ESM4/gfdl_2071_2100_370_bio12.tif")

gfdl_2071_2100_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/GFDL_ESM4/gfdl_2071_2100_370_bio14.tif")

gfdl_2071_2100_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/GFDL_ESM4/gfdl_2071_2100_370_bio15.tif")

gfdl_2071_2100_370_bio1 <- terra::mask(gfdl_2071_2100_370_bio1, indomalay_region)
gfdl_2071_2100_370_bio2 <- terra::mask(gfdl_2071_2100_370_bio2, indomalay_region)
gfdl_2071_2100_370_bio4 <- terra::mask(gfdl_2071_2100_370_bio4, indomalay_region)
gfdl_2071_2100_370_bio6 <- terra::mask(gfdl_2071_2100_370_bio6, indomalay_region)
gfdl_2071_2100_370_bio7 <- terra::mask(gfdl_2071_2100_370_bio7, indomalay_region)
gfdl_2071_2100_370_bio12 <- terra::mask(gfdl_2071_2100_370_bio12, indomalay_region)
gfdl_2071_2100_370_bio14 <- terra::mask(gfdl_2071_2100_370_bio14, indomalay_region)
gfdl_2071_2100_370_bio15 <- terra::mask(gfdl_2071_2100_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(gfdl_2071_2100_370_bio1)
plot(gfdl_2071_2100_370_bio2)
plot(gfdl_2071_2100_370_bio4)
plot(gfdl_2071_2100_370_bio6)
plot(gfdl_2071_2100_370_bio7)
plot(gfdl_2071_2100_370_bio12)
plot(gfdl_2071_2100_370_bio14)
plot(gfdl_2071_2100_370_bio15)
```

## IPSL_CM6A_LR ##
DONE
```{r}
ipsl_2071_2100_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/IPSL_CM6A_LR/ipsl_2071_2100_370_bio1.tif")

ipsl_2071_2100_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/IPSL_CM6A_LR/ipsl_2071_2100_370_bio2.tif")

ipsl_2071_2100_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/IPSL_CM6A_LR/ipsl_2071_2100_370_bio4.tif")

ipsl_2071_2100_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/IPSL_CM6A_LR/ipsl_2071_2100_370_bio6.tif")

ipsl_2071_2100_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/IPSL_CM6A_LR/ipsl_2071_2100_370_bio7.tif")

ipsl_2071_2100_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/IPSL_CM6A_LR/ipsl_2071_2100_370_bio12.tif")

ipsl_2071_2100_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/IPSL_CM6A_LR/ipsl_2071_2100_370_bio14.tif")

ipsl_2071_2100_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/IPSL_CM6A_LR/ipsl_2071_2100_370_bio15.tif")

ipsl_2071_2100_370_bio1 <- terra::mask(ipsl_2071_2100_370_bio1, indomalay_region)
ipsl_2071_2100_370_bio2 <- terra::mask(ipsl_2071_2100_370_bio2, indomalay_region)
ipsl_2071_2100_370_bio4 <- terra::mask(ipsl_2071_2100_370_bio4, indomalay_region)
ipsl_2071_2100_370_bio6 <- terra::mask(ipsl_2071_2100_370_bio6, indomalay_region)
ipsl_2071_2100_370_bio7 <- terra::mask(ipsl_2071_2100_370_bio7, indomalay_region)
ipsl_2071_2100_370_bio12 <- terra::mask(ipsl_2071_2100_370_bio12, indomalay_region)
ipsl_2071_2100_370_bio14 <- terra::mask(ipsl_2071_2100_370_bio14, indomalay_region)
ipsl_2071_2100_370_bio15 <- terra::mask(ipsl_2071_2100_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ipsl_2071_2100_370_bio1)
plot(ipsl_2071_2100_370_bio2)
plot(ipsl_2071_2100_370_bio4)
plot(ipsl_2071_2100_370_bio6)
plot(ipsl_2071_2100_370_bio7)
plot(ipsl_2071_2100_370_bio12)
plot(ipsl_2071_2100_370_bio14)
plot(ipsl_2071_2100_370_bio15)
```

## MPI_ESM1_2_HR ##
DONE
```{r}
mpi_2071_2100_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MPI_ESM1_2_HR/mpi_2071_2100_370_bio1.tif")

mpi_2071_2100_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MPI_ESM1_2_HR/mpi_2071_2100_370_bio2.tif")

mpi_2071_2100_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MPI_ESM1_2_HR/mpi_2071_2100_370_bio4.tif")

mpi_2071_2100_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MPI_ESM1_2_HR/mpi_2071_2100_370_bio6.tif")

mpi_2071_2100_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MPI_ESM1_2_HR/mpi_2071_2100_370_bio7.tif")

mpi_2071_2100_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MPI_ESM1_2_HR/mpi_2071_2100_370_bio12.tif")

mpi_2071_2100_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MPI_ESM1_2_HR/mpi_2071_2100_370_bio14.tif")

mpi_2071_2100_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MPI_ESM1_2_HR/mpi_2071_2100_370_bio15.tif")

mpi_2071_2100_370_bio1 <- terra::mask(mpi_2071_2100_370_bio1, indomalay_region)
mpi_2071_2100_370_bio2 <- terra::mask(mpi_2071_2100_370_bio2, indomalay_region)
mpi_2071_2100_370_bio4 <- terra::mask(mpi_2071_2100_370_bio4, indomalay_region)
mpi_2071_2100_370_bio6 <- terra::mask(mpi_2071_2100_370_bio6, indomalay_region)
mpi_2071_2100_370_bio7 <- terra::mask(mpi_2071_2100_370_bio7, indomalay_region)
mpi_2071_2100_370_bio12 <- terra::mask(mpi_2071_2100_370_bio12, indomalay_region)
mpi_2071_2100_370_bio14 <- terra::mask(mpi_2071_2100_370_bio14, indomalay_region)
mpi_2071_2100_370_bio15 <- terra::mask(mpi_2071_2100_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mpi_2071_2100_370_bio1)
plot(mpi_2071_2100_370_bio2)
plot(mpi_2071_2100_370_bio4)
plot(mpi_2071_2100_370_bio6)
plot(mpi_2071_2100_370_bio7)
plot(mpi_2071_2100_370_bio12)
plot(mpi_2071_2100_370_bio14)
plot(mpi_2071_2100_370_bio15)
```

## MRI_ESM2_0 ##
DONE
```{r}
mri_2071_2100_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MRI_ESM2_0/mri_2071_2100_370_bio1.tif")

mri_2071_2100_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MRI_ESM2_0/mri_2071_2100_370_bio2.tif")

mri_2071_2100_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MRI_ESM2_0/mri_2071_2100_370_bio4.tif")

mri_2071_2100_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MRI_ESM2_0/mri_2071_2100_370_bio6.tif")

mri_2071_2100_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MRI_ESM2_0/mri_2071_2100_370_bio7.tif")

mri_2071_2100_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MRI_ESM2_0/mri_2071_2100_370_bio12.tif")

mri_2071_2100_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MRI_ESM2_0/mri_2071_2100_370_bio14.tif")

mri_2071_2100_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/370/MRI_ESM2_0/mri_2071_2100_370_bio15.tif")

mri_2071_2100_370_bio1 <- terra::mask(mri_2071_2100_370_bio1, indomalay_region)
mri_2071_2100_370_bio2 <- terra::mask(mri_2071_2100_370_bio2, indomalay_region)
mri_2071_2100_370_bio4 <- terra::mask(mri_2071_2100_370_bio4, indomalay_region)
mri_2071_2100_370_bio6 <- terra::mask(mri_2071_2100_370_bio6, indomalay_region)
mri_2071_2100_370_bio7 <- terra::mask(mri_2071_2100_370_bio7, indomalay_region)
mri_2071_2100_370_bio12 <- terra::mask(mri_2071_2100_370_bio12, indomalay_region)
mri_2071_2100_370_bio14 <- terra::mask(mri_2071_2100_370_bio14, indomalay_region)
mri_2071_2100_370_bio15 <- terra::mask(mri_2071_2100_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mri_2071_2100_370_bio1)
plot(mri_2071_2100_370_bio2)
plot(mri_2071_2100_370_bio4)
plot(mri_2071_2100_370_bio6)
plot(mri_2071_2100_370_bio7)
plot(mri_2071_2100_370_bio12)
plot(mri_2071_2100_370_bio14)
plot(mri_2071_2100_370_bio15)
```

## UKESM1_0_LL ##
DONE
```{r}
ukesm_2041_2070_370_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio1.tif")

ukesm_2041_2070_370_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio2.tif")

ukesm_2041_2070_370_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio4.tif")

ukesm_2041_2070_370_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio6.tif")

ukesm_2041_2070_370_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio7.tif")

ukesm_2041_2070_370_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio12.tif")

ukesm_2041_2070_370_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio14.tif")

ukesm_2041_2070_370_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2041_2070/370/UKESM1_0_LL/ukesm_2041_2070_370_bio15.tif")

ukesm_2041_2070_370_bio1 <- terra::mask(ukesm_2041_2070_370_bio1, indomalay_region)
ukesm_2041_2070_370_bio2 <- terra::mask(ukesm_2041_2070_370_bio2, indomalay_region)
ukesm_2041_2070_370_bio4 <- terra::mask(ukesm_2041_2070_370_bio4, indomalay_region)
ukesm_2041_2070_370_bio6 <- terra::mask(ukesm_2041_2070_370_bio6, indomalay_region)
ukesm_2041_2070_370_bio7 <- terra::mask(ukesm_2041_2070_370_bio7, indomalay_region)
ukesm_2041_2070_370_bio12 <- terra::mask(ukesm_2041_2070_370_bio12, indomalay_region)
ukesm_2041_2070_370_bio14 <- terra::mask(ukesm_2041_2070_370_bio14, indomalay_region)
ukesm_2041_2070_370_bio15 <- terra::mask(ukesm_2041_2070_370_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ukesm_2041_2070_370_bio1)
plot(ukesm_2041_2070_370_bio2)
plot(ukesm_2041_2070_370_bio4)
plot(ukesm_2041_2070_370_bio6)
plot(ukesm_2041_2070_370_bio7)
plot(ukesm_2041_2070_370_bio12)
plot(ukesm_2041_2070_370_bio14)
plot(ukesm_2041_2070_370_bio15)
```


############ 2071 - 2100 ############

####### 585 #######

## GFDL_ESM4 ##
DONE
```{r}
gfdl_2071_2100_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/GFDL_ESM4/gfdl_2071_2100_585_bio1.tif")

gfdl_2071_2100_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/GFDL_ESM4/gfdl_2071_2100_585_bio2.tif")

gfdl_2071_2100_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/GFDL_ESM4/gfdl_2071_2100_585_bio4.tif")

gfdl_2071_2100_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/GFDL_ESM4/gfdl_2071_2100_585_bio6.tif")

gfdl_2071_2100_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/GFDL_ESM4/gfdl_2071_2100_585_bio7.tif")

gfdl_2071_2100_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/GFDL_ESM4/gfdl_2071_2100_585_bio12.tif")

gfdl_2071_2100_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/GFDL_ESM4/gfdl_2071_2100_585_bio14.tif")

gfdl_2071_2100_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/GFDL_ESM4/gfdl_2071_2100_585_bio15.tif")

gfdl_2071_2100_585_bio1 <- terra::mask(gfdl_2071_2100_585_bio1, indomalay_region)
gfdl_2071_2100_585_bio2 <- terra::mask(gfdl_2071_2100_585_bio2, indomalay_region)
gfdl_2071_2100_585_bio4 <- terra::mask(gfdl_2071_2100_585_bio4, indomalay_region)
gfdl_2071_2100_585_bio6 <- terra::mask(gfdl_2071_2100_585_bio6, indomalay_region)
gfdl_2071_2100_585_bio7 <- terra::mask(gfdl_2071_2100_585_bio7, indomalay_region)
gfdl_2071_2100_585_bio12 <- terra::mask(gfdl_2071_2100_585_bio12, indomalay_region)
gfdl_2071_2100_585_bio14 <- terra::mask(gfdl_2071_2100_585_bio14, indomalay_region)
gfdl_2071_2100_585_bio15 <- terra::mask(gfdl_2071_2100_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(gfdl_2071_2100_585_bio1)
plot(gfdl_2071_2100_585_bio2)
plot(gfdl_2071_2100_585_bio4)
plot(gfdl_2071_2100_585_bio6)
plot(gfdl_2071_2100_585_bio7)
plot(gfdl_2071_2100_585_bio12)
plot(gfdl_2071_2100_585_bio14)
plot(gfdl_2071_2100_585_bio15)
```

## IPSL_CM6A_LR ##
DONE
```{r}
ipsl_2071_2100_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/IPSL_CM6A_LR/ipsl_2071_2100_585_bio1.tif")

ipsl_2071_2100_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/IPSL_CM6A_LR/ipsl_2071_2100_585_bio2.tif")

ipsl_2071_2100_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/IPSL_CM6A_LR/ipsl_2071_2100_585_bio4.tif")

ipsl_2071_2100_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/IPSL_CM6A_LR/ipsl_2071_2100_585_bio6.tif")

ipsl_2071_2100_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/IPSL_CM6A_LR/ipsl_2071_2100_585_bio7.tif")

ipsl_2071_2100_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/IPSL_CM6A_LR/ipsl_2071_2100_585_bio12.tif")

ipsl_2071_2100_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/IPSL_CM6A_LR/ipsl_2071_2100_585_bio14.tif")

ipsl_2071_2100_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/IPSL_CM6A_LR/ipsl_2071_2100_585_bio15.tif")

ipsl_2071_2100_585_bio1 <- terra::mask(ipsl_2071_2100_585_bio1, indomalay_region)
ipsl_2071_2100_585_bio2 <- terra::mask(ipsl_2071_2100_585_bio2, indomalay_region)
ipsl_2071_2100_585_bio4 <- terra::mask(ipsl_2071_2100_585_bio4, indomalay_region)
ipsl_2071_2100_585_bio6 <- terra::mask(ipsl_2071_2100_585_bio6, indomalay_region)
ipsl_2071_2100_585_bio7 <- terra::mask(ipsl_2071_2100_585_bio7, indomalay_region)
ipsl_2071_2100_585_bio12 <- terra::mask(ipsl_2071_2100_585_bio12, indomalay_region)
ipsl_2071_2100_585_bio14 <- terra::mask(ipsl_2071_2100_585_bio14, indomalay_region)
ipsl_2071_2100_585_bio15 <- terra::mask(ipsl_2071_2100_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ipsl_2071_2100_585_bio1)
plot(ipsl_2071_2100_585_bio2)
plot(ipsl_2071_2100_585_bio4)
plot(ipsl_2071_2100_585_bio6)
plot(ipsl_2071_2100_585_bio7)
plot(ipsl_2071_2100_585_bio12)
plot(ipsl_2071_2100_585_bio14)
plot(ipsl_2071_2100_585_bio15)
```

## MPI_ESM1_2_HR ##
DONE
```{r}
mpi_2071_2100_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MPI_ESM1_2_HR/mpi_2071_2100_585_bio1.tif")

mpi_2071_2100_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MPI_ESM1_2_HR/mpi_2071_2100_585_bio2.tif")

mpi_2071_2100_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MPI_ESM1_2_HR/mpi_2071_2100_585_bio4.tif")

mpi_2071_2100_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MPI_ESM1_2_HR/mpi_2071_2100_585_bio6.tif")

mpi_2071_2100_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MPI_ESM1_2_HR/mpi_2071_2100_585_bio7.tif")

mpi_2071_2100_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MPI_ESM1_2_HR/mpi_2071_2100_585_bio12.tif")

mpi_2071_2100_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MPI_ESM1_2_HR/mpi_2071_2100_585_bio14.tif")

mpi_2071_2100_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MPI_ESM1_2_HR/mpi_2071_2100_585_bio15.tif")

mpi_2071_2100_585_bio1 <- terra::mask(mpi_2071_2100_585_bio1, indomalay_region)
mpi_2071_2100_585_bio2 <- terra::mask(mpi_2071_2100_585_bio2, indomalay_region)
mpi_2071_2100_585_bio4 <- terra::mask(mpi_2071_2100_585_bio4, indomalay_region)
mpi_2071_2100_585_bio6 <- terra::mask(mpi_2071_2100_585_bio6, indomalay_region)
mpi_2071_2100_585_bio7 <- terra::mask(mpi_2071_2100_585_bio7, indomalay_region)
mpi_2071_2100_585_bio12 <- terra::mask(mpi_2071_2100_585_bio12, indomalay_region)
mpi_2071_2100_585_bio14 <- terra::mask(mpi_2071_2100_585_bio14, indomalay_region)
mpi_2071_2100_585_bio15 <- terra::mask(mpi_2071_2100_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mpi_2071_2100_585_bio1)
plot(mpi_2071_2100_585_bio2)
plot(mpi_2071_2100_585_bio4)
plot(mpi_2071_2100_585_bio6)
plot(mpi_2071_2100_585_bio7)
plot(mpi_2071_2100_585_bio12)
plot(mpi_2071_2100_585_bio14)
plot(mpi_2071_2100_585_bio15)
```

## MRI_ESM2_0 ##

```{r}
mri_2071_2100_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MRI_ESM2_0/mri_2071_2100_585_bio1.tif")

mri_2071_2100_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MRI_ESM2_0/mri_2071_2100_585_bio2.tif")

mri_2071_2100_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MRI_ESM2_0/mri_2071_2100_585_bio4.tif")

mri_2071_2100_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MRI_ESM2_0/mri_2071_2100_585_bio6.tif")

mri_2071_2100_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MRI_ESM2_0/mri_2071_2100_585_bio7.tif")

mri_2071_2100_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MRI_ESM2_0/mri_2071_2100_585_bio12.tif")

mri_2071_2100_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MRI_ESM2_0/mri_2071_2100_585_bio14.tif")

mri_2071_2100_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/MRI_ESM2_0/mri_2071_2100_585_bio15.tif")

mri_2071_2100_585_bio1 <- terra::mask(mri_2071_2100_585_bio1, indomalay_region)
mri_2071_2100_585_bio2 <- terra::mask(mri_2071_2100_585_bio2, indomalay_region)
mri_2071_2100_585_bio4 <- terra::mask(mri_2071_2100_585_bio4, indomalay_region)
mri_2071_2100_585_bio6 <- terra::mask(mri_2071_2100_585_bio6, indomalay_region)
mri_2071_2100_585_bio7 <- terra::mask(mri_2071_2100_585_bio7, indomalay_region)
mri_2071_2100_585_bio12 <- terra::mask(mri_2071_2100_585_bio12, indomalay_region)
mri_2071_2100_585_bio14 <- terra::mask(mri_2071_2100_585_bio14, indomalay_region)
mri_2071_2100_585_bio15 <- terra::mask(mri_2071_2100_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(mri_2071_2100_585_bio1)
plot(mri_2071_2100_585_bio2)
plot(mri_2071_2100_585_bio4)
plot(mri_2071_2100_585_bio6)
plot(mri_2071_2100_585_bio7)
plot(mri_2071_2100_585_bio12)
plot(mri_2071_2100_585_bio14)
plot(mri_2071_2100_585_bio15)
```

## UKESM1_0_LL ##
DONE
```{r}
ukesm_2071_2100_585_bio1 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/UKESM1_0_LL/ukesm_2071_2100_585_bio1.tif")

ukesm_2071_2100_585_bio2 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/UKESM1_0_LL/ukesm_2071_2100_585_bio2.tif")

ukesm_2071_2100_585_bio4 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/UKESM1_0_LL/ukesm_2071_2100_585_bio4.tif")

ukesm_2071_2100_585_bio6 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/UKESM1_0_LL/ukesm_2071_2100_585_bio6.tif")

ukesm_2071_2100_585_bio7 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/UKESM1_0_LL/ukesm_2071_2100_585_bio7.tif")

ukesm_2071_2100_585_bio12 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/UKESM1_0_LL/ukesm_2071_2100_585_bio12.tif")

ukesm_2071_2100_585_bio14 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/UKESM1_0_LL/ukesm_2071_2100_585_bio14.tif")

ukesm_2071_2100_585_bio15 <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/chelsa_asia/2071_2100/585/UKESM1_0_LL/ukesm_2071_2100_585_bio15.tif")

ukesm_2071_2100_585_bio1 <- terra::mask(ukesm_2071_2100_585_bio1, indomalay_region)
ukesm_2071_2100_585_bio2 <- terra::mask(ukesm_2071_2100_585_bio2, indomalay_region)
ukesm_2071_2100_585_bio4 <- terra::mask(ukesm_2071_2100_585_bio4, indomalay_region)
ukesm_2071_2100_585_bio6 <- terra::mask(ukesm_2071_2100_585_bio6, indomalay_region)
ukesm_2071_2100_585_bio7 <- terra::mask(ukesm_2071_2100_585_bio7, indomalay_region)
ukesm_2071_2100_585_bio12 <- terra::mask(ukesm_2071_2100_585_bio12, indomalay_region)
ukesm_2071_2100_585_bio14 <- terra::mask(ukesm_2071_2100_585_bio14, indomalay_region)
ukesm_2071_2100_585_bio15 <- terra::mask(ukesm_2071_2100_585_bio15, indomalay_region)

par(mfrow=c(2,4))
par(mar=c(4,4,4,4))
plot(ukesm_2071_2100_585_bio1)
plot(ukesm_2071_2100_585_bio2)
plot(ukesm_2071_2100_585_bio4)
plot(ukesm_2071_2100_585_bio6)
plot(ukesm_2071_2100_585_bio7)
plot(ukesm_2071_2100_585_bio12)
plot(ukesm_2071_2100_585_bio14)
plot(ukesm_2071_2100_585_bio15)
```
