---
title: "Asian Elephant Change Maps"
author: "Grace Kumaishi"
date: "7/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(here)

# Enter YOUR data path to HWC_data folder, including "HWC_data". 
# May require double forward slashes
HWC_data <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data" 
```

### 2041-2070 ###
### SSP 1 RCP 2.6 ### 

# Read in historic and projected SDMs (10th percentile training presence)

```{r}
# historic 
historic <- raster(paste0(HWC_data, "/Wallace SDM Rasters/asia/1981_2010/asian_elephant_historic_10p_sdm.tif"))
```

```{r}
# GFDL
proj_2041_2070_126_gfdl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/126/gfdl_2041_2070_126_10p_sdm.tif"))
  
# IPSL
proj_2041_2070_126_ipsl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/126/ipsl_2041_2070_126_10p_sdm.tif"))
  
# MPI
proj_2041_2070_126_mpi <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/126/mpi_2041_2070_126_10p_sdm.tif"))
  
# MRI
proj_2041_2070_126_mri <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/126/mri_2041_2070_126_10p_sdm.tif"))
  
# UKESM
proj_2041_2070_126_ukesm <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/126/ukesm_2041_2070_126_10p_sdm.tif"))
```

# Reclasify projected rasters

```{r}
# GFDL
proj_2041_2070_126_gfdl[proj_2041_2070_126_gfdl == 0] <- 2
proj_2041_2070_126_gfdl[proj_2041_2070_126_gfdl == 1] <- 4

# IPSL
proj_2041_2070_126_ipsl[proj_2041_2070_126_ipsl == 0] <- 2
proj_2041_2070_126_ipsl[proj_2041_2070_126_ipsl == 1] <- 4

# MPI
proj_2041_2070_126_mpi[proj_2041_2070_126_mpi == 0] <- 2
proj_2041_2070_126_mpi[proj_2041_2070_126_mpi == 1] <- 4

# MRI
proj_2041_2070_126_mri[proj_2041_2070_126_mri == 0] <- 2
proj_2041_2070_126_mri[proj_2041_2070_126_mri == 1] <- 4

# UKESM
proj_2041_2070_126_ukesm[proj_2041_2070_126_ukesm == 0] <- 2
proj_2041_2070_126_ukesm[proj_2041_2070_126_ukesm == 1] <- 4
```

***NOTE***: Under this setup where we are manually giving the binomial raster these values, after subtracting the historic SDM from the projected SDM the numeric categories assigned to the rasters can be translated accordingly:
  1: Decreasing suitability
  2: No change; not suitable
  3: No change; suitable
  4: Increasing suitability

# Subtract historic from projected rasters

```{r}
# GFDL
change_2041_2070_126_gfdl <- proj_2041_2070_126_gfdl - historic

# IPSL
change_2041_2070_126_ipsl <- proj_2041_2070_126_ipsl - historic

# MPI
change_2041_2070_126_mpi <- proj_2041_2070_126_mpi - historic

# MRI
change_2041_2070_126_mri <- proj_2041_2070_126_mri - historic

# UKESM
change_2041_2070_126_ukesm <- proj_2041_2070_126_ukesm - historic
```

# View change maps

```{r}
# GFDL
plot(change_2041_2070_126_gfdl)

# IPSL
plot(change_2041_2070_126_ipsl)

# MPI
plot(change_2041_2070_126_mpi)

# MRI
plot(change_2041_2070_126_mri)

# UKESM
plot(change_2041_2070_126_ukesm)
```

# Save change maps to Google Drive

```{r}
# GFDL 
writeRaster(change_2041_2070_126_gfdl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_126_gfdl.tif")), overwrite = FALSE)

# IPSL
writeRaster(change_2041_2070_126_ipsl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_126_ipsl.tif")), overwrite = FALSE)

# MPI
writeRaster(change_2041_2070_126_mpi, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_126_mpi.tif")), overwrite = FALSE)

# MRI
writeRaster(change_2041_2070_126_mri, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_126_mri.tif")), overwrite = FALSE)

# UKESM
writeRaster(change_2041_2070_126_ukesm, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_126_ukesm.tif")), overwrite = FALSE)
```

### 2041-2070 ###
### SSP 5 RCP 8.5 ### 

# Read in projected SDMS (10th percentile training presence)

```{r}
# GFDL
proj_2041_2070_585_gfdl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/585/gfdl_2041_2070_585_10p_sdm.tif"))
  
# IPSL
proj_2041_2070_585_ipsl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/585/ipsl_2041_2070_585_10p_sdm.tif"))
  
# MPI
proj_2041_2070_585_mpi <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/585/mpi_2041_2070_585_10p_sdm.tif"))
  
# MRI
proj_2041_2070_585_mri <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/585/mri_2041_2070_585_10p_sdm.tif"))
  
# UKESM
proj_2041_2070_585_ukesm <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/585/ukesm_2041_2070_585_10p_sdm.tif"))
```

# Reclasify projected rasters

```{r}
# GFDL
proj_2041_2070_585_gfdl[proj_2041_2070_585_gfdl == 0] <- 2
proj_2041_2070_585_gfdl[proj_2041_2070_585_gfdl == 1] <- 4

# IPSL
proj_2041_2070_585_ipsl[proj_2041_2070_585_ipsl == 0] <- 2
proj_2041_2070_585_ipsl[proj_2041_2070_585_ipsl == 1] <- 4

# MPI
proj_2041_2070_585_mpi[proj_2041_2070_585_mpi == 0] <- 2
proj_2041_2070_585_mpi[proj_2041_2070_585_mpi == 1] <- 4

# MRI
proj_2041_2070_585_mri[proj_2041_2070_585_mri == 0] <- 2
proj_2041_2070_585_mri[proj_2041_2070_585_mri == 1] <- 4

# UKESM
proj_2041_2070_585_ukesm[proj_2041_2070_585_ukesm == 0] <- 2
proj_2041_2070_585_ukesm[proj_2041_2070_585_ukesm == 1] <- 4
```

# Subtract historic from projected rasters

```{r}
# GFDL
change_2041_2070_585_gfdl <- proj_2041_2070_585_gfdl - historic

# IPSL
change_2041_2070_585_ipsl <- proj_2041_2070_585_ipsl - historic

# MPI
change_2041_2070_585_mpi <- proj_2041_2070_585_mpi - historic

# MRI
change_2041_2070_585_mri <- proj_2041_2070_585_mri - historic

# UKESM
change_2041_2070_585_ukesm <- proj_2041_2070_585_ukesm - historic
```

# View change maps

```{r}
# GFDL
plot(change_2041_2070_585_gfdl)

# IPSL
plot(change_2041_2070_585_ipsl)

# MPI
plot(change_2041_2070_585_mpi)

# MRI
plot(change_2041_2070_585_mri)

# UKESM
plot(change_2041_2070_585_ukesm)
```

# Save change maps to Google Drive

```{r}
# GFDL 
writeRaster(change_2041_2070_585_gfdl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_585_gfdl.tif")), overwrite = FALSE)

# IPSL
writeRaster(change_2041_2070_585_ipsl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_585_ipsl.tif")), overwrite = FALSE) 

# MPI
writeRaster(change_2041_2070_585_mpi, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_585_mpi.tif")), overwrite = FALSE)

# MRI
writeRaster(change_2041_2070_585_mri, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_585_mri.tif")), overwrite = FALSE)

# UKESM
writeRaster(change_2041_2070_585_ukesm, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_585_ukesm.tif")), overwrite = FALSE)
```

### 2041-2070 ###
### SSP 3 RCP 7.0 ### 

# Read in projected SDMS (10th percentile training presence)
```{r}
# GFDL
proj_2041_2070_370_gfdl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/370/gfdl_2041_2070_370_10p_sdm.tif"))
  
# IPSL
proj_2041_2070_370_ipsl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/370/ipsl_2041_2070_370_10p_sdm.tif"))
  
# MPI
proj_2041_2070_370_mpi <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/370/mpi_2041_2070_370_10p_sdm.tif"))
  
# MRI
proj_2041_2070_370_mri <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/370/mri_2041_2070_370_10p_sdm.tif"))
  
# UKESM
proj_2041_2070_370_ukesm <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/370/ukesm_2041_2070_370_10p_sdm.tif"))
```

# Reclasify projected rasters
```{r}
# GFDL
proj_2041_2070_370_gfdl[proj_2041_2070_370_gfdl == 0] <- 2
proj_2041_2070_370_gfdl[proj_2041_2070_370_gfdl == 1] <- 4

# IPSL
proj_2041_2070_370_ipsl[proj_2041_2070_370_ipsl == 0] <- 2
proj_2041_2070_370_ipsl[proj_2041_2070_370_ipsl == 1] <- 4

# MPI
proj_2041_2070_370_mpi[proj_2041_2070_370_mpi == 0] <- 2
proj_2041_2070_370_mpi[proj_2041_2070_370_mpi == 1] <- 4

# MRI
proj_2041_2070_370_mri[proj_2041_2070_370_mri == 0] <- 2
proj_2041_2070_370_mri[proj_2041_2070_370_mri == 1] <- 4

# UKESM
proj_2041_2070_370_ukesm[proj_2041_2070_370_ukesm == 0] <- 2
proj_2041_2070_370_ukesm[proj_2041_2070_370_ukesm == 1] <- 4
```

# Subtract historic from projected rasters
```{r}
# GFDL
change_2041_2070_370_gfdl <- proj_2041_2070_370_gfdl - historic

# IPSL
change_2041_2070_370_ipsl <- proj_2041_2070_370_ipsl - historic

# MPI
change_2041_2070_370_mpi <- proj_2041_2070_370_mpi - historic

# MRI
change_2041_2070_370_mri <- proj_2041_2070_370_mri - historic

# UKESM
change_2041_2070_370_ukesm <- proj_2041_2070_370_ukesm - historic
```

# View change maps
```{r}
# GFDL
plot(change_2041_2070_370_gfdl)

# IPSL
plot(change_2041_2070_370_ipsl)

# MPI
plot(change_2041_2070_370_mpi)

# MRI
plot(change_2041_2070_370_mri)

# UKESM
plot(change_2041_2070_370_ukesm)
```

# Save change maps to Google Drive
```{r}
# GFDL 
writeRaster(change_2041_2070_370_gfdl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_370_gfdl.tif")), overwrite = FALSE)

# IPSL
writeRaster(change_2041_2070_370_ipsl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_370_ipsl.tif")), overwrite = FALSE) 

# MPI
writeRaster(change_2041_2070_370_mpi, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_370_mpi.tif")), overwrite = FALSE)

# MRI
writeRaster(change_2041_2070_370_mri, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_370_mri.tif")), overwrite = FALSE)

# UKESM
writeRaster(change_2041_2070_370_ukesm, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2041_2070/change_maps/change_2041_2070_370_ukesm.tif")), overwrite = FALSE)
```

### 2071-2100 ###
### SSP 1 RCP 2.6 ### 

# Read in historic and projected SDMs (10th percentile training presence)

```{r}
# historic 
historic <- raster(paste0(HWC_data, "/Wallace SDM Rasters/asia/1981_2010/asian_elephant_historic_10p_sdm.tif"))
```

```{r}
# GFDL
proj_2071_2100_126_gfdl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/126/gfdl_2071_2100_126_10p_sdm.tif"))
  
# IPSL
proj_2071_2100_126_ipsl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/126/ipsl_2071_2100_126_10p_sdm.tif"))
  
# MPI
proj_2071_2100_126_mpi <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/126/mpi_2071_2100_126_10p_sdm.tif"))
  
# MRI
proj_2071_2100_126_mri <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/126/mri_2071_2100_126_10p_sdm.tif"))
  
# UKESM
proj_2071_2100_126_ukesm <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/126/ukesm_2071_2100_126_10p_sdm.tif"))
```

# Reclasify projected rasters

```{r}
# GFDL
proj_2071_2100_126_gfdl[proj_2071_2100_126_gfdl == 0] <- 2
proj_2071_2100_126_gfdl[proj_2071_2100_126_gfdl == 1] <- 4

# IPSL
proj_2071_2100_126_ipsl[proj_2071_2100_126_ipsl == 0] <- 2
proj_2071_2100_126_ipsl[proj_2071_2100_126_ipsl == 1] <- 4

# MPI
proj_2071_2100_126_mpi[proj_2071_2100_126_mpi == 0] <- 2
proj_2071_2100_126_mpi[proj_2071_2100_126_mpi == 1] <- 4

# MRI
proj_2071_2100_126_mri[proj_2071_2100_126_mri == 0] <- 2
proj_2071_2100_126_mri[proj_2071_2100_126_mri == 1] <- 4

# UKESM
proj_2071_2100_126_ukesm[proj_2071_2100_126_ukesm == 0] <- 2
proj_2071_2100_126_ukesm[proj_2071_2100_126_ukesm == 1] <- 4
```

***NOTE***: Under this setup where we are manually giving the binomial raster these values, after subtracting the historic SDM from the projected SDM the numeric categories assigned to the rasters can be translated accordingly:
  1: Decreasing suitability
  2: No change; not suitable
  3: No change; suitable
  4: Increasing suitability

# Subtract historic from projected rasters

```{r}
# GFDL
change_2071_2100_126_gfdl <- proj_2071_2100_126_gfdl - historic

# IPSL
change_2071_2100_126_ipsl <- proj_2071_2100_126_ipsl - historic

# MPI
change_2071_2100_126_mpi <- proj_2071_2100_126_mpi - historic

# MRI
change_2071_2100_126_mri <- proj_2071_2100_126_mri - historic

# UKESM
change_2071_2100_126_ukesm <- proj_2071_2100_126_ukesm - historic
```

# View change maps

```{r}
# GFDL
plot(change_2071_2100_126_gfdl)

# IPSL
plot(change_2071_2100_126_ipsl)

# MPI
plot(change_2071_2100_126_mpi)

# MRI
plot(change_2071_2100_126_mri)

# UKESM
plot(change_2071_2100_126_ukesm)
```

# Save change maps to Google Drive

```{r}
# GFDL 
writeRaster(change_2071_2100_126_gfdl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_126_gfdl.tif")), overwrite = FALSE)

# IPSL
writeRaster(change_2071_2100_126_ipsl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_126_ipsl.tif")), overwrite = FALSE)

# MPI
writeRaster(change_2071_2100_126_mpi, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_126_mpi.tif")), overwrite = FALSE)

# MRI
writeRaster(change_2071_2100_126_mri, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_126_mri.tif")), overwrite = FALSE)

# UKESM
writeRaster(change_2071_2100_126_ukesm, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_126_ukesm.tif")), overwrite = FALSE)
```


### 2070-2100 ###
### SSP 5 RCP 8.5 ### 

# Read in projected SDMS (10th percentile training presence)

```{r}
# GFDL
proj_2071_2100_585_gfdl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/585/gfdl_2071_2100_585_10p_sdm.tif"))
  
# IPSL
proj_2071_2100_585_ipsl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/585/ipsl_2071_2100_585_10p_sdm.tif"))
  
# MPI
proj_2071_2100_585_mpi <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/585/mpi_2071_2100_585_10p_sdm.tif"))
  
# MRI
proj_2071_2100_585_mri <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/585/mri_2071_2100_585_10p_sdm.tif"))
  
# UKESM
proj_2071_2100_585_ukesm <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/585/ukesm_2071_2100_585_10p_sdm.tif"))
```

# Reclasify projected rasters

```{r}
# GFDL
proj_2071_2100_585_gfdl[proj_2071_2100_585_gfdl == 0] <- 2
proj_2071_2100_585_gfdl[proj_2071_2100_585_gfdl == 1] <- 4

# IPSL
proj_2071_2100_585_ipsl[proj_2071_2100_585_ipsl == 0] <- 2
proj_2071_2100_585_ipsl[proj_2071_2100_585_ipsl == 1] <- 4

# MPI
proj_2071_2100_585_mpi[proj_2071_2100_585_mpi == 0] <- 2
proj_2071_2100_585_mpi[proj_2071_2100_585_mpi == 1] <- 4

# MRI
proj_2071_2100_585_mri[proj_2071_2100_585_mri == 0] <- 2
proj_2071_2100_585_mri[proj_2071_2100_585_mri == 1] <- 4

# UKESM
proj_2071_2100_585_ukesm[proj_2071_2100_585_ukesm == 0] <- 2
proj_2071_2100_585_ukesm[proj_2071_2100_585_ukesm == 1] <- 4
```

# Subtract historic from projected rasters

```{r}
# GFDL
change_2071_2100_585_gfdl <- proj_2071_2100_585_gfdl - historic

# IPSL
change_2071_2100_585_ipsl <- proj_2071_2100_585_ipsl - historic

# MPI
change_2071_2100_585_mpi <- proj_2071_2100_585_mpi - historic

# MRI
change_2071_2100_585_mri <- proj_2071_2100_585_mri - historic

# UKESM
change_2071_2100_585_ukesm <- proj_2071_2100_585_ukesm - historic
```

# View change maps

```{r}
# GFDL
plot(change_2071_2100_585_gfdl)

# IPSL
plot(change_2071_2100_585_ipsl)

# MPI
plot(change_2071_2100_585_mpi)

# MRI
plot(change_2071_2100_585_mri)

# UKESM
plot(change_2071_2100_585_ukesm)
```

# Save change maps to Google Drive

```{r}
# GFDL 
writeRaster(change_2071_2100_585_gfdl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_585_gfdl.tif")), overwrite = FALSE)

# IPSL
writeRaster(change_2071_2100_585_ipsl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_585_ipsl.tif")), overwrite = FALSE) 

# MPI
writeRaster(change_2071_2100_585_mpi, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_585_mpi.tif")), overwrite = FALSE)

# MRI
writeRaster(change_2071_2100_585_mri, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_585_mri.tif")), overwrite = FALSE)

# UKESM
writeRaster(change_2071_2100_585_ukesm, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_585_ukesm.tif")), overwrite = FALSE)
```

### 2071-2100 ###
### SSP 3 RCP 7.0 ### 

# Read in projected SDMS (10th percentile training presence)
```{r}
# GFDL
proj_2071_2100_370_gfdl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/370/gfdl_2071_2100_370_10p_sdm.tif"))
  
# IPSL
proj_2071_2100_370_ipsl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/370/ipsl_2071_2100_370_10p_sdm.tif"))
  
# MPI
proj_2071_2100_370_mpi <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/370/mpi_2071_2100_370_10p_sdm.tif"))
  
# MRI
proj_2071_2100_370_mri <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/370/mri_2071_2100_370_10p_sdm.tif"))
  
# UKESM
proj_2071_2100_370_ukesm <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/370/ukesm_2071_2100_370_10p_sdm.tif"))
```

# Reclasify projected rasters
```{r}
# GFDL
proj_2071_2100_370_gfdl[proj_2071_2100_370_gfdl == 0] <- 2
proj_2071_2100_370_gfdl[proj_2071_2100_370_gfdl == 1] <- 4

# IPSL
proj_2071_2100_370_ipsl[proj_2071_2100_370_ipsl == 0] <- 2
proj_2071_2100_370_ipsl[proj_2071_2100_370_ipsl == 1] <- 4

# MPI
proj_2071_2100_370_mpi[proj_2071_2100_370_mpi == 0] <- 2
proj_2071_2100_370_mpi[proj_2071_2100_370_mpi == 1] <- 4

# MRI
proj_2071_2100_370_mri[proj_2071_2100_370_mri == 0] <- 2
proj_2071_2100_370_mri[proj_2071_2100_370_mri == 1] <- 4

# UKESM
proj_2071_2100_370_ukesm[proj_2071_2100_370_ukesm == 0] <- 2
proj_2071_2100_370_ukesm[proj_2071_2100_370_ukesm == 1] <- 4
```

# Subtract historic from projected rasters
```{r}
# GFDL
change_2071_2100_370_gfdl <- proj_2071_2100_370_gfdl - historic

# IPSL
change_2071_2100_370_ipsl <- proj_2071_2100_370_ipsl - historic

# MPI
change_2071_2100_370_mpi <- proj_2071_2100_370_mpi - historic

# MRI
change_2071_2100_370_mri <- proj_2071_2100_370_mri - historic

# UKESM
change_2071_2100_370_ukesm <- proj_2071_2100_370_ukesm - historic
```

# View change maps
```{r}
# GFDL
plot(change_2071_2100_370_gfdl)

# IPSL
plot(change_2071_2100_370_ipsl)

# MPI
plot(change_2071_2100_370_mpi)

# MRI
plot(change_2071_2100_370_mri)

# UKESM
plot(change_2071_2100_370_ukesm)
```

# Save change maps to Google Drive
```{r}
# GFDL 
writeRaster(change_2071_2100_370_gfdl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_370_gfdl.tif")), overwrite = FALSE)

# IPSL
writeRaster(change_2071_2100_370_ipsl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_370_ipsl.tif")), overwrite = FALSE) 

# MPI
writeRaster(change_2071_2100_370_mpi, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_370_mpi.tif")), overwrite = FALSE)

# MRI
writeRaster(change_2071_2100_370_mri, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_370_mri.tif")), overwrite = FALSE)

# UKESM
writeRaster(change_2071_2100_370_ukesm, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/change_maps/change_2071_2100_370_ukesm.tif")), overwrite = FALSE)
```

### 2011-2040 ###
### SSP 1 RCP 2.6 ### 

# Read in historic and projected SDMs (10th percentile training presence)

```{r}
# historic 
historic <- raster(paste0(HWC_data, "/Wallace SDM Rasters/asia/1981_2010/asian_elephant_historic_10p_sdm.tif"))
```

```{r}
# GFDL
proj_2011_2040_126_gfdl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/126/gfdl_2011_2040_126_10p_sdm.tif"))
  
# IPSL
proj_2011_2040_126_ipsl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/126/ipsl_2011_2040_126_10p_sdm.tif"))
  
# MPI
proj_2011_2040_126_mpi <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/126/mpi_2011_2040_126_10p_sdm.tif"))
  
# MRI
proj_2011_2040_126_mri <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/126/mri_2011_2040_126_10p_sdm.tif"))
  
# UKESM
proj_2011_2040_126_ukesm <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/126/ukesm_2011_2040_126_10p_sdm.tif"))
```

# Reclasify projected rasters

```{r}
# GFDL
proj_2011_2040_126_gfdl[proj_2011_2040_126_gfdl == 0] <- 2
proj_2011_2040_126_gfdl[proj_2011_2040_126_gfdl == 1] <- 4

# IPSL
proj_2011_2040_126_ipsl[proj_2011_2040_126_ipsl == 0] <- 2
proj_2011_2040_126_ipsl[proj_2011_2040_126_ipsl == 1] <- 4

# MPI
proj_2011_2040_126_mpi[proj_2011_2040_126_mpi == 0] <- 2
proj_2011_2040_126_mpi[proj_2011_2040_126_mpi == 1] <- 4

# MRI
proj_2011_2040_126_mri[proj_2011_2040_126_mri == 0] <- 2
proj_2011_2040_126_mri[proj_2011_2040_126_mri == 1] <- 4

# UKESM
proj_2011_2040_126_ukesm[proj_2011_2040_126_ukesm == 0] <- 2
proj_2011_2040_126_ukesm[proj_2011_2040_126_ukesm == 1] <- 4
```

***NOTE***: Under this setup where we are manually giving the binomial raster these values, after subtracting the historic SDM from the projected SDM the numeric categories assigned to the rasters can be translated accordingly:
  1: Decreasing suitability
  2: No change; not suitable
  3: No change; suitable
  4: Increasing suitability

# Subtract historic from projected rasters

```{r}
# GFDL
change_2011_2040_126_gfdl <- proj_2011_2040_126_gfdl - historic

# IPSL
change_2011_2040_126_ipsl <- proj_2011_2040_126_ipsl - historic

# MPI
change_2011_2040_126_mpi <- proj_2011_2040_126_mpi - historic

# MRI
change_2011_2040_126_mri <- proj_2011_2040_126_mri - historic

# UKESM
change_2011_2040_126_ukesm <- proj_2011_2040_126_ukesm - historic
```

# View change maps

```{r}
# GFDL
plot(change_2011_2040_126_gfdl)

# IPSL
plot(change_2011_2040_126_ipsl)

# MPI
plot(change_2011_2040_126_mpi)

# MRI
plot(change_2011_2040_126_mri)

# UKESM
plot(change_2011_2040_126_ukesm)
```

# Save change maps to Google Drive

```{r}
# GFDL 
writeRaster(change_2011_2040_126_gfdl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_126_gfdl.tif")), overwrite = FALSE)

# IPSL
writeRaster(change_2011_2040_126_ipsl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_126_ipsl.tif")), overwrite = FALSE)

# MPI
writeRaster(change_2011_2040_126_mpi, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_126_mpi.tif")), overwrite = FALSE)

# MRI
writeRaster(change_2011_2040_126_mri, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_126_mri.tif")), overwrite = FALSE)

# UKESM
writeRaster(change_2011_2040_126_ukesm, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_126_ukesm.tif")), overwrite = FALSE)
```

### 2011-2040 ###
### SSP 5 RCP 8.5 ### 

# Read in projected SDMS (10th percentile training presence)

```{r}
# GFDL
proj_2011_2040_585_gfdl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/585/gfdl_2011_2040_585_10p_sdm.tif"))
  
# IPSL
proj_2011_2040_585_ipsl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/585/ipsl_2011_2040_585_10p_sdm.tif"))
  
# MPI
proj_2011_2040_585_mpi <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/585/mpi_2011_2040_585_10p_sdm.tif"))
  
# MRI
proj_2011_2040_585_mri <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/585/mri_2011_2040_585_10p_sdm.tif"))
  
# UKESM
proj_2011_2040_585_ukesm <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/585/ukesm_2011_2040_585_10p_sdm.tif"))
```

# Reclasify projected rasters

```{r}
# GFDL
proj_2011_2040_585_gfdl[proj_2011_2040_585_gfdl == 0] <- 2
proj_2011_2040_585_gfdl[proj_2011_2040_585_gfdl == 1] <- 4

# IPSL
proj_2011_2040_585_ipsl[proj_2011_2040_585_ipsl == 0] <- 2
proj_2011_2040_585_ipsl[proj_2011_2040_585_ipsl == 1] <- 4

# MPI
proj_2011_2040_585_mpi[proj_2011_2040_585_mpi == 0] <- 2
proj_2011_2040_585_mpi[proj_2011_2040_585_mpi == 1] <- 4

# MRI
proj_2011_2040_585_mri[proj_2011_2040_585_mri == 0] <- 2
proj_2011_2040_585_mri[proj_2011_2040_585_mri == 1] <- 4

# UKESM
proj_2011_2040_585_ukesm[proj_2011_2040_585_ukesm == 0] <- 2
proj_2011_2040_585_ukesm[proj_2011_2040_585_ukesm == 1] <- 4
```

# Subtract historic from projected rasters

```{r}
# GFDL
change_2011_2040_585_gfdl <- proj_2011_2040_585_gfdl - historic

# IPSL
change_2011_2040_585_ipsl <- proj_2011_2040_585_ipsl - historic

# MPI
change_2011_2040_585_mpi <- proj_2011_2040_585_mpi - historic

# MRI
change_2011_2040_585_mri <- proj_2011_2040_585_mri - historic

# UKESM
change_2011_2040_585_ukesm <- proj_2011_2040_585_ukesm - historic
```

# View change maps

```{r}
# GFDL
plot(change_2011_2040_585_gfdl)

# IPSL
plot(change_2011_2040_585_ipsl)

# MPI
plot(change_2011_2040_585_mpi)

# MRI
plot(change_2011_2040_585_mri)

# UKESM
plot(change_2011_2040_585_ukesm)
```

# Save change maps to Google Drive

```{r}
# GFDL 
writeRaster(change_2011_2040_585_gfdl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_585_gfdl.tif")), overwrite = FALSE)

# IPSL
writeRaster(change_2011_2040_585_ipsl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_585_ipsl.tif")), overwrite = FALSE) 

# MPI
writeRaster(change_2011_2040_585_mpi, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_585_mpi.tif")), overwrite = FALSE)

# MRI
writeRaster(change_2011_2040_585_mri, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_585_mri.tif")), overwrite = FALSE)

# UKESM
writeRaster(change_2011_2040_585_ukesm, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_585_ukesm.tif")), overwrite = FALSE)
```

### 2011-2040 ###
### SSP 3 RCP 7.0 ### 

# Read in projected SDMS (10th percentile training presence)
```{r}
# GFDL
proj_2011_2040_370_gfdl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/370/gfdl_2011_2040_370_10p_sdm.tif"))
  
# IPSL
proj_2011_2040_370_ipsl <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/370/ipsl_2011_2040_370_10p_sdm.tif"))
  
# MPI
proj_2011_2040_370_mpi <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/370/mpi_2011_2040_370_10p_sdm.tif"))
  
# MRI
proj_2011_2040_370_mri <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/370/mri_2011_2040_370_10p_sdm.tif"))
  
# UKESM
proj_2011_2040_370_ukesm <- raster(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/370/ukesm_2011_2040_370_10p_sdm.tif"))
```

# Reclasify projected rasters
```{r}
# GFDL
proj_2011_2040_370_gfdl[proj_2011_2040_370_gfdl == 0] <- 2
proj_2011_2040_370_gfdl[proj_2011_2040_370_gfdl == 1] <- 4

# IPSL
proj_2011_2040_370_ipsl[proj_2011_2040_370_ipsl == 0] <- 2
proj_2011_2040_370_ipsl[proj_2011_2040_370_ipsl == 1] <- 4

# MPI
proj_2011_2040_370_mpi[proj_2011_2040_370_mpi == 0] <- 2
proj_2011_2040_370_mpi[proj_2011_2040_370_mpi == 1] <- 4

# MRI
proj_2011_2040_370_mri[proj_2011_2040_370_mri == 0] <- 2
proj_2011_2040_370_mri[proj_2011_2040_370_mri == 1] <- 4

# UKESM
proj_2011_2040_370_ukesm[proj_2011_2040_370_ukesm == 0] <- 2
proj_2011_2040_370_ukesm[proj_2011_2040_370_ukesm == 1] <- 4
```

# Subtract historic from projected rasters
```{r}
# GFDL
change_2011_2040_370_gfdl <- proj_2011_2040_370_gfdl - historic

# IPSL
change_2011_2040_370_ipsl <- proj_2011_2040_370_ipsl - historic

# MPI
change_2011_2040_370_mpi <- proj_2011_2040_370_mpi - historic

# MRI
change_2011_2040_370_mri <- proj_2011_2040_370_mri - historic

# UKESM
change_2011_2040_370_ukesm <- proj_2011_2040_370_ukesm - historic
```

# View change maps
```{r}
# GFDL
plot(change_2011_2040_370_gfdl)

# IPSL
plot(change_2011_2040_370_ipsl)

# MPI
plot(change_2011_2040_370_mpi)

# MRI
plot(change_2011_2040_370_mri)

# UKESM
plot(change_2011_2040_370_ukesm)
```

# Save change maps to Google Drive
```{r}
# GFDL 
writeRaster(change_2011_2040_370_gfdl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_370_gfdl.tif")), overwrite = FALSE)

# IPSL
writeRaster(change_2011_2040_370_ipsl, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_370_ipsl.tif")), overwrite = FALSE) 

# MPI
writeRaster(change_2011_2040_370_mpi, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_370_mpi.tif")), overwrite = FALSE)

# MRI
writeRaster(change_2011_2040_370_mri, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_370_mri.tif")), overwrite = FALSE)

# UKESM
writeRaster(change_2011_2040_370_ukesm, filename = file.path(paste0(HWC_data,"/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_370_ukesm.tif")), overwrite = FALSE)
```














