---
title: "Asia Wallace Output & More"
author: "Grace Kumaishi"
date: "7/15/2022"
output: html_document
---

Below is the R code history from a *Wallace* v1.1.0 session.

### Package installation

Wallace uses the following R packages that must be installed and loaded
before starting.

```{r}
library(spocc)
library(spThin)
library(dismo)
library(rgeos)
library(ENMeval)
library(dplyr)
library(here)

# Enter data path to YOUR HWC_data folder, including "HWC_data". 
# May require double forward slashes
HWC_data <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data" 
```

Wallace also includes several functions developed to help integrate
different packages and some additional functionality. For this reason,
it is necessary to load the file `functions.R`, The function
`system.file()` finds this script, and `source()` loads it.

```{r}
source(system.file('shiny/funcs', 'functions.R', package = 'wallace'))
```

## Record of analysis for \*\*.

User CSV path with occurrence data. If the CSV file is not in the
current workspace, change to the correct file path
(e.g. “/Users/darwin/Documents/occs.csv”).

```{r}
# NOTE: provide the path to the folder that contains the CSV file
d.occs <- paste0(HWC_data, '/Data/Asian_Elephant/')

# create path to user occurrences csv file
userOccs.path <- file.path(d.occs, "all_combined_asian_elephant_coords.csv")

# read in csv
userOccs.csv <- read.csv(userOccs.path, header = TRUE)

# remove rows with duplicate coordinates
occs.dups <- duplicated(userOccs.csv[c('longitude', 'latitude')])
occs <- userOccs.csv[!occs.dups,]

# remove NAs
occs <- occs[complete.cases(occs$longitude, occs$latitude), ]

# give all records a unique ID
occs$occID <- row.names(occs)
```

### Obtain Environmental Data

```{r}
# NOTE: provide the path to the folder that contains the rasters
d.envs <- paste0(HWC_data, '/Data/Chelsa_Data/asia_masked_CHELSA_data')

# create paths to the raster files
userRas.paths <- file.path(d.envs, c('asia_masked_CHELSA_layer01.tif','asia_masked_CHELSA_layer02.tif', 'asia_masked_CHELSA_layer04.tif', 'asia_masked_CHELSA_layer06.tif', 'asia_masked_CHELSA_layer07.tif', 'asia_masked_CHELSA_layer12.tif', 'asia_masked_CHELSA_layer14.tif', 'asia_masked_CHELSA_layer15.tif'))

# make a RasterStack out of the raster files
envs <- raster::stack(userRas.paths)
```

### Process Environmental Data

Background selection technique chosen as .

Read in the .shp file and generate a Spatial Polygon object.

```{r}
# NOTE: provide the path to the folder that contains the shapefile
d.bg <- paste0(HWC_data, '/R_files/R_output_data/indomalay_region')
# read csv with coordinates for polygon
bgExt <- rgdal::readOGR(d.bg, "indomalay_region")
```

Mask environmental variables by , and take a random sample of background
values from the study extent. As the sample is random, your results may
be different than those in the session. If there seems to be too much
variability in these background samples, try increasing the number from
10,000 to something higher (e.g. 50,000 or 100,000). The better your
background sample, the less variability you’ll have between runs.

```{r}
# crop the environmental rasters by the background extent shape
envsBgCrop <- raster::crop(envs, bgExt)

# mask the background extent shape from the cropped raster
envsBgMsk <- raster::mask(envsBgCrop, bgExt)

# sample random background points
bg.xy <- dismo::randomPoints(envsBgMsk, 10000)

# convert matrix output to data frame
bg.xy <- as.data.frame(bg.xy)  
colnames(bg.xy) <- c("longitude", "latitude")
```

### Partition Occurrence Data

Occurrence data is now partitioned for cross-validation, a method that
iteratively builds a model on all but one group and evaluates that model
on the left-out group.

For example, if the data is partitioned into 3 groups A, B, and C, a
model is first built with groups A and B and is evaluated on C. This is
repeated by building a model with B and C and evaluating on A, and so on
until all combinations are done.

Cross-validation operates under the assumption that the groups are
independent of each other, which may or may not be a safe assumption for
your dataset. Spatial partitioning is one way to ensure more
independence between groups.

You selected to partition your occurrence data by the method.

```{r}
occs.xy <- occs[c('longitude', 'latitude')]
group.data <- ENMeval::get.checkerboard2(occ = occs.xy, env = envsBgMsk,
                                         bg = bg.xy, aggregation.factor = 2)
```

```{r}
# pull out the occurrence and background partition group numbers from the list
occs.grp <- group.data[[1]]
bg.grp <- group.data[[2]]
```

### Build and Evaluate Niche Model

You selected the maxent model.

```{r}
# define the vector of regularization multipliers to test
rms <- seq(0.5, 1, 0.5)

# iterate model building over all chosen parameter settings
e <- ENMeval::ENMevaluate(occ = occs.xy, env = envsBgMsk, bg.coords = bg.xy,
                          RMvalues = rms, fc = c('L', 'LQ'), method = 'user', 
                          occ.grp = occs.grp, bg.grp = bg.grp, 
                          clamp = TRUE, algorithm = "maxnet")

# unpack the results data frame, the list of models, and the RasterStack of raw predictions
evalTbl <- e@results
evalMods <- e@models
names(evalMods) <- e@tune.settings$tune.args
evalPreds <- e@predictions
```

```{r}
# view ENMeval results
ENMeval::evalplot.stats(e, stats = "auc.val", "rm", "fc")
```

```{r}
# Select your model from the models list
mod <- evalMods[["rm.0.5_fc.LQ"]]
```

```{r}
# generate cloglog prediction
pred <- predictMaxnet(mod, envsBgMsk, type = 'cloglog', clamp = TRUE) 
```

```{r}
# generate raw prediction
pred_raw <- evalPreds[["rm.0.5_fc.LQ"]]

# save raw prediction as raster
asian_elephant_historic_raw <- writeRaster(pred_raw, filename = file.path(here(HWC_data, "/Wallace SDM Rasters/asia/1981_2010/asian_elephant_historic_raw.tif")), overwrite = FALSE)
```

```{r}
# get predicted values for occurrence grid cells
occPredVals <- raster::extract(pred, occs.xy)
# define minimum training presence threshold
thr <- thresh(occPredVals, "p10")
# threshold model prediction
pred_thr <- pred > thr
```

```{r}
# generate response curves
plot(evalMods[["rm.0.5_fc.LQ"]], type = "cloglog")
```

```{r}
# plot the model prediction
plot(pred_thr)
#points(occs.xy$longitude, occs.xy$latitude, col = "black")

plot(pred)
#points(occs.xy$longitude, occs.xy$latitude, col = "black")

# save as raster
asian_elephant_historic_10p_sdm <- writeRaster(pred_thr, filename = file.path(here(HWC_data, "/Wallace SDM Rasters/asia/1981_2010/asian_elephant_historic_10p_sdm.tif")), overwrite = FALSE)
```

### Project Niche Model to New Time

Now download the future climate variables chosen with *Wallace*, crop
and mask them by projPoly, and use the maxnet.predictRaster() function
to predict the values for the new time based on the model selected.

```{r}
# NOTE: provide the path to the folder that contains the rasters
d.envsFuture <- paste0(HWC_data, '/R_files/R_output_data/chelsa_asia/2071_2100/585/UKESM1_0_LL')

# create paths to the raster files
userRas.pathsFuture <- file.path(d.envsFuture, c('ukesm_2071_2100_585_bio1.tif','ukesm_2071_2100_585_bio2.tif', 'ukesm_2071_2100_585_bio4.tif', 'ukesm_2071_2100_585_bio6.tif', 'ukesm_2071_2100_585_bio7.tif', 'ukesm_2071_2100_585_bio12.tif', 'ukesm_2071_2100_585_bio14.tif', 'ukesm_2071_2100_585_bio15.tif'))

# make a RasterStack out of the raster files
envsFuture <- raster::stack(userRas.pathsFuture)

presProj <- raster::crop(envsFuture, bgExt)
predsProj <- raster::mask(presProj, bgExt)
```

```{r}
# rename future climate variable names
names(predsProj) <- paste0('asia_masked_CHELSA_layer', sprintf("%02d", c(1, 2, 4, 6, 7, 12, 14, 15)))
```

```{r}
# predict model
proj <- predictMaxnet(mod, predsProj, type = 'cloglog', clamp = TRUE)
```

```{r}
# get predicted values for occurrence grid cells
occPredVals <- raster::extract(pred, occs.xy)
# define minimum training presence threshold
thr <- thresh(occPredVals, "p10")
# threshold model prediction
proj_thr <- proj > thr
```

```{r}
# plot the model prediction
plot(proj_thr)
plot(proj)

# # save as raster (continuous)
# ukesm_2071_2100_585_sdm <- writeRaster(proj, filename = file.path("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Wallace SDM Rasters/asia/2071_2100/585/ukesm_2071_2100_585_sdm.tif"), overwrite = FALSE)
# 
# # save as raster (10th percentile threshold)
# ukesm_2071_2100_585_10p_sdm <- writeRaster(proj_thr, filename = file.path("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Wallace SDM Rasters/asia/2071_2100/585/ukesm_2041_2070_585_10p_sdm.tif"), overwrite = FALSE)
```

## Plot model agreement (2071-2100)
```{r}
### 2071-2100 126
#read in 10 percentile threshold tifs
all_2071_2100_126 <- here(HWC_data, c("/Wallace SDM Rasters/asia/2071_2100/126/gfdl_2071_2100_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/126/ipsl_2071_2100_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/126/mpi_2071_2100_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/126/mri_2071_2100_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/126/ukesm_2071_2100_126_10p_sdm.tif"))
 
all_2071_2100_126_stack <- stack(all_2071_2100_126)
 
all_2071_2100_126_model_agreement <- calc(all_2071_2100_126_stack, sum)

plot(all_2071_2100_126_model_agreement)

# save as raster (10 percentile threshold - model agreement)
#all_2071_2100_126_10p_sdm <- writeRaster(all_2071_2100_126_model_agreement, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2071_2100/126/all_2071_2100_126_10p_sdm.tif"), overwrite = FALSE) 

# reclassify
all_2071_2100_126_model_agreement_reclass <- all_2071_2100_126_model_agreement
all_2071_2100_126_model_agreement_reclass[all_2071_2100_126_model_agreement_reclass %in% c(0, 1, 2)] <- 0
all_2071_2100_126_model_agreement_reclass[all_2071_2100_126_model_agreement_reclass %in% c(3, 4, 5)] <- 1

plot(all_2071_2100_126_model_agreement_reclass)

# # save as binary raster
#all_2071_2100_126_01_sdm <- writeRaster(all_2071_2100_126_model_agreement_reclass, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2071_2100/126/all_2071_2100_126_01_sdm.tif"), overwrite = FALSE)

### 2071-2100 370
#read in 10 percentile threshold tifs
all_2071_2100_370 <- here(HWC_data, c("/Wallace SDM Rasters/asia/2071_2100/370/gfdl_2071_2100_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/370/ipsl_2071_2100_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/370/mpi_2071_2100_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/370/mri_2071_2100_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/370/ukesm_2071_2100_370_10p_sdm.tif"))
 
all_2071_2100_370_stack <- stack(all_2071_2100_370)
 
all_2071_2100_370_model_agreement <- calc(all_2071_2100_370_stack, sum)

# save as raster (10 percentile threshold - model agreement)
#all_2071_2100_370_10p_sdm <- writeRaster(all_2071_2100_370_model_agreement, filename = here(HWC_data,"/Wallace SDM Rasters/asia/2071_2100/370/all_2071_2100_370_10p_sdm.tif"), overwrite = FALSE)

# reclassify
all_2071_2100_370_model_agreement_reclass <- all_2071_2100_370_model_agreement
all_2071_2100_370_model_agreement_reclass[all_2071_2100_370_model_agreement_reclass %in% c(0, 1, 2)] <- 0
all_2071_2100_370_model_agreement_reclass[all_2071_2100_370_model_agreement_reclass %in% c(3, 4, 5)] <- 1

# save as binary raster
#all_2071_2100_370_01_sdm <- writeRaster(all_2071_2100_370_model_agreement_reclass, filename = here(HWC_data, "//Wallace SDM Rasters/asia/2071_2100/370/all_2071_2100_370_01_sdm.tif"), overwrite = FALSE)

### 2071-2100 585
#read in 10 percentile threshold tifs
all_2071_2100_585 <- here(HWC_data, c("/Wallace SDM Rasters/asia/2071_2100/585/gfdl_2071_2100_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/585/ipsl_2071_2100_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/585/mpi_2071_2100_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/585/mri_2071_2100_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2071_2100/585/ukesm_2071_2100_585_10p_sdm.tif"))
 
all_2071_2100_585_stack <- stack(all_2071_2100_585)
 
all_2071_2100_585_model_agreement <- calc(all_2071_2100_585_stack, sum)

# save as raster (10 percentile threshold - model agreement)
#all_2071_2100_585_10p_sdm <- writeRaster(all_2071_2100_585_model_agreement, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2071_2100/585/all_2071_2100_585_10p_sdm.tif"), overwrite = FALSE)

# reclassify
all_2071_2100_585_model_agreement_reclass <- all_2071_2100_585_model_agreement
all_2071_2100_585_model_agreement_reclass[all_2071_2100_585_model_agreement_reclass %in% c(0, 1, 2)] <- 0
all_2071_2100_585_model_agreement_reclass[all_2071_2100_585_model_agreement_reclass %in% c(3, 4, 5)] <- 1

# save as binary raster
#all_2071_2100_585_01_sdm <- writeRaster(all_2071_2100_585_model_agreement_reclass, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2071_2100/585/all_2071_2100_585_01_sdm.tif"), overwrite = FALSE)
```

## Plot model agreement (2041-2070)
```{r}
### 2041-2070 126
#read in 10 percentile threshold tifs
all_2041_2070_126 <- here(HWC_data, c("/Wallace SDM Rasters/asia/2041_2070/126/gfdl_2041_2070_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/126/ipsl_2041_2070_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/126/mpi_2041_2070_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/126/mri_2041_2070_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/126/ukesm_2041_2070_126_10p_sdm.tif"))
 
all_2041_2070_126_stack <- stack(all_2041_2070_126)
 
all_2041_2070_126_model_agreement <- calc(all_2041_2070_126_stack, sum)

# save as raster (10 percentile threshold - model agreement)
#all_2041_2070_126_10p_sdm <- writeRaster(all_2041_2070_126_model_agreement, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2041_2070/126/all_2041_2070_126_10p_sdm.tif"), overwrite = FALSE)

# reclassify
all_2041_2070_126_model_agreement_reclass <- all_2041_2070_126_model_agreement
all_2041_2070_126_model_agreement_reclass[all_2041_2070_126_model_agreement_reclass %in% c(0, 1, 2)] <- 0
all_2041_2070_126_model_agreement_reclass[all_2041_2070_126_model_agreement_reclass %in% c(3, 4, 5)] <- 1

# save as binary raster
#all_2041_2070_126_10p_01_sdm <- writeRaster(all_2041_2070_126_model_agreement_reclass, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2041_2070/126/all_2041_2070_126_10p_01_sdm.tif"), overwrite = FALSE)

### 2041-2070 370
#read in 10 percentile threshold tifs
all_2041_2070_370 <- here(HWC_data, c("/Wallace SDM Rasters/asia/2041_2070/370/gfdl_2041_2070_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/370/ipsl_2041_2070_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/370/mpi_2041_2070_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/370/mri_2041_2070_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/370/ukesm_2041_2070_370_10p_sdm.tif"))
 
all_2041_2070_370_stack <- stack(all_2041_2070_370)
 
all_2041_2070_370_model_agreement <- calc(all_2041_2070_370_stack, sum)

# save as raster (10 percentile threshold - model agreement)
#all_2041_2070_370_10p_sdm <- writeRaster(all_2041_2070_370_model_agreement, filename = file.path("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Wallace SDM Rasters/asia/2041_2070/370/all_2041_2070_370_10p_sdm.tif"), overwrite = FALSE)

# reclassify
all_2041_2070_370_model_agreement_reclass <- all_2041_2070_370_model_agreement
all_2041_2070_370_model_agreement_reclass[all_2041_2070_370_model_agreement_reclass %in% c(0, 1, 2)] <- 0
all_2041_2070_370_model_agreement_reclass[all_2041_2070_370_model_agreement_reclass %in% c(3, 4, 5)] <- 1

# save as binary raster
#all_2041_2070_370_10p_01_sdm <- writeRaster(all_2041_2070_370_model_agreement_reclass, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2041_2070/370/all_2041_2070_370_10p_01_sdm.tif"), overwrite = FALSE)

### 2041-2070 585
#read in 10 percentile threshold tifs
all_2041_2070_585 <- here(HWC_data, c("/Wallace SDM Rasters/asia/2041_2070/585/gfdl_2041_2070_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/585/ipsl_2041_2070_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/585/mpi_2041_2070_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/585/mri_2041_2070_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2041_2070/585/ukesm_2041_2070_585_10p_sdm.tif"))
 
all_2041_2070_585_stack <- stack(all_2041_2070_585)
 
all_2041_2070_585_model_agreement <- calc(all_2041_2070_585_stack, sum)

# save as raster (10 percentile threshold - model agreement)
#all_2041_2070_585_10p_sdm <- writeRaster(all_2041_2070_585_model_agreement, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2041_2070/585/all_2041_2070_585_10p_sdm.tif"), overwrite = FALSE)

# reclassify
all_2041_2070_585_model_agreement_reclass <- all_2041_2070_585_model_agreement
all_2041_2070_585_model_agreement_reclass[all_2041_2070_585_model_agreement_reclass %in% c(0, 1, 2)] <- 0
all_2041_2070_585_model_agreement_reclass[all_2041_2070_585_model_agreement_reclass %in% c(3, 4, 5)] <- 1

# save as binary raster
#all_2041_2070_585_10p_01_sdm <- writeRaster(all_2041_2070_585_model_agreement_reclass, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2041_2070/585/all_2041_2070_585_10p_01_sdm.tif"), overwrite = FALSE)
```

## Plot model agreement (2011-2040)
```{r}
### 2011-2040 126
#read in 10 percentile threshold tifs
all_2011_2040_126 <- here(HWC_data, c("/Wallace SDM Rasters/asia/2011_2040/126/gfdl_2011_2040_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/126/ipsl_2011_2040_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/126/mpi_2011_2040_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/126/mri_2011_2040_126_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/126/ukesm_2011_2040_126_10p_sdm.tif"))
 
all_2011_2040_126_stack <- stack(all_2011_2040_126)
 
all_2011_2040_126_model_agreement <- calc(all_2011_2040_126_stack, sum)

# save as raster (10 percentile threshold - model agreement)
all_2011_2040_126_10p_sdm <- writeRaster(all_2011_2040_126_model_agreement, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2011_2040/126/all_2011_2040_126_10p_sdm.tif"), overwrite = FALSE)

# reclassify
all_2011_2040_126_model_agreement_reclass <- all_2011_2040_126_model_agreement
all_2011_2040_126_model_agreement_reclass[all_2011_2040_126_model_agreement_reclass %in% c(0, 1, 2)] <- 0
all_2011_2040_126_model_agreement_reclass[all_2011_2040_126_model_agreement_reclass %in% c(3, 4, 5)] <- 1

# save as binary raster
all_2011_2040_126_10p_01_sdm <- writeRaster(all_2011_2040_126_model_agreement_reclass, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2011_2040/126/all_2011_2040_126_10p_01_sdm.tif"), overwrite = FALSE)

### 2011-2040 370
#read in 10 percentile threshold tifs
all_2011_2040_370 <- here(HWC_data, c("/Wallace SDM Rasters/asia/2011_2040/370/gfdl_2011_2040_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/370/ipsl_2011_2040_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/370/mpi_2011_2040_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/370/mri_2011_2040_370_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/370/ukesm_2011_2040_370_10p_sdm.tif"))
 
all_2011_2040_370_stack <- stack(all_2011_2040_370)
 
all_2011_2040_370_model_agreement <- calc(all_2011_2040_370_stack, sum)

# save as raster (10 percentile threshold - model agreement)
all_2011_2040_370_10p_sdm <- writeRaster(all_2011_2040_370_model_agreement, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2011_2040/370/all_2011_2040_370_10p_sdm.tif"), overwrite = FALSE)

# reclassify
all_2011_2040_370_model_agreement_reclass <- all_2011_2040_370_model_agreement
all_2011_2040_370_model_agreement_reclass[all_2011_2040_370_model_agreement_reclass %in% c(0, 1, 2)] <- 0
all_2011_2040_370_model_agreement_reclass[all_2011_2040_370_model_agreement_reclass %in% c(3, 4, 5)] <- 1

# save as binary raster
all_2011_2040_370_10p_01_sdm <- writeRaster(all_2011_2040_370_model_agreement_reclass, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2011_2040/370/all_2011_2040_370_10p_01_sdm.tif"), overwrite = FALSE)

### 2011-2040 585
#read in 10 percentile threshold tifs
all_2011_2040_585 <- here(HWC_data, c("/Wallace SDM Rasters/asia/2011_2040/585/gfdl_2011_2040_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/585/ipsl_2011_2040_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/585/mpi_2011_2040_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/585/mri_2011_2040_585_10p_sdm.tif",
               "/Wallace SDM Rasters/asia/2011_2040/585/ukesm_2011_2040_585_10p_sdm.tif"))
 
all_2011_2040_585_stack <- stack(all_2011_2040_585)
 
all_2011_2040_585_model_agreement <- calc(all_2011_2040_585_stack, sum)

# save as raster (10 percentile threshold - model agreement)
all_2011_2040_585_10p_sdm <- writeRaster(all_2011_2040_585_model_agreement, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2011_2040/585/all_2011_2040_585_10p_sdm.tif"), overwrite = FALSE)

# reclassify
all_2011_2040_585_model_agreement_reclass <- all_2011_2040_585_model_agreement
all_2011_2040_585_model_agreement_reclass[all_2011_2040_585_model_agreement_reclass %in% c(0, 1, 2)] <- 0
all_2011_2040_585_model_agreement_reclass[all_2011_2040_585_model_agreement_reclass %in% c(3, 4, 5)] <- 1

# save as binary raster
all_2011_2040_585_10p_01_sdm <- writeRaster(all_2011_2040_585_model_agreement_reclass, filename = here(HWC_data, "/Wallace SDM Rasters/asia/2011_2040/585/all_2011_2040_585_10p_01_sdm.tif"), overwrite = FALSE)
```
