---
title: "Asian Elephant Occurrence Data"
author: "Grace Kumaishi"
date: "1/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load packages:
library(tidyverse)
library(rgbif) # interface to GBIF
library(maptools)
library(dismo)
#library(rgeos)
#library(viridis)
library(raster)
library(spocc) # Interface to species occurrence data sources
library(sf)
library(sp)
#library(rgdal)
#library(spData)
#library(lubridate)
#library(kableExtra)
#library(tmap)
library(here)
library(dplyr)
library(ggplot2)
#library(ggbeeswarm)
#library(patchwork)

### Install Wallace:
library(wallace)

### Load Wallace functions:
source(system.file('shiny/funcs', 'functions.R', package = 'wallace'))
```

## Description:

This markdown file outlines the first steps for creating data for species distribution modeling (SDM) with Wallace.

### Download species occurence data and get coordinates

We begin by downloading the species occurrence points for the Asian Elephant subspecies using Wallace's spocc:occ() function. Choose which chunk to run based on the species of interest.

#### Indian Elephant

```{r}
### Gives global records. If limit is set high, this function can take a while to run.
results <- spocc::occ(query = "Elephas maximus indicus", # scientific name
                      from = "gbif", # set to records from https://www.gbif.org/
                      limit = 15000, # max number of records
                      has_coords = TRUE) # gets the lat/long for each observation

### Select just GBIF records, format the species name:
results[["gbif"]]$data[[formatSpName("Elephas maximus indicus")]]

### Select just the necessary information:
indicus_coords <- as.data.frame(results$gbif$data$Elephas_maximus_indicus) %>% # using GBIF data
  dplyr::select(longitude, latitude, occurrenceStatus, coordinateUncertaintyInMeters, institutionCode, references, basisOfRecord, eventDate) %>%  # selecting just the columns that we want
  filter(!basisOfRecord %in% c("FOSSIL_SPECIMEN", "PRESERVED_SPECIMEN", "LIVING_SPECIMEN"),
         occurrenceStatus == "PRESENT",
        eventDate <= "2021-12-31" & eventDate >= "1981-01-01")
```

#### Sri Lankan Elephant

```{r}
### Gives global records.  If limit is set high, this function can take a while to run.
results <- spocc::occ(query = "Elephas maximus maximus", # scientific name
                      from = "gbif", # set to records from https://www.gbif.org/
                      limit = 15000, # max number of records
                      has_coords = TRUE) # gets the lat/long for each observation

### Select just GBIF records, format the species name:
results[["gbif"]]$data[[formatSpName("Elephas maximus maximus")]]

### Select just the necessary information:
maximus_coords <- as.data.frame(results$gbif$data$Elephas_maximus_maximus) %>% # using GBIF data
  dplyr::select(longitude, latitude, occurrenceStatus, coordinateUncertaintyInMeters, institutionCode, references, basisOfRecord, eventDate) %>%  # selecting just the columns that we want
  filter(!basisOfRecord %in% c("FOSSIL_SPECIMEN", "PRESERVED_SPECIMEN", "LIVING_SPECIMEN"),
         occurrenceStatus == "PRESENT",
        eventDate <= "2021-12-31" & eventDate >= "1981-01-01")
```

#### Sumatran Elephant

```{r}
### Gives global records.  If limit is set high, this function can take a while to run.
results <- spocc::occ(query = "Elephas maximus sumatranus", # scientific name
                      from = "gbif", # set to records from https://www.gbif.org/
                      limit = 15000, # max number of records
                      has_coords = TRUE) # gets the lat/long for each observation

### Select just GBIF records, format the species name:
results[["gbif"]]$data[[formatSpName("Elephas maximus sumatranus")]]

### Select just the necessary information:
sumatranus_coords <- as.data.frame(results$gbif$data$Elephas_maximus_sumatranus) %>% # using GBIF data
  dplyr::select(longitude, latitude, occurrenceStatus, coordinateUncertaintyInMeters, institutionCode, references, basisOfRecord, eventDate) %>%  # selecting just the columns that we want
  filter(!basisOfRecord %in% c("FOSSIL_SPECIMEN", "PRESERVED_SPECIMEN", "LIVING_SPECIMEN"),
         occurrenceStatus == "PRESENT",
        eventDate <= "2021-12-31" & eventDate >= "1981-01-01")
```

### Download WWF Terrestrial Ecoregions

```{r}
### Get spatial extent using IndoMalay ecoregion from WWF. Data downloaded from: https://www.worldwildlife.org/publications/terrestrial-ecoregions-of-the-world
# indomalay_region <- read_sf(dsn = "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_input_data/wwf_ecoregions/official", layer = "wwf_terr_ecos") %>% 
#    filter(REALM == "IM")

### Check CRS:
# crs(indomalay_region) #+proj=longlat +datum=WGS84 +no_defs 

# indomalay_region_sp <- as_Spatial(indomalay_region, cast = TRUE)

### Create shapefile for wallace:
#st_write(indomalay_region, dsn = "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/indomalay_region/indomalay_region.shp", layer = "indomalay_region.shp", driver = "ESRI Shapefile")

### Read in shapefile from Google Drive:
indomalay_region <- st_read("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/R_files/R_output_data/indomalay_region/indomalay_region.shp")

indomalay_region_sp <- as_Spatial(indomalay_region, cast = TRUE)

### Check shapefile:
plot(indomalay_region_sp)
crs(indomalay_region_sp)
```

### Clean Data

```{r}
### Remove rows with duplicate coordinates:
occs.dups <- duplicated(indicus_coords[c('longitude', 'latitude')])
indicus_coords <- indicus_coords[!occs.dups,]

occs.dups <- duplicated(maximus_coords[c('longitude', 'latitude')])
maximus_coords <- maximus_coords[!occs.dups,]

occs.dups <- duplicated(sumatranus_coords[c('longitude', 'latitude')])
sumatranus_coords <- sumatranus_coords[!occs.dups,]

### Make sure latitude and longitude are numeric (sometimes they are characters):
indicus_coords$latitude <- as.numeric(indicus_coords$latitude)
indicus_coords$longitude <- as.numeric(indicus_coords$longitude)

maximus_coords$latitude <- as.numeric(maximus_coords$latitude)
maximus_coords$longitude <- as.numeric(maximus_coords$longitude)

sumatranus_coords$latitude <- as.numeric(sumatranus_coords$latitude)
sumatranus_coords$longitude <- as.numeric(sumatranus_coords$longitude)

### Give all records a unique ID:
indicus_coords$occID <- row.names(indicus_coords)
maximus_coords$occID <- row.names(maximus_coords)
sumatranus_coords$occID <- row.names(sumatranus_coords)

### Add species column to each dataset:
indicus_coords$species <- "Indian elephant" 
  
indicus_coords <- indicus_coords %>% 
  relocate(species, .before = longitude)

maximus_coords$species <- "Sri Lankan elephant" 
  
maximus_coords <- maximus_coords %>% 
  relocate(species, .before = longitude)

sumatranus_coords$species <- "Sumatran elephant" 
  
sumatranus_coords <- sumatranus_coords %>% 
  relocate(species, .before = longitude)
```

### Crop data by species range

```{r}
### Turn data frames into sf object in order to crop by range shapefile:
indicus_coords_sf <- st_as_sf(x = indicus_coords,
                              coords = c("longitude", "latitude"),
                              crs = 4326)

maximus_coords_sf <- st_as_sf(x = maximus_coords,
                              coords = c("longitude", "latitude"),
                              crs = 4326)

sumatranus_coords_sf <- st_as_sf(x = sumatranus_coords,
                              coords = c("longitude", "latitude"),
                              crs = 4326)
```

```{r}
### Read in shapefile:
range <- st_read("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Asian_Elephant/redlist_species_data/data_0.shp")

### Crop coordinates by species range file:
cropped_indicus_coords_sf <- indicus_coords_sf[range, op = st_intersects]

cropped_maximus_coords_sf <- maximus_coords_sf[range, op = st_intersects]

cropped_sumatranus_coords_sf <- sumatranus_coords_sf[range, op = st_intersects]

### Crop coordinates by WWF ecoregions shapefile:
cropped_indicus_coords_sf <- cropped_indicus_coords_sf[indomalay_region, op = st_intersects]

cropped_maximus_coords_sf <- cropped_maximus_coords_sf[indomalay_region, op = st_intersects]

cropped_sumatranus_coords_sf <- cropped_sumatranus_coords_sf[indomalay_region, op = st_intersects]
```

```{r}
### Need just lat/long values in two columns to use raster extract, also need separate lat/long columns for the spatial thin below
cropped_indicus_coords_sf <- cropped_indicus_coords_sf %>% # extract lat/long from geometry column in sf object
  dplyr::mutate(longitude = sf::st_coordinates(.)[,1],
                latitude = sf::st_coordinates(.)[,2])

cropped_maximus_coords_sf <- cropped_maximus_coords_sf %>% # extract lat/long from geometry column in sf object
  dplyr::mutate(longitude = sf::st_coordinates(.)[,1],
                latitude = sf::st_coordinates(.)[,2])

cropped_sumatranus_coords_sf <- cropped_sumatranus_coords_sf %>% # extract lat/long from geometry column in sf object
  dplyr::mutate(longitude = sf::st_coordinates(.)[,1],
                latitude = sf::st_coordinates(.)[,2])

### Pull out species, lat, long columns:
cropped_indicus_coords_sf <- cropped_indicus_coords_sf[c("species", "longitude", "latitude")] 

cropped_maximus_coords_sf <- cropped_maximus_coords_sf[c("species", "longitude", "latitude")] 

cropped_sumatranus_coords_sf <- cropped_sumatranus_coords_sf[c("species", "longitude", "latitude")] 

### Drop geometry column that remains:
cropped_indicus_coords_sf <- st_set_geometry(cropped_indicus_coords_sf, NULL)

cropped_maximus_coords_sf <- st_set_geometry(cropped_maximus_coords_sf, NULL)

cropped_sumatranus_coords_sf <- st_set_geometry(cropped_sumatranus_coords_sf, NULL)
```

### Spatial thin

```{r}
library(spThin)

##### Indian Elephant

### Just doing 10 replicates for now, thinning to 10 km
thinned_indicus_coords <- spThin::thin(cropped_indicus_coords_sf, 'longitude', 'latitude', 'species',
                       thin.par = 10, # thinned to 10 km
                       reps = 10, # default on Wallace is 100, but run time is long, so a low number is good for testing
                       locs.thinned.list.return = TRUE, 
                       write.files = FALSE, 
                       verbose = FALSE)

### Find the iteration that returns the max number of occurrences:
indicus_maxThin <- which(sapply(thinned_indicus_coords, nrow) == max(sapply(thinned_indicus_coords, nrow)))

### If there's more than one max, pick the first one:
indicus_maxThin <- thinned_indicus_coords[[ifelse(length(indicus_maxThin) > 1, indicus_maxThin[1], indicus_maxThin)]]  

### Subset data to those thinned records:
thinned_indicus_coords_final <- cropped_indicus_coords_sf[as.numeric(rownames(indicus_maxThin)),]

### Rename species column to "name":
thinned_indicus_coords_final <- as_tibble(thinned_indicus_coords_final) %>% 
  dplyr::rename(name = species)

### Save occs to upload to Wallace if needed
#          all_spp_occs_wallace <- all_spp_occs %>% 
#            dplyr::select(species, longitude, latitude) # change order to match
```

```{r}
##### Sri Lankan Elephant

### Just doing 10 replicates for now, thinning to 10 km
thinned_maximus_coords <- spThin::thin(cropped_maximus_coords_sf, 'longitude', 'latitude', 'species',
                       thin.par = 10, # thinned to 10 km
                       reps = 10, # default on Wallace is 100, but run time is long, so a low number is good for testing
                       locs.thinned.list.return = TRUE, 
                       write.files = FALSE, 
                       verbose = FALSE)

### Find the iteration that returns the max number of occurrences:
maximus_maxThin <- which(sapply(thinned_maximus_coords, nrow) == max(sapply(thinned_maximus_coords, nrow)))

### If there's more than one max, pick the first one:
maximus_maxThin <- thinned_maximus_coords[[ifelse(length(maximus_maxThin) > 1, maximus_maxThin[1], maximus_maxThin)]]  

### Subset data to those thinned records:
thinned_maximus_coords_final <- cropped_maximus_coords_sf[as.numeric(rownames(maximus_maxThin)),]

### Rename species column to "name":
thinned_maximus_coords_final <- as_tibble(thinned_maximus_coords_final) %>% 
  dplyr::rename(name = species)
```

```{r}
##### Sumatran Elephant

### Just doing 10 replicates for now, thinning to 10 km
thinned_sumatranus_coords <- spThin::thin(cropped_sumatranus_coords_sf, 'longitude', 'latitude', 'species',
                       thin.par = 10, # thinned to 10 km
                       reps = 10, # default on Wallace is 100, but run time is long, so a low number is good for testing
                       locs.thinned.list.return = TRUE, 
                       write.files = FALSE, 
                       verbose = FALSE)

### Find the iteration that returns the max number of occurrences:
sumatranus_maxThin <- which(sapply(thinned_sumatranus_coords, nrow) == max(sapply(thinned_sumatranus_coords, nrow)))

### If there's more than one max, pick the first one:
sumatranus_maxThin <- thinned_sumatranus_coords[[ifelse(length(sumatranus_maxThin) > 1, sumatranus_maxThin[1], sumatranus_maxThin)]]  

### Subset data to those thinned records:
thinned_sumatranus_coords_final <- cropped_sumatranus_coords_sf[as.numeric(rownames(sumatranus_maxThin)),]

### Rename species column to "name":
thinned_sumatranus_coords_final <- as_tibble(thinned_sumatranus_coords_final) %>% 
  dplyr::rename(name = species)
```

### Map occurrence data

```{r}
thinned_indicus_coords_sf <- st_as_sf(x = thinned_indicus_coords_final,
                              coords = c("longitude", "latitude"),
                              crs = 4326)

thinned_maximus_coords_sf <- st_as_sf(x = thinned_maximus_coords_final,
                              coords = c("longitude", "latitude"),
                              crs = 4326)

thinned_sumatranus_coords_sf <- st_as_sf(x = thinned_sumatranus_coords_final,
                              coords = c("longitude", "latitude"),
                              crs = 4326)

tmap_mode(mode = "view")

asian_elephant_map <-
  tm_shape(thinned_indicus_coords_sf) +
    tm_symbols(col = "red",
               size = 0.2,
               alpha = 0.75) +
  tm_shape(thinned_maximus_coords_sf) +
    tm_symbols(col = "green",
               size = 0.2) +
  tm_shape(thinned_sumatranus_coords_sf) +
    tm_symbols(col = "blue",
                size = 0.2)

asian_elephant_map
```

### Combine all subspecies into single dataframe

```{r}
### Create dataframe with subspecies defined
all_subspecies_coords <- rbind(thinned_indicus_coords_final, thinned_maximus_coords_final, thinned_sumatranus_coords_final) 
# 
# # Save for MESS analysis
# write.csv(all_subspecies_coords, "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Asia_MESS_analysis/input_dataframes/all_subspecies_coords.csv", row.names = TRUE)

### Create dataframe where name = Asian Elephant
all_combined_asian_elephant_coords <- all_subspecies_coords %>% 
  mutate(name = case_when( 
    name == "Indian elephant" ~ "Elephas_maximus", 
    name == "Sri Lankan elephant" ~ "Elephas_maximus",
    name == "Sumatran elephant" ~ "Elephas_maximus"))

all_combined_asian_elephant_coords_sf <- st_as_sf(x = all_combined_asian_elephant_coords,
                              coords = c("longitude", "latitude"),
                              crs = 4326)
```

```{r}
# ### Save occs to Google Drive:
# write_csv(all_combined_asian_elephant_coords, "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Asian_Elephant/all_combined_asian_elephant_coords.csv") # overwrite = FALSE prevents from overwriting
# 
# st_write(all_combined_asian_elephant_coords_sf, "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Asian_Elephant/all_combined_asian_elephant_coords.shp")
# 
# ### Indian Elephant only:
# write_csv(thinned_indicus_coords_final, "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Asian_Elephant/final_indicus_coords.csv") # overwrite = FALSE prevents from overwriting
# 
# ### Sri Lankan Elephant only:
# write_csv(thinned_maximus_coords_final, "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Asian_Elephant/final_maximus_coords.csv") # overwrite = FALSE prevents from overwriting
# 
# ### Sumatran Elephant only:
# write_csv(thinned_sumatranus_coords_final, "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Asian_Elephant/final_sumatranus_coords.csv") # overwrite = FALSE prevents from overwriting
```

### Plot Wallace model outputs (historic)

```{r}
indicus_historic <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Wallace SDM Rasters/asia/1981_2010/indicus_historic.tif")

indicus_coords_final <- read_csv("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Asian_Elephant/final_indicus_coords.csv")

all_combined_asian_elephant_coords <- read_csv("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Data/Asian_Elephant/all_combined_asian_elephant_coords.csv")

all_spp_historic <- raster("/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Wallace SDM Rasters/asia/1981_2010/new_all_spp.tif")
```

```{r}
plot(all_spp_historic)
#points(all_combined_asian_elephant_coords$longitude, all_combined_asian_elephant_coords$latitude, col = "black", alpha = 0.5)
#plot(range, col = "black", add=TRUE)

plot(indicus_historic)
#points(indicus_coords_final$longitude, indicus_coords_final$latitude, col = "black", alpha = 0.5)

tmap_mode(mode = "view")

tm_shape(all_combined_asian_elephant_coords_sf) +
    tm_symbols(col = "black",
               size = 0.2,
               alpha = 0.75)
```

