---
title: "Africa Bivariate Maps"
author: "Taylor Lockmann"
date: "7/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load in packages
library(tidyverse)
library(terra)
library(raster)
```


## BASELINE/HISTORIC MAPPING ##

```{r}
# Read in the baseline land use and SDM
sdm <- rast("G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Wallace SDM Rasters/LQ/1981_2010/afel_historic_sdm.tif")
lu <- rast("G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif")
```


#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)

```{r}
ext(sdm) <- c(-25.3584728410000011,
              77.5998600799999849,
              -40.4084724209999990,
              26.3831939790000014)
```


#### Plot to look at them

```{r}
plot(sdm)
plot(lu)
```


#### Re-project the land use layer to have the same CRS as the SDM layer

This tends to take a while.

```{r}
lu_reproj <- lu %>% 
  project(crs(sdm))

plot(lu_reproj)
```


#### Reclassify values of the baseline year for cropland
We want cropland (category 5) to be 1, everything else to be 0

```{r}
baseline_cropland <- lu_reproj
baseline_cropland[baseline_cropland != 5] <- 0
baseline_cropland[baseline_cropland == 5] <- 1
plot(baseline_cropland)
```


#### Next, crop the baseline cropland map to the extent of the SDM

```{r}
baseline_afrotrop_crops <- crop(baseline_cropland, sdm)
plot(baseline_afrotrop_crops)
```


#### Now reclassify the values of the SDM raster for easier raster math

```{r}
sdm[sdm >= 0 & sdm < 0.33] <- 10
sdm[sdm >= 0.33 & sdm < 0.66] <- 20
sdm[sdm >=0.66 & sdm <= 1] <- 30

plot(sdm)
```


#### Make both of the rasters have the same resolution

```{r}
baseline_afrotrop_crops_resampled <- resample(baseline_afrotrop_crops, sdm, method = "near")
```


#### Add the two layers together

```{r}
baseline_bivariate <- (sdm + baseline_afrotrop_crops_resampled)
plot(baseline_bivariate)
```


#### Write the file to a .tif to export to QGIS

```{r}
writeRaster(baseline_bivariate, "G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Geospatial Data/bivariate_outputs/afel_bivariate_baseline.tif", overwrite = TRUE)
```







## FUTURE PROJECTIONS ##

### Year: 2041-2070
### Scenario: SSP1/RCP2.6
### GCM: GFDL

```{r}
# Load in packages
library(tidyverse)
library(terra)
library(raster)
```


#### Read in the PROJECTED land use and SDM
```{r}
sdm_126_2050 <- rast("G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Wallace SDM Rasters/LQ/2041_2070/126/change_maps/afel_change_2041_2070_126_gfdl.tif")
lu_126_2050 <- rast("G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Geospatial Data/Chen_LULC_data/SSP1_RCP26/global_SSP1_RCP26_2055.tif")
```


#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)

```{r}
ext(sdm_126_2050) <- c(-25.3584728410000011,
              77.5998600799999849,
              -40.4084724209999990,
              26.3831939790000014)
```


#### Plot to look at them

FOR SDM:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

```{r}
plot(sdm_126_2050)
plot(lu_126_2050)
```


#### Re-project the land use layer to have the same CRS as the SDM layer

```{r}
lu_reproj_126_2050 <- lu_126_2050 %>% 
  project(crs(sdm_126_2050))

plot(lu_reproj_126_2050)
```


#### Make both of the rasters have the same resolution

```{r}
crops_126_2050_resampled <- resample(lu_reproj_126_2050, sdm_126_2050, method = "near")
```


#### Reclassify values of the SDM Change map

In original:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

Now:
Same, except reclassify 2 (no change, not suitable) as NA

```{r}
sdm_126_2050[sdm_126_2050 == 2] <- NA
plot(sdm_126_2050)
```



#### Reclassify values of the year 2055 for cropland
We want cropland (category 5) to be 1, everything else to be 0

```{r}
cropland_126_2050 <- crops_126_2050_resampled
cropland_126_2050[cropland_126_2050 != 5] <- 0
cropland_126_2050[cropland_126_2050 == 5] <- 1
plot(cropland_126_2050)
```


#### Next, crop the cropland map to the extent of the SDM

```{r}
afrotrop_crops_126_2050 <- crop(cropland_126_2050, sdm_126_2050)
plot(afrotrop_crops_126_2050)
```


#### Make a map of cropland CHANGE

We want (future crops - present crops)

-1: Decrease in cropland (crops -> no crops)
0: No change
1: Increase in cropland (no crop -> crops)

```{r}
crops_change_126_2050 <- (afrotrop_crops_126_2050 - baseline_afrotrop_crops_resampled)
plot(crops_change_126_2050)
```

#### Reclassify cropland change map for easier raster math

```{r}
crops_change_126_2050[crops_change_126_2050 == -1] <- 10
crops_change_126_2050[crops_change_126_2050 == 0] <- 20
crops_change_126_2050[crops_change_126_2050 == 1] <- 30

plot(crops_change_126_2050)
```


#### Raster math - Cropland change vs SDM change (RCP1/SSP2.6, 2055)

```{r}
bivariate_change_126_2050 <- (sdm_126_2050 + crops_change_126_2050)
plot(bivariate_change_126_2050)
```

#### Write the file to a .tif to export to QGIS

```{r}
writeRaster(bivariate_change_126_2050, "G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Geospatial Data/bivariate_outputs/afel_bivariate_change_126_2050.tif", overwrite = TRUE)
```




### Year: 2041-2070
### Scenario: SSP5/RCP8.5
### GCM: GFDL

```{r}
# Load in packages
library(tidyverse)
library(terra)
library(raster)
```


#### Read in the PROJECTED land use and SDM
```{r}
sdm_585_2050 <- rast("G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Wallace SDM Rasters/LQ/2041_2070/585/change_maps/afel_change_2041_2070_585_gfdl.tif")
lu_585_2050 <- rast("G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Geospatial Data/Chen_LULC_data/SSP5_RCP85/global_SSP5_RCP85_2055.tif")
```


#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)

```{r}
ext(sdm_585_2050) <- c(-25.3584728410000011,
              77.5998600799999849,
              -40.4084724209999990,
              26.3831939790000014)
```


#### Plot to look at them

FOR SDM:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

```{r}
plot(sdm_585_2050)
plot(lu_585_2050)
```


#### Re-project the land use layer to have the same CRS as the SDM layer

```{r}
lu_reproj_585_2050 <- lu_585_2050 %>% 
  project(crs(sdm_585_2050))

plot(lu_reproj_585_2050)
```


#### Make both of the rasters have the same resolution

```{r}
crops_585_2050_resampled <- resample(lu_reproj_585_2050, sdm_585_2050, method = "near")
```


#### Reclassify values of the SDM Change map

In original:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

Now:
Same, except reclassify 2 (no change, not suitable) as NA

```{r}
sdm_585_2050[sdm_585_2050 == 2] <- NA
plot(sdm_585_2050)
```



#### Reclassify values of the year 2055 for cropland
We want cropland (category 5) to be 1, everything else to be 0

```{r}
cropland_585_2050 <- crops_585_2050_resampled
cropland_585_2050[cropland_585_2050 != 5] <- 0
cropland_585_2050[cropland_585_2050 == 5] <- 1
plot(cropland_585_2050)
```


#### Next, crop the cropland map to the extent of the SDM

```{r}
afrotrop_crops_585_2050 <- crop(cropland_585_2050, sdm_585_2050)
plot(afrotrop_crops_585_2050)
```


#### Make a map of cropland CHANGE

We want (future crops - present crops)

-1: Decrease in cropland (crops -> no crops)
0: No change
1: Increase in cropland (no crop -> crops)

```{r}
crops_change_585_2050 <- (afrotrop_crops_585_2050 - baseline_afrotrop_crops_resampled)
plot(crops_change_585_2050)
```

#### Reclassify cropland change map for easier raster math

```{r}
crops_change_585_2050[crops_change_585_2050 == -1] <- 10
crops_change_585_2050[crops_change_585_2050 == 0] <- 20
crops_change_585_2050[crops_change_585_2050 == 1] <- 30

plot(crops_change_585_2050)
```


#### Raster math - Cropland change vs SDM change (RCP1/SSP2.6, 2055)

```{r}
bivariate_change_585_2050 <- (sdm_585_2050 + crops_change_585_2050)
plot(bivariate_change_585_2050)
```

#### Write the file to a .tif to export to QGIS

```{r}
writeRaster(bivariate_change_585_2050, "G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Geospatial Data/bivariate_outputs/afel_bivariate_change_585_2050.tif", overwrite = TRUE)
```




