---
title: "Africa Bivariate Maps"
author: "Taylor Lockmann"
date: "7/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load in packages
library(tidyverse)
library(terra)
library(raster)

# Enter google filestream path including "HWC_data"
HWC_data <- "G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data"
```


## BASELINE/HISTORIC MAPPING ##

### CROPLAND ###

```{r}
# Read in the baseline land use and SDM
sdm <- rast(paste0(HWC_data, "/Wallace SDM Rasters/LQ/1981_2010/afel_historic_sdm.tif"))
lu <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))
```


#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)

```{r}
ext(sdm) <- c(-25.3584728410000011,
              77.5998600799999849,
              -40.4084724209999990,
              26.3831939790000014)
```


#### Plot to look at them

```{r}
plot(sdm)
plot(lu)
```


#### Re-project the land use layer to have the same CRS as the SDM layer

This tends to take a while.

```{r}
lu_reproj <- lu %>% 
  project(crs(sdm))

plot(lu_reproj)
```


#### Reclassify values of the baseline year for cropland
We want cropland (category 5) to be 1, everything else to be 0

```{r}
baseline_cropland <- lu_reproj
baseline_cropland[baseline_cropland != 5] <- 0
baseline_cropland[baseline_cropland == 5] <- 1
plot(baseline_cropland)
```


#### Aggregate cropland 
aggregate by factor of 10 (1km -> 10km)
factor <- ceiling(res(sdm)[1]/res(chen)[1])
terra::aggregate() (fact -> factor, function  -> mean, na.rm=true)
Then resample
Then reclassify into l/m/h categories (want to maintain No Cropland/0 category) (0, 0-0.5, 0.5-1)

```{r}
factor <- ceiling(res(sdm)[1]/res(lu_reproj)[1])

baseline_cropland <- terra::aggregate(x = baseline_cropland, fact = factor, fun = mean, na.rm = TRUE)

plot(baseline_cropland)
```



#### Now reclassify the values of the SDM raster for easier raster math

```{r}
sdm[sdm >= 0 & sdm < 0.33] <- 10
sdm[sdm >= 0.33 & sdm < 0.66] <- 20
sdm[sdm >=0.66 & sdm <= 1] <- 30

plot(sdm)
```


#### Make both of the rasters have the same resolution

```{r}
baseline_afrotrop_crops_resampled <- terra::resample(baseline_cropland, sdm, method = "bilinear")
```


#### Add the two layers together

```{r}
baseline_bivariate <- (sdm + baseline_afrotrop_crops_resampled)
plot(baseline_bivariate)
```


#### Write the file to a .tif to export to QGIS

```{r}
writeRaster(baseline_bivariate, paste0(HWC_data, "/Geospatial Data/bivariate_outputs/afel_bivariate_baseline.tif"), overwrite = TRUE)
```





### URBAN ###


```{r}
# Read in the baseline land use and SDM
sdm <- rast(paste0(HWC_data, "/Wallace SDM Rasters/LQ/1981_2010/afel_historic_sdm.tif"))
lu <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))
```


#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)

```{r}
ext(sdm) <- c(-25.3584728410000011,
              77.5998600799999849,
              -40.4084724209999990,
              26.3831939790000014)
```


#### Plot to look at them

```{r}
plot(sdm)
plot(lu)
```


#### Re-project the land use layer to have the same CRS as the SDM layer

This tends to take a while.

```{r}
lu_reproj <- lu %>% 
  project(crs(sdm))

plot(lu_reproj)
```


#### Reclassify values of the baseline year for urban
We want urban (category 5) to be 1, everything else to be 0

```{r}
baseline_urban <- lu_reproj
baseline_urban[baseline_urban != 6] <- 0
baseline_urban[baseline_urban == 6] <- 1
plot(baseline_urban)
```


#### Next, crop the baseline cropland map to the extent of the SDM

```{r}
baseline_afrotrop_urban <- crop(baseline_urban, sdm)
plot(baseline_afrotrop_urban)
```


#### Now reclassify the values of the SDM raster for easier raster math

```{r}
sdm[sdm >= 0 & sdm < 0.33] <- 10
sdm[sdm >= 0.33 & sdm < 0.66] <- 20
sdm[sdm >=0.66 & sdm <= 1] <- 30

plot(sdm)
```


#### Make both of the rasters have the same resolution

```{r}
baseline_afrotrop_urban_resampled <- resample(baseline_afrotrop_urban, sdm, method = "near")
```


#### Add the two layers together

```{r}
baseline_urban_bivariate <- (sdm + baseline_afrotrop_urban_resampled)
plot(baseline_urban_bivariate)
```


#### Write the file to a .tif to export to QGIS

```{r}
writeRaster(baseline_urban_bivariate, paste0(HWC_data, "/Geospatial Data/bivariate_outputs/afel_urban_bivariate_baseline.tif"), overwrite = TRUE)
```




## FUTURE PROJECTIONS ##

### Year: 2041-2070
### Scenario: SSP1/RCP2.6
### GCM: GFDL

```{r}
# Load in packages
library(tidyverse)
library(terra)
library(raster)
```


#### Read in the PROJECTED land use and SDM
```{r}
sdm_126_2050 <- rast(paste0(HWC_data, "/Wallace SDM Rasters/LQ/2041_2070/126/change_maps/afel_change_2041_2070_126_gfdl.tif"))
lu_126_2050 <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/SSP1_RCP26/global_SSP1_RCP26_2055.tif"))
```


#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)

```{r}
ext(sdm_126_2050) <- c(-25.3584728410000011,
              77.5998600799999849,
              -40.4084724209999990,
              26.3831939790000014)
```


#### Plot to look at them

FOR SDM:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

```{r}
plot(sdm_126_2050)
plot(lu_126_2050)
```


#### Re-project the land use layer to have the same CRS as the SDM layer

```{r}
lu_reproj_126_2050 <- lu_126_2050 %>% 
  project(crs(sdm_126_2050))

plot(lu_reproj_126_2050)
```


#### Make both of the rasters have the same resolution

```{r}
crops_126_2050_resampled <- resample(lu_reproj_126_2050, sdm_126_2050, method = "near")
```


#### Reclassify values of the SDM Change map

In original:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

Now:
Same, except reclassify 2 (no change, not suitable) as NA

```{r}
sdm_126_2050[sdm_126_2050 == 2] <- NA
plot(sdm_126_2050)
```



#### Reclassify values of the year 2055 for cropland
We want cropland (category 5) to be 1, everything else to be 0

```{r}
cropland_126_2050 <- crops_126_2050_resampled
cropland_126_2050[cropland_126_2050 != 5] <- 0
cropland_126_2050[cropland_126_2050 == 5] <- 1
plot(cropland_126_2050)
```


#### Next, crop the cropland map to the extent of the SDM

```{r}
afrotrop_crops_126_2050 <- crop(cropland_126_2050, sdm_126_2050)
plot(afrotrop_crops_126_2050)
```


#### Make a map of cropland CHANGE

We want (future crops - present crops)

-1: Decrease in cropland (crops -> no crops)
0: No change
1: Increase in cropland (no crop -> crops)

```{r}
crops_change_126_2050 <- (afrotrop_crops_126_2050 - baseline_afrotrop_crops_resampled)
plot(crops_change_126_2050)
```

#### Reclassify cropland change map for easier raster math

```{r}
crops_change_126_2050[crops_change_126_2050 == -1] <- 10
crops_change_126_2050[crops_change_126_2050 == 0] <- 20
crops_change_126_2050[crops_change_126_2050 == 1] <- 30

plot(crops_change_126_2050)
```


#### Raster math - Cropland change vs SDM change (SSP1/RCP2.6, 2055)

```{r}
bivariate_change_126_2050 <- (sdm_126_2050 + crops_change_126_2050)
plot(bivariate_change_126_2050)
```

#### Write the file to a .tif to export to QGIS

```{r}
writeRaster(bivariate_change_126_2050, paste0(HWC_data, "/Geospatial Data/bivariate_outputs/afel_bivariate_change_126_2050.tif"), overwrite = TRUE)
```




### Year: 2041-2070
### Scenario: SSP5/RCP8.5
### GCM: GFDL

```{r}
# Load in packages
library(tidyverse)
library(terra)
library(raster)
```


#### Read in the PROJECTED land use and SDM
```{r}
sdm_585_2050 <- rast(paste0(HWC_data, "/Wallace SDM Rasters/LQ/2041_2070/585/change_maps/afel_change_2041_2070_585_gfdl.tif"))
lu_585_2050 <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/SSP5_RCP85/global_SSP5_RCP85_2055.tif"))
```


#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)

```{r}
ext(sdm_585_2050) <- c(-25.3584728410000011,
              77.5998600799999849,
              -40.4084724209999990,
              26.3831939790000014)
```


#### Plot to look at them

FOR SDM:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

```{r}
plot(sdm_585_2050)
plot(lu_585_2050)
```


#### Re-project the land use layer to have the same CRS as the SDM layer

```{r}
lu_reproj_585_2050 <- lu_585_2050 %>% 
  project(crs(sdm_585_2050))

plot(lu_reproj_585_2050)
```


#### Make both of the rasters have the same resolution

```{r}
crops_585_2050_resampled <- resample(lu_reproj_585_2050, sdm_585_2050, method = "near")
```


#### Reclassify values of the SDM Change map

In original:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

Now:
Same, except reclassify 2 (no change, not suitable) as NA

```{r}
sdm_585_2050[sdm_585_2050 == 2] <- NA
plot(sdm_585_2050)
```



#### Reclassify values of the year 2055 for cropland
We want cropland (category 5) to be 1, everything else to be 0

```{r}
cropland_585_2050 <- crops_585_2050_resampled
cropland_585_2050[cropland_585_2050 != 5] <- 0
cropland_585_2050[cropland_585_2050 == 5] <- 1
plot(cropland_585_2050)
```


#### Next, crop the cropland map to the extent of the SDM

```{r}
afrotrop_crops_585_2050 <- crop(cropland_585_2050, sdm_585_2050)
plot(afrotrop_crops_585_2050)
```


#### Make a map of cropland CHANGE

We want (future crops - present crops)

-1: Decrease in cropland (crops -> no crops)
0: No change
1: Increase in cropland (no crop -> crops)

```{r}
crops_change_585_2050 <- (afrotrop_crops_585_2050 - baseline_afrotrop_crops_resampled)
plot(crops_change_585_2050)
```

#### Reclassify cropland change map for easier raster math

```{r}
crops_change_585_2050[crops_change_585_2050 == -1] <- 10
crops_change_585_2050[crops_change_585_2050 == 0] <- 20
crops_change_585_2050[crops_change_585_2050 == 1] <- 30

plot(crops_change_585_2050)
```


#### Raster math - Cropland change vs SDM change (SSP1/RCP2.6, 2055)

```{r}
bivariate_change_585_2050 <- (sdm_585_2050 + crops_change_585_2050)
plot(bivariate_change_585_2050)
```

#### Write the file to a .tif to export to QGIS

```{r}
writeRaster(bivariate_change_585_2050, paste0(HWC_data, "/Geospatial Data/bivariate_outputs/afel_bivariate_change_585_2050.tif"), overwrite = TRUE)
```


### Year: 2070-2100
### Scenario: SSP1/RCP2.6
### GCM: GFDL

```{r}
# Load in packages
library(tidyverse)
library(terra)
library(raster)
```


#### Read in the PROJECTED land use and SDM
```{r}
sdm_126_2080 <- rast(paste0(HWC_data, "/Wallace SDM Rasters/LQ/2071_2100/126/afel_historic_2071_2100_126_change_sdm.tif"))
lu_126_2080 <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/SSP1_RCP26/global_SSP1_RCP26_2085.tif"))
```


#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)

```{r}
ext(sdm_126_2080) <- c(-25.3584728410000011,
              77.5998600799999849,
              -40.4084724209999990,
              26.3831939790000014)
```


#### Plot to look at them

FOR SDM:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

```{r}
plot(sdm_126_2080)
plot(lu_126_2080)
```


#### Re-project the land use layer to have the same CRS as the SDM layer

```{r}
lu_reproj_126_2080 <- lu_126_2080 %>% 
  project(crs(sdm_126_2080))

plot(lu_reproj_126_2080)
```


#### Make both of the rasters have the same resolution

```{r}
crops_126_2080_resampled <- resample(lu_reproj_126_2080, sdm_126_2080, method = "near")
```


#### Reclassify values of the SDM Change map

In original:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

Now:
Same, except reclassify 2 (no change, not suitable) as NA

```{r}
sdm_126_2080[sdm_126_2080 == 2] <- NA
plot(sdm_126_2080)
```



#### Reclassify values of the year 2085 for cropland
We want cropland (category 5) to be 1, everything else to be 0

```{r}
cropland_126_2080 <- crops_126_2080_resampled
cropland_126_2080[cropland_126_2080 != 5] <- 0
cropland_126_2080[cropland_126_2080 == 5] <- 1
plot(cropland_126_2080)
```


#### Next, crop the cropland map to the extent of the SDM

```{r}
afrotrop_crops_126_2080 <- crop(cropland_126_2080, sdm_126_2080)
plot(afrotrop_crops_126_2080)
```


#### Make a map of cropland CHANGE

We want (future crops - present crops)

-1: Decrease in cropland (crops -> no crops)
0: No change
1: Increase in cropland (no crop -> crops)

```{r}
crops_change_126_2080 <- (afrotrop_crops_126_2080 - baseline_afrotrop_crops_resampled)
plot(crops_change_126_2080)
```

#### Reclassify cropland change map for easier raster math

```{r}
crops_change_126_2080[crops_change_126_2080 == -1] <- 10
crops_change_126_2080[crops_change_126_2080 == 0] <- 20
crops_change_126_2080[crops_change_126_2080 == 1] <- 30

plot(crops_change_126_2080)
```


#### Raster math - Cropland change vs SDM change (SSP1/RCP2.6, 2085)

```{r}
bivariate_change_126_2080 <- (sdm_126_2080 + crops_change_126_2080)
plot(bivariate_change_126_2080)
```

#### Write the file to a .tif to export to QGIS

```{r}
writeRaster(bivariate_change_126_2080, paste0(HWC_data, "/Geospatial Data/bivariate_outputs/afel_bivariate_change_126_2080.tif"), overwrite = TRUE)
```

### Year: 2070-2100
### Scenario: SSP5/RCP8.5
### GCM: GFDL

```{r}
# Load in packages
library(tidyverse)
library(terra)
library(raster)
```


#### Read in the PROJECTED land use and SDM
```{r}
sdm_585_2080 <- rast(paste0(HWC_data, "/Wallace SDM Rasters/LQ/2071_2100/585/afel_historic_2071_2100_585_change_sdm.tif"))
lu_585_2080 <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/SSP5_RCP85/global_SSP5_RCP85_2085.tif"))
```


#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)

```{r}
ext(sdm_585_2080) <- c(-25.3584728410000011,
              77.5998600799999849,
              -40.4084724209999990,
              26.3831939790000014)
```


#### Plot to look at them

FOR SDM:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

```{r}
plot(sdm_585_2080)
plot(lu_585_2080)
```


#### Re-project the land use layer to have the same CRS as the SDM layer

```{r}
lu_reproj_585_2080 <- lu_585_2080 %>% 
  project(crs(sdm_585_2080))

plot(lu_reproj_585_2080)
```


#### Make both of the rasters have the same resolution

```{r}
crops_585_2080_resampled <- resample(lu_reproj_585_2080, sdm_585_2080, method = "near")
```


#### Reclassify values of the SDM Change map

In original:
1 - decreasing suitability
2 - no change, not suitable
3 - no change, suitable
4 - increasing suitability

Now:
Same, except reclassify 2 (no change, not suitable) as NA

```{r}
sdm_585_2080[sdm_585_2080 == 2] <- NA
plot(sdm_585_2080)
```



#### Reclassify values of the year 2085 for cropland
We want cropland (category 5) to be 1, everything else to be 0

```{r}
cropland_585_2080 <- crops_585_2080_resampled
cropland_585_2080[cropland_585_2080 != 5] <- 0
cropland_585_2080[cropland_585_2080 == 5] <- 1
plot(cropland_585_2080)
```


#### Next, crop the cropland map to the extent of the SDM

```{r}
afrotrop_crops_585_2080 <- crop(cropland_585_2080, sdm_585_2080)
plot(afrotrop_crops_585_2080)
```


#### Make a map of cropland CHANGE

We want (future crops - present crops)

-1: Decrease in cropland (crops -> no crops)
0: No change
1: Increase in cropland (no crop -> crops)

```{r}
crops_change_585_2080 <- (afrotrop_crops_585_2080 - baseline_afrotrop_crops_resampled)
plot(crops_change_585_2080)
```

#### Reclassify cropland change map for easier raster math

```{r}
crops_change_585_2080[crops_change_585_2080 == -1] <- 10
crops_change_585_2080[crops_change_585_2080 == 0] <- 20
crops_change_585_2080[crops_change_585_2080 == 1] <- 30

plot(crops_change_585_2080)
```


#### Raster math - Cropland change vs SDM change (SSP5/RCP8.5, 2085)

```{r}
bivariate_change_585_2080 <- (sdm_585_2080 + crops_change_585_2080)
plot(bivariate_change_585_2080)
```

#### Write the file to a .tif to export to QGIS

```{r}
writeRaster(bivariate_change_585_2080, paste0(HWC_data, "/Geospatial Data/bivariate_outputs/afel_bivariate_change_585_2080.tif"), overwrite = TRUE)
```







