---
title: "Asia Bivariate Maps"
author: "Taylor Lockmann"
date: '2022-07-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load in packages
library(tidyverse)
library(terra)
library(raster)

HWC_data <- "G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data"
```


## BASELINE/HISTORIC MAPPING ##


# Read in the baseline land use and SDM

```{r}
sdm <- rast(paste0(HWC_data, "/Wallace SDM Rasters/asia/1981_2010/indicus_historic.tif"))
lu <- rast(paste0(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))
```


#### SDM raster does not have an extent, so we're going to assign it (found by importing to QGIS)
              
```{r}
ext(sdm) <- c(65.8581934609999990,
              131.0665265334999958,
              -12.2168058669999979,
              35.8248606080000016)
```
   
#### Plot to look at them

```{r}
plot(sdm)
plot(lu)
```

# Re-project the land use layer to have the same CRS as the SDM layer

```{r}
lu_reproj <- lu %>% 
  project(crs(sdm))

plot(lu_reproj)
```

#### Reclassify values of the baseline year for cropland
We want cropland (category 5) to be 1, everything else to be 0

```{r}
baseline_cropland <- lu_reproj
baseline_cropland[baseline_cropland != 5] <- 0
baseline_cropland[baseline_cropland == 5] <- 1
plot(baseline_cropland)
```

#### Next, crop the baseline cropland map to the extent of the SDM

```{r}
baseline_indomalaya_crops <- crop(baseline_cropland, sdm)
plot(baseline_indomalaya_crops)
```

# Now reclassify the values of the SDM raster for easier raster math

```{r}
sdm[sdm >= 0 & sdm < 0.33] <- 10
sdm[sdm >= 0.33 & sdm < 0.66] <- 20
sdm[sdm >=0.66 & sdm <= 1] <- 30

plot(sdm)
```


# Make both of the rasters have the same resolution

```{r}
baseline_indomalaya_crops_resampled <- resample(baseline_indomalaya_crops, sdm, method = "near")
```


# Add the two layers together

```{r}
baseline_bivariate_indomalaya <- (sdm + baseline_indomalaya_crops_resampled)
plot(baseline_bivariate_indomalaya)
```


# Write the file to a .tif to export to QGIS

```{r}
writeRaster(baseline_bivariate_indomalaya, "G:/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data/Geospatial Data/bivariate_outputs/asel_bivariate_baseline.tif", overwrite = TRUE)
```

