---
title: "Replication of Di Minin 2021 Analysis"
author: "Mia Guarnieri"
date: '2022-10-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(terra)
library(sf)
library(tmap)
library(geos)
library(rnaturalearth)
library(rnaturalearthdata)
library(tidyterra)

#File path to the HWC_data folder

HWC_data <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data"
```

#Input data

##Range data

Species range data for savanna and forest elephants, downloaded from IUCN redlist.

```{r}
#turn off spherical geometry to simplify joins, etc.
sf_use_s2(FALSE)

#savanna elephant range (filtered to only keep extant ranges)
sav <- read_sf(here(HWC_data, "/Geospatial Data/range_data/iucn_range_sav_elephant/data_0.shp")) %>% 
  filter(LEGEND %in% c("Extant (resident)", "Extant & Reintroduced (resident)"))

#savanna elephant range, geometry only (no other data)

sav_geom <- sav %>% 
  select(geometry)

#forest elephant range (filtered to only keep extant ranges)
forest <- read_sf(here(HWC_data, "/Geospatial Data/range_data/iucn_range_forest_elephant/data_0.shp")) %>% 
  filter(LEGEND %in% c("Extant (resident)", "Extant & Reintroduced (resident)"))

#combined range map for savanna and forest elephants
all_elephant_range <- rbind(sav, forest)
```

```{r}
#save combined range data

st_write(all_elephant_range, dsn = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/range_sav_forest/all_elephant_range.shp"))

#read it back in and check it

all_range <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/range_sav_forest/all_elephant_range.shp"))

```


```{r}
#plot combined range
tm_shape(all_elephant_range) +
  tm_polygons(col = "LEGEND") +
  tmap_mode("view")

#plot savanna elephant range
tm_shape(sav_geom) +
  tm_polygons() +
  tmap_mode("view")
```

##World protected areas (WPAs) data

WPA data obtained from The World Database on Protected Areas (<http://www.protectedplanet.net>).

World protected area aata is divided into 3 sets of polygons and 3 sets of points which need to be merged together to create one polygon layer and one points layer for use. We will be using only the polygons layer for analysis.

Di Minin et al. (2021) only included in their analysis IUCN categories Ia (Strict Nature Reserve), Ib (Wilderness Area), II (National Park), III (Natural Monument or Feature), and IV (Habitat/Species Management Area). Additionally, to prevent overestimation of the area coverage of protected areas caused by overlapping designations, Di Minin et al. merged polygons into a single layer. 


```{r}
#turn off spherical geometry to simplify joins, etc.
sf_use_s2(FALSE)

#polygon layers

wpa_1_pol <- read_sf(here(HWC_data, "/Geospatial Data/protected_areas/WDPA_Africa_Oct2022_shp/WDPA_WDOECM_Oct2022_Public_AF_shp_0/WDPA_WDOECM_Oct2022_Public_AF_shp-polygons.shp")) 

wpa_2_pol <- read_sf(here(HWC_data, "/Geospatial Data/protected_areas/WDPA_Africa_Oct2022_shp/WDPA_WDOECM_Oct2022_Public_AF_shp_1/WDPA_WDOECM_Oct2022_Public_AF_shp-polygons.shp"))

wpa_3_pol <- read_sf(here(HWC_data, "/Geospatial Data/protected_areas/WDPA_Africa_Oct2022_shp/WDPA_WDOECM_Oct2022_Public_AF_shp_2/WDPA_WDOECM_Oct2022_Public_AF_shp-polygons.shp")) 

#combine polygon layers and filter for IUCN categories Ia (Strict Nature Reserve), Ib (Wilderness Area), II (National Park), III (Natural Monument or Feature), and IV (Habitat/Species Management Area)

wpa_all_polygons <- rbind(wpa_1_pol, wpa_2_pol, wpa_3_pol) %>% 
  filter(IUCN_CAT %in% c("Ia", "Ib", "II", "III", "IV"))

#merge polygons into a single layer

wpa_allpol_dissolved <- st_union(wpa_all_polygons, by_feature = FALSE) %>% 
  st_cast(to = "POLYGON")

#wpa polygons, geometry only - no other attributes

wpa_allpol_geom <- wpa_all_polygons %>% 
  select(geometry)

#plot merged polygon layer

tm_shape(wpa_allpol_dissolved) +
  tm_polygons() +
  tmap_mode("view")

```

```{r}
#save the wpa shapefiles

st_write(wpa_all_polygons, dsn = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/wpas_merged_filtered/wpa_allpol_filtered.shp"))

st_write(wpa_allpol_dissolved, dsn = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/wpas_filtered_dissolved/wpa_allpol_filtered_diss.shp"))

#read them back in and check them

wpa_allpol <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/wpas_merged_filtered/wpa_allpol_filtered.shp"))

wpa_dissolved <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/wpas_filtered_dissolved/wpa_allpol_filtered_diss.shp"))

```

```{r point data}
#point data layers - not used in analysis, provided just for thoroughness

wpa_1_point <- read_sf(here(HWC_data, "/Geospatial Data/protected_areas/WDPA_Africa_Oct2022_shp/WDPA_WDOECM_Oct2022_Public_AF_shp_0/WDPA_WDOECM_Oct2022_Public_AF_shp-points.shp"))

wpa_2_point <- read_sf(here(HWC_data, "/Geospatial Data/protected_areas/WDPA_Africa_Oct2022_shp/WDPA_WDOECM_Oct2022_Public_AF_shp_1/WDPA_WDOECM_Oct2022_Public_AF_shp-points.shp"))

wpa_3_point <- read_sf(here(HWC_data, "/Geospatial Data/protected_areas/WDPA_Africa_Oct2022_shp/WDPA_WDOECM_Oct2022_Public_AF_shp_2/WDPA_WDOECM_Oct2022_Public_AF_shp-points.shp"))

#combined points layer

wpa_all_points <- rbind(wpa_1_point, wpa_2_point, wpa_3_point)

#plot points layer

tm_shape(wpa_all_points) +
  tm_dots() +
  tmap_mode("view")

#plot polygon and point layers together
tm_shape(wpa_allpol_dissolved) +
  tm_polygons() +
tm_shape(wpa_all_points) +
  tm_dots() +
  tmap_mode("view")
```


#Creating extended range maps

From Di Minin et al: The elephant range maps and the protected area layer were intersected to select all protected areas that contain parts of lion and elephant range and/or were adjacent to the species-range maps. The identified protected areas were then merged with the species-range maps to create a new extended range layer

```{r}

##Savanna elephant only in this chunk

#protected areas that contain part of elephant range

wpa_intersect <- st_join(wpa_allpol_geom, sav_geom, join = st_intersects, left = FALSE)

#verification plot: sav range and intersection

tm_shape(sav_geom) +
  tm_polygons() +
tm_shape(wpa_intersect) +
  tm_polygons( col = "blue") +
tmap_mode("view")

#protected areas that are adjacent to elephant range

wpa_adj <- st_join(wpa_allpol_geom, sav_geom, join = st_touches, left = FALSE)

#this join is returning no data, suggesting that there are no polygons that satisfy the st_touches function (i.e., no adjacent polygons)

#creating an extended range map - no data, just polygons

ext_range <- rbind(sav_geom, wpa_intersect, wpa_adj)

#dissolving polygons into one layer - didn't save this one as it may not be correct
ext_range_dissolved <- st_union(ext_range)
```

```{r}
#save the shapefile

st_write(ext_range, dsn = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/extended_range/extended_range_sav.shp"))

#read it back in and check it

ext_range_sav <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/extended_range/extended_range_sav.shp"))

tm_shape(ext_range) +
  tm_polygons(col = "blue") +
tm_shape(ext_range_sav) +
  tm_polygons() +
  tmap_mode("view")

```


```{r}
#test plots

#verification plots: sav range and extended range map
tm_shape(ext_range) +
  tm_polygons() +
tm_shape(sav_geom) +
  tm_polygons(col = "blue") +
  tmap_mode("view")

tm_shape(ext_range) +
  tm_polygons() +
tm_shape(wpa_intersect) +
  tm_polygons(col = "blue") +
  tmap_mode("view")

tm_shape(ext_range) +
  tm_polygons() +
  tmap_mode("view")
```

```{r}
##Savanna and forest elephant ranges in this chunk

#read in wpa data and filter for geometry
wpa_allpol <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/wpas_merged_filtered/wpa_allpol_filtered.shp"))

#wpa polygons, geometry only - no other attributes

wpa_allpol_geom <- wpa_allpol %>% 
  select(geometry)

#read in range data

el_range <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/range_sav_forest/all_elephant_range.shp"))

#filter just for geometry

range_geom <- el_range %>% 
  select(geometry)

#protected areas that contain part of elephant range

wpa_int <- st_join(wpa_allpol_geom, range_geom, join = st_intersects, left = FALSE)

#verification plot: sav range and intersection

tm_shape(range_geom) +
  tm_polygons() +
tm_shape(wpa_int) +
  tm_polygons( col = "blue") +
tmap_mode("view")

#protected areas that are adjacent to elephant range

wpa_adjacent <- st_join(wpa_allpol_geom, range_geom, join = st_touches, left = FALSE)

#this join is returning no data, suggesting that there are no polygons that satisfy the st_touches function (i.e., no adjacent polygons)

#creating an extended range map - no data, just polygons

ext_range_all <- rbind(range_geom, wpa_int, wpa_adjacent)

#dissolving polygons into one layer - didn't save this one as it may not be correct
ext_range_all_dissolved <- st_union(ext_range_all)

```

```{r}
#test plots

tm_shape(ext_range_all) +
  tm_polygons() +
tm_shape(range_geom) +
  tm_polygons(col = "blue") +
  tmap_mode("view")

tm_shape(ext_range_all) +
  tm_polygons() +
tm_shape(wpa_int) +
  tm_polygons(col = "blue") +
  tmap_mode("view")

tm_shape(ext_range_all) +
  tm_polygons(col = "cyan4") +
  tmap_mode("view")
```


#Pressure Layers

Di Minin et al. only retained areas where human, cattle, and crop densities were in the first decile (the decile with the highest human population, crop, and cattle densities). We will only be using human population and cropland measurements, as we aren't looking at lion conflict (cattle predation).

##Land cover data

Land classification：
1	Water
2	Forest
3	Grassland
4	Barren
5	Cropland - this is the one we will select for
6	Urban
7	Permanent snow and ice

```{r cropping to Africa}
#turn off spherical geometry to simplify joins, etc.
sf_use_s2(FALSE)

#load in the land use/ land cover data

lulc <- rast(here(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))

#read in a shapefile for Africa and rasterize it

africa <- vect(here(HWC_data, "/Geospatial Data/basemaps/africa_continent/africa_continent.shp"))

africa_rast <- rasterize(africa, lulc)

#mask lulc to africa extent

lulc_africa <- mask(lulc, africa)

#test plot

plot(lulc_africa)

tm_shape(lulc_africa, raster.warp = FALSE) +
  tm_raster() +
  tmap_mode("view")
```

```{r save}
#save the file to the drive

writeRaster(lulc_africa, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/cropped_lulc/lulc_africa.tif"), filetype = "GTiff")
```


```{r aggregate}
#read in lulc data

lulc_africa <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/cropped_lulc/lulc_africa.tif"))

#filter just for cropland by reclassifying (cropland is 1, everything else is 0)

africa_cropland <- lulc_africa

africa_cropland[africa_cropland != 5] <- 0

africa_cropland[africa_cropland == 5] <- 1

#test plot

plot(africa_cropland)

#aggregate cropland

africa_cropland_agg <- terra::aggregate(africa_cropland, fact = 10, fun = mean, na.rm = TRUE)

plot(africa_cropland_agg)

#save raster for aggregated cropland
writeRaster(africa_cropland_agg, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/lulc_formatted/lulc_aggregated/africa_cropland_agg.tif"), filetype = "GTiff", overwrite = TRUE)

#read in and calculate max
crop <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/lulc_formatted/lulc_aggregated/africa_cropland_agg.tif"))

#max value: 1
```


```{r top decile}
#read in the data
crop <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/lulc_formatted/lulc_aggregated/africa_cropland_agg.tif"))

#calculate deciles
decs_crop <- global(africa_cropland_agg, quantile, probs = seq(0, 1, 0.1), na.rm = TRUE)
  
#save cutoff value for highest decile
topdec_crop <- decs_crop$X90.

# keep only the top decile (as in Di Minin et al.)

top10_crop <- africa_cropland_agg

top10_crop[top10_crop < topdec_crop] <- NA

top10_crop[top10_crop >= topdec_crop] <- 1

plot(top10_crop)

#save raster for cropland top decile

writeRaster(top10_crop, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/lulc_formatted/lulc_top10/top10_crop.tif"), filetype = "GTiff", overwrite = TRUE)

#90th percentile: 0.65
```


```{r data vis}
#visualization

#turn off spherical geometry to simplify joins, etc.
sf_use_s2(FALSE)

extended_range <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/extended_range/extended_range_sav.shp"))

crop_dens <- (rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/lulc_formatted/lulc_top10/top10_crop.tif")))

#create a basemap

basemap_africa <- ne_countries(
  continent = "Africa",
  scale = "medium", 
  returnclass = "sf") %>% 
  st_transform(crs = crs(crop_dens))  # make sure crs is same as raster

basemap_africa_vect <- basemap_africa %>% 
  vect()

#map crop density

plot(basemap_africa_vect, col = "grey90")
plot(crop_dens, add = TRUE)
```


##Human density data

Fpop data - exploratory

```{r}
#read in necessary data layers

#read in lulc for reprojection
lulc <- rast(here(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))
  
#turn off spherical geometry to simplify joins, etc.
sf_use_s2(FALSE)
  
#read in a raster for Africa
  
africa <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/africa_rast/africa_rast.tif"))

#create a function

pop_wrangling <- function(x){
  
  #reproject the designated population raster
  popdens <- project(x, lulc)
  
  #mask pop density to africa extent
  popdens_africa <- mask(popdens, africa)
  
  #aggregate pop density
  
  africa_popdens_agg <- terra::aggregate(popdens_africa, fact = 10, fun = sum, na.rm = TRUE)
  
  #keep only the top decile (as in Di Minin et al.)
  
  #calculate deciles
  decs <- global(africa_popdens_agg, quantile, probs = seq(0, 1, 0.1), na.rm = TRUE)
  
  #save cutoff value for highest decile
  
  topdec <- decs$X90.
  
  #reclassify so that the upper decile is 1 and all other values are NA
  
  top10_pop <- africa_popdens_agg
  
  top10_pop[top10_pop < topdec] <- NA
  
  top10_pop[top10_pop >= topdec] <- 1
  
  return(top10_pop)
}

#SSP1
SSP1 <- rast(here(HWC_data, "/Geospatial Data/Pop_dens/fpop_data/FPOP_SSP1/FPOP_SSP1_2020.tif"))
  
SSP1_wrangled <- pop_wrangling(SSP1)

#SSP2
SSP2 <- rast(here(HWC_data, "/Geospatial Data/Pop_dens/fpop_data/FPOP_SSP2/FPOP_SSP2_2020.tif"))

SSP2_wrangled <- pop_wrangling(SSP2)

#SSP3
SSP3 <- rast(here(HWC_data, "/Geospatial Data/Pop_dens/fpop_data/FPOP_SSP3/FPOP_SSP3_2020.tif"))

SSP3_wrangled <- pop_wrangling(SSP3)

#SSP4
SSP4 <- rast(here(HWC_data, "/Geospatial Data/Pop_dens/fpop_data/FPOP_SSP4/FPOP_SSP4_2020.tif"))

SSP4_wrangled <- pop_wrangling(SSP4)

#SSP5
SSP5 <- rast(here(HWC_data, "/Geospatial Data/Pop_dens/fpop_data/FPOP_SSP5/FPOP_SSP5_2020.tif"))

SSP5_wrangled <- pop_wrangling(SSP5)
```

```{r}
#test plots for human population density layers

#create a basemap

basemap_africa <- ne_countries(
  continent = "Africa",
  scale = "medium", 
  returnclass = "sf") %>% 
  st_transform(crs = crs(SSP1_wrangled))  # make sure crs is same as raster

basemap_africa_vect <- basemap_africa %>% 
  vect()

#map pop density rasters

#combine all plots into one graphic
par(mfrow=c(2,3))

#SSP1
plot(basemap_africa_vect, col = "grey98")
plot(SSP1_wrangled, add = TRUE, col = "darkgreen")

#SSP2
plot(basemap_africa_vect, col = "grey98")
plot(SSP2_wrangled, add = TRUE, col = "darkseagreen4")

#SSP3
plot(basemap_africa_vect, col = "grey98")
plot(SSP3_wrangled, add = TRUE, col = "goldenrod1")

#SSP4
plot(basemap_africa_vect, col = "grey98")
plot(SSP4_wrangled, add = TRUE, col = "orange1")

#SSP5
plot(basemap_africa_vect, col = "grey98")
plot(SSP5_wrangled, add = TRUE, col = "orangered")
```


```{r}
#save raster for aggregated pop density

writeRaster(africa_popdens_agg, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/pop_density/africa_popdens_agg.tif"), filetype = "GTiff", overwrite = TRUE)

#save raster for pop density top decile

writeRaster(top10_pop, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/pop_density/top10_pop.tif"), filetype = "GTiff", overwrite = TRUE)

```

Worldpop 2015 - exploratory

```{r}
#read in the data
wpop_2015 <- rast(here(HWC_data, "/Geospatial Data/Pop_dens/fpop_data/ppp_2015_1km_Aggregated.tif"))

#read in lulc for reprojection
lulc <- rast(here(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))

#read in a raster for Africa
  
africa <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/africa_rast/africa_rast.tif"))

#run the wrangling function (created above)
wp_15_wrangled <- pop_wrangling(wpop_2015)

#save raster for pop density top decile

writeRaster(wp_15_wrangled, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/pop_density/wpop_2015_top10.tif"), filetype = "GTiff", overwrite = TRUE)

```

Worldpop 2010 - this is the layer we will use for the baseline

```{r wp2010 aggregated}

#read in the data
wpop_2010 <- rast(here(HWC_data, "/Geospatial Data/Pop_dens/fpop_data/ppp_2010_1km_Aggregated.tif"))

lulc <- rast(here(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))

africa <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/africa_rast/africa_rast.tif"))

#calclulating max value
agg_pop <- function(x){
  
  #reproject the designated population raster
  popdens <- project(x, lulc)
  
  #mask pop density to africa extent
  popdens_africa <- mask(popdens, africa)
  
  #aggregate pop density
  
  africa_popdens_agg <- terra::aggregate(popdens_africa, fact = 10, fun = sum, na.rm = TRUE)
  
  return(africa_popdens_agg)
}

wp2010_aggregated <- agg_pop(wpop_2010)


writeRaster(wp2010_aggregated, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/pop_density/wpop_2010_agg.tif"), filetype = "GTiff", overwrite = TRUE)

#max: 2953414

```


```{r wp2010 top dec}

#read in aggregated raster

wp2010_agg <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/pop_density/wpop_2010_agg.tif"))

#keep only the top decile (as in Di Minin et al.)
  
#calculate deciles
decs <- global(wp2010_agg, quantile, probs = seq(0, 1, 0.1), na.rm = TRUE)
  
#save cutoff value for highest decile
  
topdec <- decs$X90.
  
#reclassify so that the upper decile is 1 and all other values are NA
  
top10_pop <- wp2010_agg
  
top10_pop[top10_pop < topdec] <- NA
  
top10_pop[top10_pop >= topdec] <- 1

#save raster for pop density top decile

writeRaster(top10_pop, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/pop_density/wpop_2010_top10.tif"), filetype = "GTiff", overwrite = TRUE)


#top decile: 5184.694 (rounded to 3 decimals)
```


GPW v 4 - we decided ultimately not to use this one

```{r}
lulc <- rast(here(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))

popdensgpw <- rast(here(HWC_data, "/Geospatial Data/Pop_dens/gpw_v4_population_density_adjusted_to_2015_unwpp_country_totals_rev11_2015_2pt5_min.tif")) %>% 
  project(lulc)

#turn off spherical geometry to simplify joins, etc.
sf_use_s2(FALSE)

#read in a shapefile for Africa and rasterize it

africa <- vect(here(HWC_data, "/Geospatial Data/basemaps/africa_continent/africa_continent.shp"))

africa_rast <- rasterize(africa, popdensgpw)

#mask lulc to africa extent

gpw_africa <- mask(popdensgpw, africa)

#test plot

plot(gpw_africa)

#aggregate pop density

africa_gpw_agg <- terra::aggregate(gpw_africa, fact = 10, fun = sum, na.rm = TRUE)

plot(africa_gpw_agg)

#reclassify aggregated agriculture into 3 categories

# keep only the top decile (as in Di Minin et al.)

decsgpw <- global(africa_gpw_agg, quantile, probs = seq(0, 1, 0.1), na.rm = TRUE)
  
topdecgpw <- decsgpw$X90.

top10_pop_gpw <- africa_gpw_agg

top10_pop_gpw[top10_pop_gpw < topdecgpw] <- NA

top10_pop_gpw[top10_pop_gpw >= topdecgpw] <- 1

#create a basemap

basemap_africa <- ne_countries(
  continent = "Africa",
  scale = "medium", 
  returnclass = "sf") %>% 
  st_transform(crs = crs(top10_pop_gpw))  # make sure crs is same as raster

basemap_africa_vect <- basemap_africa %>% 
  vect()

#map pop density

plot(basemap_africa_vect, col = "grey98")
plot(top10_pop_gpw, add = TRUE)
```

```{r}
#save raster for aggregated pop density

writeRaster(africa_gpw_agg, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/pop_density/africa_gpw_agg.tif"), filetype = "GTiff", overwrite = TRUE)

#save raster for pop density top decile

writeRaster(top10_pop_gpw, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/pop_density/top10_pop_gpw.tif"), filetype = "GTiff", overwrite = TRUE)

```

##Ranked pressures layer

2 - High risk: high human + crop density 
1 - Med risk: high human OR crop density 
0 - Low risk: NO high human and NO high crop density

```{r}
#read in the data, set NA values to 0

human_dens <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/pop_density/wpop_2010_top10.tif"))

human_dens[is.na(human_dens)] <- 0 

crop_dens <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/lulc_formatted/lulc_top10/top10_crop.tif"))

crop_dens[is.na(crop_dens)] <- 0 

#read in a shapefile for Africa and rasterize it

africa <- vect(here(HWC_data, "/Geospatial Data/basemaps/africa_continent/africa_continent.shp")) %>% 
  project(crop_dens)

africa_rast <-rasterize(africa, crop_dens)

#raster math to create ranked conflict layer

ranked_conflict <- human_dens + crop_dens

#re-mask to Africa

ranked_conflict_masked <- mask(ranked_conflict, africa_rast)

#create a basemap

basemap_africa <- ne_countries(
  continent = "Africa",
  scale = "medium", 
  returnclass = "sf") %>% 
  st_transform(crs = crs(ranked_conflict))  # make sure crs is same as raster

basemap_africa_vect <- basemap_africa %>% 
  vect()

#map ranked conflict

plot(basemap_africa_vect, col = "grey98")
plot(ranked_conflict_masked, add = TRUE)

```


```{r}
#save the ranked conflict layer

writeRaster(ranked_conflict_masked, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/ranked_pressure_layers/wp2010_current_day_rp.tif"), filetype = "GTiff", overwrite = TRUE)

```


#Conflict boundaries

##Raster version
Extended range map is buffered by 10 km and intersected with classified pressures layer

```{r}
#read in lulc data for reprojection

lulc <- rast(here(HWC_data, "/Geospatial Data/Chen_LULC_data/global_LULC_2015.tif"))

crs <- crs(lulc)

#read in the extended range map and reproject to the correct crs

ext_range <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/extended_range/extended_range_sav.shp")) %>% 
  st_transform(crs = crs)

#buffer the extended range map by 10 km

ext_range_buffered <- st_buffer(ext_range, 10000)

#intersect the pressure layer with extended range map

#convert range map to a spatvector and then a spatraster

range_buff_rast <- vect(ext_range_buffered) %>% 
  rasterize(lulc)

#cut out internal polygons of protected areas so that only the buffer remains

ext_range_rast <- vect(ext_range) %>% 
  rasterize(lulc)

buffers_only <- mask(range_buff_rast, ext_range_rast, inverse = TRUE)

#read in the ranked pressures map

ranked_press <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/ranked_pressure_layers/wp2010_current_day_rp.tif")) %>% 
  project(lulc, method = "near")

conflict_int <- mask(ranked_press, buffers_only)

#create a basemap

basemap_africa <- ne_countries(
  continent = "Africa",
  scale = "medium", 
  returnclass = "sf") %>% 
  st_transform(crs = crs(ranked_press))  # make sure crs is same as raster

basemap_africa_vect <- basemap_africa %>% 
  vect()

#set color matrix

colors <- rbind(c(0, "darkgreen"),
                c(1, "goldenrod"),
                c(2, "orangered"))

#plot conflict intersection
plot(basemap_africa_vect, col = "grey98")
plot(conflict_int, add = TRUE, col = colors)

```

```{r}
#test plots

#buffered extended range map
tm_shape(ext_range_buffered) +
  tm_polygons() +
  tm_shape(ext_range) +
  tm_polygons(col = "blue") +
  tmap_mode("view")
```

```{r}
#save the layer into drive

writeRaster(conflict_int, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/conflict_boundaries/wp2010_current_day_cb_raster.tif"), filetype = "GTiff", overwrite = TRUE)

```

##Vector version

```{r}
#read in the conflict boundaries and test plot

current_cb <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/conflict_boundaries/wp2010_current_day_cb_raster.tif"))

#create a basemap

basemap_africa <- ne_countries(
  continent = "Africa",
  scale = "medium", 
  returnclass = "sf") %>% 
  st_transform(crs = crs(current_cb))  # make sure crs is same as raster

basemap_africa_vect <- basemap_africa %>% 
  vect()

#set color matrix

colors <- rbind(c(0, "darkgreen"),
                c(1, "goldenrod"),
                c(2, "orangered"))

pal <- c("darkgreen", "goldenrod", "orangered")

#plot conflict boundaries
plot(basemap_africa_vect, col = "grey98")
plot(current_cb, add = TRUE, col = colors)

#vectorize

#first make it a spatvector
current_cb_vect <- terra::as.polygons(current_cb, trunc=TRUE, dissolve=TRUE, values=TRUE,
    na.rm=TRUE, na.all=FALSE, extent=FALSE)

#then turn that into a polyline
current_cb_line <- st_as_sf(current_cb_vect) %>% 
  st_cast("MULTILINESTRING")

#plot conflict boundaries
plot(basemap_africa_vect, col = "grey98")
plot(current_cb_line, add = TRUE, pal = pal)

```

```{r}
#save the polyline shapefile

st_write(current_cb_line, dsn = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/conflict_boundaries/wp2010_current_day_cb_lines.shp"))

```


##Asessing validity

"Used Latin hypercube sampling, which is a form of sampling used to reduce the number of runs necessary for a Monte Carlo simulation to achieve a reasonably accurate random distribution67, to randomly vary 100 times the distance values between the extended range and human pressure maps. Specifically, we divided the low, moderate, high, and severe conflict lines into 100-m segments, calculated the minimum distance for each segment to human pressure within a 10, 20, and 30-km buffer distance from the edge of the extended range map layer, and then randomly varied that distance 100 times across ±10% of the value. We then averaged the resulting 100 randomly created distance values for each segment and identified which segments fell outside of the analyzed buffer distances of 10, 20, and 30-km. We tested for 20 and 30-km buffer distances, as we wanted to assess the variability of the fencing distance to different buffer sizes."
