---
title: "Conflict and SDM Asia"
author: "Mia Guarnieri"
date: "2023-02-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(terra)
library(sf)
library(tmap)
library(geos)
library(rnaturalearth)
library(rnaturalearthdata)
library(tidyterra)
library(kableExtra)

#File path to the HWC_data folder

HWC_data <- "/Users/mia/Library/CloudStorage/GoogleDrive-mguarnieri@ucsb.edu/My Drive/Arnhold Project/HWC_data"
```

#Reclass conflict layers to be binary inc/dec

```{r}
#reclassify function
reclass_rast <- function(x){
  
  rast <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/differenced_rasters_asia/", x))
  
  rast[rast == 0] <- NA
  
  rast[rast > 0] <- 1
  
  rast[rast < 0] <- -1
  
  writeRaster(rast, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/differenced_rasters_asia/binary_diffs_asia/", name), overwrite = TRUE)

}

rast_list <- list.files(path = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/differenced_rasters_asia/"), pattern = '.tif')

for (i in rast_list) {
  
  name <- paste0("asia_binary_", i)
  
  reclass_rast(i)
  
}

```

#Filter binary conflict layers and mask SDMs

Load in and reproject SDMs

```{r}
#read in raster for reprojection

asia_diff_s12050 <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/differenced_rasters_asia/ssp1_rcp26_2050_diff.tif"))

#read in and reproject SDMs
asia_sdm_ssp1 <- rast(here(HWC_data, "/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_126_gfdl.tif")) %>% 
  project(asia_diff_s12050)

asia_sdm_ssp3 <- rast(here(HWC_data, "/Wallace SDM Rasters/asia/2011_2040/change_maps/change_2011_2040_370_gfdl.tif")) %>% 
  project(asia_diff_s12050)
```


Read in binary conflict rasters and split into increasing/decreasing only

```{r}
asia_diff_s12050 <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/differenced_rasters_asia/ssp1_rcp26_2050_diff.tif"))

s12050_inc <- asia_diff_s12050

s12050_inc[s12050_inc > 0] <- 1

s12050_inc[s12050_inc <= 0] <- NA


s12050_dec <- asia_diff_s12050

s12050_dec[s12050_dec >= 0] <- NA

s12050_dec[s12050_dec < 0] <- 1



asia_diff_s32050 <- rast(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/differenced_rasters_asia/ssp3_rcp70_2050_diff.tif"))

s32050_inc <- asia_diff_s32050

s32050_inc[s32050_inc > 0] <- 1

s32050_inc[s32050_inc <= 0] <- NA


s32050_dec <- asia_diff_s32050

s32050_dec[s32050_dec >= 0] <- NA

s32050_dec[s32050_dec < 0] <- 1

```


Mask SDM by separated rasters

```{r}
#increasing rasters

s1_sdm_inc <- mask(asia_sdm_ssp1, s12050_inc)

s3_sdm_inc <- mask(asia_sdm_ssp3, s32050_inc)

#decreasing rasters

s1_sdm_dec <- mask(asia_sdm_ssp1, s12050_dec)

s3_sdm_dec <- mask(asia_sdm_ssp3, s32050_dec)

```


#Polygonize masked SDM rasters

```{r}
polygons <- function(x){
  
  pol <- x %>%
    terra::as.polygons(trunc=TRUE, dissolve=TRUE, values=TRUE, na.rm=TRUE, na.all=FALSE, extent=FALSE)
  
  name <- paste0(deparse(substitute(x)), ".shp")
 
  writeVector(pol, filename = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/sdm_exploration_polygons", name), overwrite = TRUE)
  
}

polygons(s1_sdm_inc)
polygons(s3_sdm_inc)
polygons(s1_sdm_dec)
polygons(s3_sdm_dec)

```


#Percent area calculations

1 = decreasing suitability
4 = increasing suitability

```{r}

#set up the function

perc_area_table <- function(x){
  
  diff_pol <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/sdm_exploration_polygons", x))
  
  colnames(diff_pol) = c("conflict_change", "geometry")
  
  table <- diff_pol %>% 
    as.data.frame() %>% 
    mutate(area = st_area(diff_pol, unit = "m")) %>% 
    mutate(perc_area = (area/sum(area) * 100)) %>% 
    select(conflict_change, perc_area) %>% 
    filter(conflict_change == 1 | conflict_change == 4)
  
  return(table)
}

#list all of the files

sdm_pol_list <- list.files(path = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/sdm_exploration_polygons"), pattern = '.shp')


#apply the area function over the list

sdm_area_list <- lapply(sdm_pol_list, perc_area_table)

sdm_conf_change_table_pol <- sdm_area_list %>% reduce(full_join, by = "conflict_change") %>% 
  units::drop_units()

colnames(sdm_conf_change_table_pol) = c("suitability", sdm_pol_list)

descriptor <- c("Decreasing", "Increasing")

sdm_conf_change_table_pol$suitability <- descriptor

write.csv(sdm_conf_change_table_pol, file = here(HWC_data, "Data/Di Minin HWC", "sdm_conf_change_table_asia.csv"), row.names=FALSE)

```

#Make a nice table

```{r}
sdm_conf_change_table_pol <- read_csv(here(HWC_data, "Data/Di Minin HWC", "sdm_conf_change_table_asia.csv"))

dec <- c(rep(2, each = 5))

align <- c(rep("c", each = 5))

sdm_conf_change_pol_nicetable <- sdm_conf_change_table_pol %>%
  kable(digits = dec,
        escape = FALSE,
        align = align,
        col.names = c("Suitability Change", "Decreasing", "Increasing", "Decreasing", "Increasing"),
        caption = "<center><strong>Percentage of Increasing or Decreasing Habitat Suitability Within Increasing or Decreasing Conflict Boundaries for Asian Elephants</strong></center>") %>% 
  kable_styling(full_width = FALSE, position = "center") %>% 
  add_header_above(c(" ", "SSP 1/RCP 2.6" = 2, "SSP 3/RCP 7.0" = 2), background = c("#ffd3b6", "#a8e6cf")) %>% 
  add_header_above(c("", "Change in Conflict Risk" = 4)) %>% 
  column_spec(2:3, background = "#a8e6cf") %>%
  column_spec(4:5, background = "#ffd3b6")

sdm_conf_change_pol_nicetable

library(magick)

save_kable(sdm_conf_change_pol_nicetable, file = here("/Users/mia/Desktop/Fellowships/Arnhold HWC/sdm_conf_change_pol_nicetable_asia.jpeg"), zoom = 2.5)
```


#Scaling it so that it is % of total range

```{r}
#read in range proportions from earlier

props_table <- read_csv(here(HWC_data, "Data/Di Minin HWC", "conflict_change_polygons_byyear_asia.csv"))

s1_inc <- (props_table$"SSP1 2050"[[4]] + props_table$"SSP1 2050"[[5]])/100

s1_dec <- (props_table$"SSP1 2050"[[1]] + props_table$"SSP1 2050"[[2]])/100


s3_inc <- (props_table$"SSP3 2050"[[4]] + props_table$"SSP3 2050"[[5]])/100

s3_dec <- (props_table$"SSP3 2050"[[1]] + props_table$"SSP3 2050"[[2]])/100



#multiply the percentages calculated here by those proportions to scale properly

sdm_conf_change_table_pol <- read_csv(here(HWC_data, "Data/Di Minin HWC", "sdm_conf_change_table_asia.csv"))

scaled_sdm_props <- sdm_conf_change_table_pol %>% 
  transform(s1_sdm_dec.shp = ((s1_sdm_dec.shp/100) * s1_dec) * 100,
            s1_sdm_inc.shp = ((s1_sdm_inc.shp/100) * s1_inc) * 100,
            s3_sdm_dec.shp = ((s3_sdm_dec.shp/100) * s3_dec) * 100,
            s3_sdm_inc.shp = ((s3_sdm_inc.shp/100) * s3_inc) * 100)

write.csv(scaled_sdm_props, file = here(HWC_data, "Data/Di Minin HWC", "scaled_sdm_conf_change_table_asia.csv"), row.names=FALSE)

```


```{r}
scaled_sdm_props <- read_csv(here(HWC_data, "Data/Di Minin HWC", "scaled_sdm_conf_change_table_asia.csv"))

dec <- c(rep(2, each = 5))

align <- c(rep("c", each = 5))

sdm_conf_change_pol_nicetable <- scaled_sdm_props %>%
  kable(digits = dec,
        escape = FALSE,
        align = align,
        col.names = c("Suitability Change", "Decreasing", "Increasing", "Decreasing", "Increasing")) %>% 
  kable_styling(full_width = FALSE, position = "center") %>% 
  add_header_above(c(" ", "SSP 1/RCP 2.6" = 2, "SSP 3/RCP 7.0" = 2), background = c("#ffd3b6", "#a8e6cf")) %>% 
  add_header_above(c("", "Change in Conflict Risk" = 4)) %>% 
  column_spec(2:3, background = "#a8e6cf") %>%
  column_spec(4:5, background = "#ffd3b6")

sdm_conf_change_pol_nicetable

library(magick)

save_kable(sdm_conf_change_pol_nicetable, file = here("/Users/mia/Desktop/Fellowships/Arnhold HWC/scaled_sdm_conf_change_table_asia.jpeg"), zoom = 2.5)
```

