---
title: "Replication of DiMinin 2021 Analysis - ASIA"
author: "Grace Kumaishi"
date: "1/12/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(terra)
library(sf)
library(tmap)
library(geos)
library(rnaturalearth)
library(rnaturalearthdata)
library(tidyterra)

#File path to the HWC_data folder

HWC_data <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1YB-Hz3L-kWyiZMg2UM89GQkvqXyZUW1H/HWC_data"
```

# Input data

## Range data

Species range data for Asian elephant, downloaded from IUCN redlist.

```{r}
# turn off spherical geometry to simplify joins, etc.
sf_use_s2(FALSE)

# Asian elephant range (filtered to keep only extant ranges)
asian_elephant_range <- read_sf(here(HWC_data, "/Data/Asian_Elephant/redlist_species_data/data_0.shp")) %>% 
  filter(LEGEND %in% c("Extant (resident)", "Extant & Reintroduced (resident)"))
```

```{r}
# plot range
tm_shape(asian_elephant_range) +
  tm_polygons(col = "LEGEND") +
  tmap_mode("view")
```

## World protected areas (WPAs) data

WPA data obtained from The World Database on Protected Areas (<http://www.protectedplanet.net>).

World protected area data is divided into 3 sets of polygons and 3 sets of points which need to be merged together to create one polygon layer and one points layer for use. We will be using only the polygons layer for analysis.

Di Minin et al. (2021) only included in their analysis IUCN categories Ia (Strict Nature Reserve), Ib (Wilderness Area), II (National Park), III (Natural Monument or Feature), and IV (Habitat/Species Management Area). Additionally, to prevent overestimation of the area coverage of protected areas caused by overlapping designations, Di Minin et al. merged polygons into a single layer. 

```{r}
indomalay_region <- read_sf(here(HWC_data, "/R_files/R_output_data/indomalay_region/indomalay_region.shp"))
```

```{r}
#turn off spherical geometry to simplify joins, etc.
sf_use_s2(FALSE)

#polygon layers

wpa_1_pol <- read_sf(here(HWC_data, "/Geospatial Data/protected_areas/WDPA_Asia_Jan2023_shp/WDPA_WDOECM_Jan2023_Public_AS_shp_0/WDPA_WDOECM_Jan2023_Public_AS_shp-polygons.shp"))

wpa_2_pol <- read_sf(here(HWC_data, "/Geospatial Data/protected_areas/WDPA_Asia_Jan2023_shp/WDPA_WDOECM_Jan2023_Public_AS_shp_1/WDPA_WDOECM_Jan2023_Public_AS_shp-polygons.shp"))

wpa_3_pol <- read_sf(here(HWC_data, "/Geospatial Data/protected_areas/WDPA_Asia_Jan2023_shp/WDPA_WDOECM_Jan2023_Public_AS_shp_2/WDPA_WDOECM_Jan2023_Public_AS_shp-polygons.shp"))

#combine polygon layers and filter for IUCN categories Ia (Strict Nature Reserve), Ib (Wilderness Area), II (National Park), III (Natural Monument or Feature), and IV (Habitat/Species Management Area)

wpa_all_polygons_uncropped <- rbind(wpa_1_pol, wpa_2_pol, wpa_3_pol) %>% 
  filter(IUCN_CAT %in% c("Ia", "Ib", "II", "III", "IV"))

# crop to indomalaya region
wpa_all_polygons <- st_crop(wpa_all_polygons_uncropped, indomalay_region)

#merge polygons into a single layer

wpa_allpol_dissolved <- st_union(wpa_all_polygons, by_feature = FALSE) %>% 
  st_cast(to = "POLYGON")

#wpa polygons, geometry only - no other attributes

wpa_allpol_geom <- wpa_all_polygons %>% 
  select(geometry)

#plot merged polygon layer

tm_shape(wpa_allpol_dissolved) +
  tm_polygons() +
  tmap_mode("view")
```

```{r}
# save the wpa shapefiles

st_write(wpa_all_polygons, dsn = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/wpas_merged_filtered/wpa_allpol_filtered_ASIA.shp"))

st_write(wpa_allpol_dissolved, dsn = here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/wpas_filtered_dissolved/wpa_allpol_filtered_diss_ASIA.shp"))

#read them back in and check them

wpa_allpol <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/wpas_merged_filtered/wpa_allpol_filtered_ASIA.shp"))

wpa_dissolved <- read_sf(here(HWC_data, "/Geospatial Data/Diminin_Replication_Data/wpas_filtered_dissolved/wpa_allpol_filtered_diss_ASIA.shp"))
```







