---
title: "HWC Occurrence Data"
author: "Roshni Katrak-Adefowora"
date: "11/29/2021"
output: html_document
---

# NOTE: This does not need to be run again unless we're changing the input settings to create and thin our occurrence data. All occurrence results are saved as csv's and can be read in with the other Rmds.

## Description:

This markdown file outlines the first steps for creating data for species distribution modeling (SDM) with Wallace. Here, we create a csv of occurrence points for each species of interest (African lion, African savanna elephant, and African forest elephant). Occurrence points were downloaded from GBIF, cropped to our study area boundary (Afrotropical region), and spatially thinned.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load packages
library(tidyverse)
library(rgbif)
library(maptools)
library(dismo)
library(rgeos)
library(viridis)
library(raster)
library(DHARMa)
library(spocc)
library(sf)
library(rgdal)
library(spData)
library(here)
library(lubridate)
library(kableExtra)

#install wallace
library(wallace)

#load Wallace functions
source(system.file('shiny/funcs', 'functions.R', package = 'wallace'))

#HWC data file path (# Enter file path to YOUR HWC_data folder, including "HWC_data")
hwc_data <- "I:/My Drive/HWC_data"
```

### Download species occurence data and get coordinates

We begin by downloading the species occurrence points for the African lion, African savanna elephant, and African forest elephant using Wallace's spocc:occ() function. Choose which chunk to run based on the species of interest.

African Lion
```{r}
# Gives global records.  If limit is set high, this function can take a while to run.
results <- spocc::occ(query = "Panthera leo", # scientific name, here we are using lions
                      from = "gbif", # set to records from https://www.gbif.org/
                      limit = 15000, # max number of records
                      has_coords = TRUE) # gets the lat/long for each observation

# select just GBIF records, format the species name
results[["gbif"]]$data[[formatSpName("Panthera leo")]]

# select just the necessary information
myspecies_coords <- as.data.frame(results$gbif$data$Panthera_leo) %>% # using GBIF data
  dplyr::select(longitude, latitude, occurrenceStatus, coordinateUncertaintyInMeters, institutionCode, references, basisOfRecord, eventDate) %>%  # selecting just the columns that we want
  filter(!basisOfRecord %in% c("FOSSIL_SPECIMEN", "PRESERVED_SPECIMEN", "LIVING_SPECIMEN"),
         occurrenceStatus == "PRESENT",
        eventDate <= "2010-12-31" & eventDate >= "1981-01-01")
```

African Savanna Elephant
```{r}
# Gives global records.  If limit is set high, this function can take a while to run.
results <- spocc::occ(query = "Loxodonta africana (Blumenbach, 1797)", # scientific name, here we are using lions
                      from = "gbif", # set to records from https://www.gbif.org/
                      limit = 15000, # max number of records
                      has_coords = TRUE) # gets the lat/long for each observation

# select just GBIF records, format the species name
results[["gbif"]]$data[[formatSpName("Loxodonta africana")]]

# select just the necessary information
myspecies_coords <- as.data.frame(results$gbif$data$Loxodonta_africana) %>% # using GBIF data
  dplyr::select(longitude, latitude, occurrenceStatus, coordinateUncertaintyInMeters, institutionCode, references, basisOfRecord, eventDate) %>%  # selecting just the columns that we want
  filter(!basisOfRecord %in% c("FOSSIL_SPECIMEN", "PRESERVED_SPECIMEN", "LIVING_SPECIMEN"),
         occurrenceStatus == "PRESENT",
        eventDate <= "2010-12-31" & eventDate >= "1981-01-01")
```

African Forest Elephant
```{r}
# Gives global records.  If limit is set high, this function can take a while to run.
results <- spocc::occ(query = "Loxodonta cyclotis",
                      from = "gbif", # set to records from https://www.gbif.org/
                      limit = 15000, # max number of records
                      has_coords = TRUE) # gets the lat/long for each observation

# select just GBIF records, format the species name
results[["gbif"]]$data[[formatSpName("Loxodonta cyclotis")]]

# select just the necessary information
myspecies_coords <- as.data.frame(results$gbif$data$Loxodonta_cyclotis) %>% # using GBIF data
  dplyr::select(longitude, latitude, occurrenceStatus, coordinateUncertaintyInMeters, institutionCode, references, basisOfRecord, eventDate) %>%  # selecting just the columns that we want
  filter(!basisOfRecord %in% c("FOSSIL_SPECIMEN", "PRESERVED_SPECIMEN", "LIVING_SPECIMEN"),
         occurrenceStatus == "PRESENT",
         eventDate <= "2010-12-31" & eventDate >= "1981-01-01")
```

### Clean data

```{r}
# remove rows with duplicate coordinates
occs.dups <- duplicated(myspecies_coords[c('longitude', 'latitude')])
myspecies_coords <- myspecies_coords[!occs.dups,]

# make sure latitude and longitude are numeric (sometimes they are characters)
myspecies_coords$latitude <- as.numeric(myspecies_coords$latitude)
myspecies_coords$longitude <- as.numeric(myspecies_coords$longitude)

# give all records a unique ID
myspecies_coords$occID <- row.names(myspecies_coords)
```

### Crop data using Africa boundary

We created a shapefile of the Afrotropical region, which we cropped the occurrence points to. The shapefile was read into Wallace. We decided to use a shapefile of Africa instead of selecting with a polygon on Wallace because it's easier and cleaner.

```{r}
#get spatial extent using Afrotropical ecoregion from WWF. Data downloaded from https://www.worldwildlife.org/publications/terrestrial-ecoregions-of-the-world
# afrotropical_region <- read_sf(dsn = here(hwc_data, "R_files/R_input_data/wwf_ecoregions/official"), layer = "wwf_terr_ecos") %>% 
#   filter(REALM == "AT")
# 
# #check crs
# crs(afrotropical_region) # +proj=longlat +datum=WGS84 +no_defs 

# create shapefile for wallace
# st_write(afrotropical_region, dsn = here(hwc_data, "R_files/R_output_data/afrotropical_region/afrotropical_region.shp"), layer = "afrotropical_region.shp", driver = "ESRI Shapefile")

afrotropical_region_sp <- st_read(here(hwc_data, "R_files/R_output_data/afrotropical_region/afrotropical_region.shp"))

# convert to a spatial polygon
afrotropical_region_spatial <- as_Spatial(afrotropical_region_sp, cast = TRUE)

# creates new data frame with observation data lat/long points
occs.xy <- myspecies_coords[c('longitude', 'latitude')]

# convert species data to spatial layer
coordinates(occs.xy) <- ~longitude+latitude
projection(occs.xy) <- CRS('+proj=longlat +datum=WGS84')

# double-check that polygon and points have the same projection
crs(afrotropical_region_spatial) # +proj=longlat +datum=WGS84 +no_defs 
crs(occs.xy) # +proj=longlat +datum=WGS84 +no_defs 

# overlays those points over the polygon
intersect <- sp::over(occs.xy, afrotropical_region_spatial)
# could also use 
# raster::crop(occs.xy, afrotropical_region_spatial)

# removes na values, so selects for points where they overlap the focal polygon
intersect.rowNums <- as.numeric(which(!(is.na(intersect))))

# filters our occurrence data to those overlapping points
occs <- myspecies_coords[intersect.rowNums, ] %>% #again, change occs to myspecies_coords
  drop_na(longitude, latitude)
occs$name <- "Loxodonta africana" #change depending on the species!
```

#### Plot occurrence points on map

```{r}
# world map example

(data("wrld_simpl"))

# run plot and points function at once
plot(wrld_simpl, 
     xlim = range(occs$long, na.rm=TRUE),
     ylim = range(occs$lat, na.rm=TRUE), 
     axes = TRUE, 
     col = "light yellow"
     )
points(occs$longitude, occs$latitude, col = 'blue', pch = 20, cex = 0.75) #add the points
```

### Spatial thin

This will remove occurrence points that are within a specified distance from one-another, and is very important when dealing with areas that have a disproportionate amount of observations in a small area (like in wildlife reserves and parks, which we observe in Africa). It may not necessarily reflect that the climate in that area is ideally suited for that organism. For us, it may be a reflection of reduced human-impacts and an increase in reported occurrences by visitors.

```{r}
# just doing 10 replicates for now, thinning to 10 km
output <- spThin::thin(occs, 'latitude', 'longitude', 'name', 
                       thin.par = 10, # thinned to 10 km
                       reps = 10, # default on Wallace is 100, but run time is long, so a low number is good for testing
                       locs.thinned.list.return = TRUE, 
                       write.files = FALSE, 
                       verbose = FALSE)

# find the iteration that returns the max number of occurrences
maxThin <- which(sapply(output, nrow) == max(sapply(output, nrow)))

# if there's more than one max, pick the first one
maxThin <- output[[ifelse(length(maxThin) > 1, maxThin[1], maxThin)]]  

# subset data to those thinned records
occs <- occs[as.numeric(rownames(maxThin)),]

# save occs to upload to Wallace if needed
         occs_wallace <- occs %>% 
           dplyr::select(name, longitude, latitude, eventDate) # change order to match

write_csv(occs_wallace, here(hwc_data, "R_files/R_output_data/occurrence_points/savanna_elephant_chelsa_points_thinned_data.csv"), append = TRUE)
```


### Plot again (thinned points)

```{r}
# world map example

(data("wrld_simpl"))

# run plot and points function at once
plot(wrld_simpl, 
     xlim = range(occs_wallace$long, na.rm=TRUE),
     ylim = range(occs_wallace$lat, na.rm=TRUE), 
     axes = TRUE, 
     col = "light yellow"
     )
points(occs_wallace$longitude, occs_wallace$latitude, col = 'blue', pch = 20, cex = 0.75) #add the points
```